---
title: "Analysis of immune cells from prostate tumor microenvironment"
author: "Leonard Herault"
date: '2024-01-04'
output: html_document
---

## Workflow used

Multiomics metacell were identified in each sample using SCimplify by combining log norm RNA and cell ranger atac peaks (same peaks as in the orginal study).
RNA and ATAC modality were integrated separately using a similar workflow as in the original study at the single cell level.
Seurat RPCA was used to integrate RNA, Harmony for ATAC.
As in the original study, a WNN graph was computed (here for the metacells), using the 2 integrated modality.
Major cell type corresponding to original clusters were identified.

After this step a new peak calling was performed in each major type using macs2.
This allow us to use more precise and narrow peaks for downstream analysis of the ATAC modality (motif analysis, DA peaks)
**Note that here we won't use these new peaks to compute a new multimodal latent space.**

Here we analyzed more deeply the immune clusters of metacells.
First we will recompute a WNN for the immune metacells (from the corrected LSI + PCA computed for all metacells).


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Environment loading

```{r}
library(Seurat)
library(dplyr)
library(Matrix)
library(ggplot2)
library(cowplot)
library(EnsDb.Mmusculus.v79)
library(Signac)
library(S4Vectors)
library(patchwork)
#library(JASPAR2022)
library(TFBSTools)
library(BSgenome.Mmusculus.UCSC.mm10)
```

## Loading of data

We load the integrated data of immune cells with 2 ATAC slot:

* ATAC : based on cell ranger peaks, used for data integration and clustering
* peaks : based on the second peak calling with mac2, here only use for downstream analysis of the ATAC modality

```{r}
combined.metacells <- readRDS("../../output/10xMultiomeProstateHan22/logNorm/macs2_major_type/immune_hoccomoco_motifs/combined.metacells.with.macs.peak.rds")
```


First LSI component is correlated with sequencing depth. As previously, we won't use it for computing the wnn 
```{r}
DepthCor(combined.metacells)
```

We compute the the new WNN for immune metacells.
We use this WNN for clustering at different resolution and UMAP projection.

```{r}
combined.metacells <- FindMultiModalNeighbors(combined.metacells, 
                                              reduction.list = list("integrated_pca", "integrated_lsi"), 
                                              dims.list = list(1:50, 2:50))

combined.metacells <- FindClusters(combined.metacells, 
                                   resolution = c(c(1:9)*0.1),
                                   graph.name = "wsnn") 

combined.metacells <- RunUMAP(combined.metacells,
                              nn.name = "weighted.nn", 
                              reduction.name = "wnn.umap", 
                              reduction.key = "wnnUMAP_")


combined.metacells <- RunUMAP(combined.metacells, 
                              reduction  = "integrated_lsi", 
                              reduction.name = "atac.umap", 
                              reduction.key = "atacUMAP_",
                              dims = c(2:50))

combined.metacells <- RunUMAP(combined.metacells, 
                              reduction  = "integrated_pca", 
                              reduction.name = "rna.umap", 
                              reduction.key = "rnaUMAP_",
                              dims = c(1:50))


```

PLot of the results

```{r fig.height= 2.5,fig.width=2.5}
DimPlot(combined.metacells,reduction = "wnn.umap")
DimPlot(combined.metacells,reduction = "wnn.umap",group.by = "celltype")
DimPlot(combined.metacells,reduction = "wnn.umap",group.by = "wsnn_res.0.3")
DimPlot(combined.metacells,reduction = "rna.umap",group.by = "wsnn_res.0.3")
DimPlot(combined.metacells,reduction = "atac.umap",group.by = "wsnn_res.0.3")

VlnPlot(combined.metacells,"ATAC.weight",sort = T,group.by = "wsnn_res.0.3")

DimPlot(combined.metacells,reduction = "wnn.umap",group.by = "wsnn_res.0.9",label = T)

DimPlot(combined.metacells,reduction = "wnn.umap",group.by = "wsnn_res.0.4",label = T)

```

Plot of major types and their markers

```{r}
DefaultAssay(combined.metacells) <- "RNA"
FeaturePlot(combined.metacells,c("S100a9","Cd3e","Cd19","C1qa"),reduction = "wnn.umap")
VlnPlot(combined.metacells,features = c("S100a9","Cd3e","Cd19","C1qa"),pt.size = 0.01,group.by = "celltype",ncol = 2)
```

We retain the 0.4 resolution separating DC (Ciita, Flt3) from macrophages.

```{r, fig.height=4,fig.width=3}
VlnPlot(combined.metacells,features = c("Cd8a","Cd4","Cd19",
                                        "Clec10a","Ciita","Flt3",
                                        "Trem2","Gpnmb","Lrp12",
                                        "Fn1","Cd86",
                                        "Cxcr2","Mreg"),pt.size = 0.001,ncol = 3)
```









```{r,}


```

We can make a marker analysis of this first clustering.
```{r}
Idents(combined.metacells) <- "wsnn_res.0.4"
DefaultAssay(combined.metacells) <- "RNA"
markers <- FindAllMarkers(combined.metacells,only.pos = T)
markers <- markers[markers$p_val_adj < 0.05,]
head(markers)
```


## Finner annotation

We can 
# Neutrophils

```{r}
VlnPlot(combined.metacells[,combined.metacells$wsnn_res.0.4 %in% c(0,3,5)], features = c("Nfkb1","Hdc","Il1b","Siglecf","Trem1","Cxcr2"),group.by = "wsnn_res.0.4")
```



```{r}
FeaturePlot(combined.metacells[,combined.metacells$wsnn_res.0.4 %in% c(0,3,5)],
            features = c("Nfkb1","Hdc","Il1b","Siglecf","Trem1","Cxcr2","P2rx7","Mreg"),reduction = "wnn.umap")

```


```{r}

## NK and CD8 T cells
Idents(combined.metacells) <- 'wsnn_res.0.4'
combined.metacells <- FindSubCluster(combined.metacells,cluster = 4,resolution = 0.6,graph.name = "wsnn")
DimPlot(combined.metacells[,combined.metacells$wsnn_res.0.4 == 4],group.by = 'sub.cluster',reduction = "wnn.umap",label = T)

```
```{r}
DimPlot(combined.metacells[,combined.metacells$wsnn_res.0.4 == 4],group.by = 'sub.cluster',reduction = "wnn.umap",label = T)
VlnPlot(combined.metacells[,combined.metacells$wsnn_res.0.4 %in% c(4)],features = c("Cd8a","Cd4","Cd3g","Tox","Tcf7","Il7r","Ncr1","Klrb1c", "Klrb1b"),group.by="sub.cluster")
```


```{r}
DimPlot(combined.metacells,reduction = "wnn.umap",label = T,repel = T)

```






```{r}
Idents(combined.metacells) <- "sub.cluster"
DimPlot(combined.metacells,reduction = "wnn.umap")
combined.metacells <- RenameIdents(combined.metacells,
                                   "0" = "Neutro_inf_low",
                                   "1" = "Macro_Cd86_high",
                                   "2" = "Macro_Fn1_high",
                                   "3" = "Neutro_inf_high",
                                   "4_0" = "Tex_CD8",
                                   "4_1" = "Tnaive_CD8",
                                   "4_2" = "NKT",
                                   "5" = "Neutro_Siglecf_high",
                                   "6" = "CD4",
                                   "7" = "Macro_Trem2_high",
                                   "8" = "DC",
                                   "9" = "B cells"
)

combined.metacells$celltype.l2 <- Idents(combined.metacells)

DimPlot(combined.metacells,reduction = "wnn.umap",label = T,repel = T)

combined.metacells$fine_celltype = Idents(combined.metacells)
```
#Subdivide CD4

# CD4
```{r}
Idents(combined.metacells) <- "wsnn_res.0.4"

combined.metacells <- FindSubCluster(combined.metacells,cluster = 6,resolution = 0.8,graph.name = "wsnn")

DimPlot(combined.metacells[,combined.metacells$wsnn_res.0.4 == 6],reduction = "wnn.umap",group.by = "sub.cluster")

FeaturePlot(combined.metacells[,combined.metacells$wsnn_res.0.4 == 6],reduction = "wnn.umap",features  = c("Cd8a","Cd4"))
```
```{r}
FeatureScatter(combined.metacells[,combined.metacells$wsnn_res.0.4 == 6],feature1 = "Cd8a", feature2 = "Cd4",group.by = "sub.cluster")

```



```{r}
Idents(combined.metacells) <- "sub.cluster"

VlnPlot(combined.metacells[,combined.metacells$wsnn_res.0.4 %in% c(6)],features = c("Cd8a","Runx3","Il7r","Tcf7","Cd4","Foxp3","Il2ra","Pdcd1","Trdc","Tcrg-C1","Tcrg-C2"),group.by = "sub.cluster")
```


```{r}
Idents(combined.metacells) <- "sub.cluster"
combined.metacells <- RenameIdents(combined.metacells,
                                   "6_0" = "Naive_T_cells",
                                   "6_1" = "T_reg",
                                   "6_2" = "gd_T",
                                   "6_3" = "CD4_CD25posFOXP3neg"
)
levels(combined.metacells$fine_celltype) <- c(levels(combined.metacells$fine_celltype),c("Naive_T_cells","T_reg",'gd_T',"CD4_CD25posFOXP3neg"))
combined.metacells$fine_celltype[combined.metacells$fine_celltype == "CD4"] <- Idents(combined.metacells[,combined.metacells$fine_celltype == "CD4"])

DimPlot(combined.metacells,reduction = "wnn.umap",label = T,repel = T,group.by = "fine_celltype")

```
```{r fig.height=2.5,fig.width=4}
mycolors <- c('#E5D2DD', '#53A85F', '#F1BB72', '#F3B1A0', '#D6E7A3', '#57C3F3', '#476D87',
              '#E95C59', '#E59CC4', '#AB3282', '#BD956A', '#8C549C',
              '#9FA3A8', '#58A4C3', "#b20000",'#E4C755', '#F7F398',
              '#AA9A59', '#E63863', '#E39A35', '#C1E6F3', '#6778AE', '#91D0BE', '#B53E2B',
              '#712820', '#DCC1DD', '#CCE0F5', '#CCC9E6', '#625D9E', '#68A180', '#3A6963',
              '#968175')

DimPlot(combined.metacells,reduction = "wnn.umap",label = T,repel = T,group.by = "celltype") + ggtitle("original celltype")



DimPlot(combined.metacells,reduction = "wnn.umap",label = T,repel = T, cols = mycolors,group.by = "fine_celltype")

```


```{r fig.height=5, fig.width=12}

DefaultAssay(combined.metacells) <- "RNA"
genes <- c("S100a9","Nfkb1","Siglecf","C1qa","Fn1","Cd86","Trem2","Flt3","Cd3g","Klrb1c","Cd8a","Tox","Tcf7","Cd4","Foxp3","Il2ra","Tcrg-C1","Cd19")

combined.metacells$fine_celltype <- factor(combined.metacells$fine_celltype,
                                           levels = c("","Neutro_inf_high","Neutro_inf_low","Neutro_Siglecf_high",
                                                      "Macro_Fn1_high","Macro_Cd86_high","Macro_Trem2_high",
                                                      "DC","NKT","Tex_CD8","Tnaive_CD8","Naive_T_cells",
                                                      "T_reg","CD4_CD25posFOXP3neg","gd_T","B cells")) 

VlnPlot(object = combined.metacells,features = genes,stack = T,group.by = "fine_celltype",fill.by= "ident",cols = mycolors,same.y.lims = F)  + NoLegend() + theme(axis.title.y = element_blank())
```
```{r}
Idents(combined.metacells) <- "fine_celltype"
library(SuperCellMultiomics)
supercell_FeatureFeaturePlot_Seurat(seurat.mc = combined.metacells[,combined.metacells$fine_celltype %in% c("T_reg","Tex_CD8","Tnaive_CD8","Naive_T_cells","CD4_CD25posFOXP3neg")],
                                    feature_x = c("Cd4","Cd4"),
                                    feature_y = c("Cd8a","Cd8a"),
                                    assays = c("RNA","RNA"),color.use = c(scales::hue_pal()(4),"darkgrey"),
                                    is.normalized = T,cluster = "fine_celltype")
```



```{r}
combined.metacells <- readRDS("../../output/10xMultiomeProstateHan22/logNorm/macs2_major_type/immune_hoccomoco_motifs/combined.metacells.with.macs.peak.annotated.rd")

pfm <- readRDS('../../input/HOCCOMOCO_motifs/H12CORE_pfm.rds')

library(BiocParallel)
register(MulticoreParam(6))

combined.metacells <- AddMotifs(
  object = combined.metacells,
  genome = BSgenome.Mmusculus.UCSC.mm10,
  pfm = pfm,
  assay = "ATAC"
)

DefaultAssay(combined.metacells) <- "ATAC"

combined.metacells <- RunChromVAR(
  object = combined.metacells,
  genome = BSgenome.Mmusculus.UCSC.mm10,
  new.assay.name = "chromvar_pfm_cellranger"
)


saveRDS(combined.metacells,"../../output/10xMultiomeProstateHan22/logNorm/macs2_major_type/immune_hoccomoco_motifs/combined.metacells.with.macs.peak.annotated.rd")

```


# cross heatmap TF RNA - motif

```{r}
motif_tf_name <- read.table("../../input/HOCCOMOCO_motifs/H12CORE_motifs.tsv",header = T,sep = '\t')
rownames(motif_tf_name) <- motif_tf_name$Motif

DefaultAssay(combined.metacells) <- "chromvar_pfm_cellranger"
Idents(combined.metacells) <- "fine_celltype"

differential.activity <- FindAllMarkers(
  object = combined.metacells,
  only.pos = TRUE,
  mean.fxn = rowMeans, only.pos = T,
  fc.name = "avg_diff"
)

differential.activity <- differential.activity[differential.activity$p_val_adj< 0.05,]
differential.activity <- differential.activity[differential.activity$avg_diff>0,]

differential.activity <- differential.activity[order(differential.activity$avg_diff,decreasing = T),]

rownames(motif_tf_name) <- motif_tf_name$Motif

differential.activity$TF <- plyr::mapvalues(x=differential.activity$gene,from = motif_tf_name$Motif,to = motif_tf_name$Gene..mouse.)

head(differential.activity)

```

```{r}
Idents(combined.metacells) <- "celltype"
markers.rna <- FindAllMarkers(combined.metacells,assay = "RNA",only.pos = T)

markers.rna <- markers.rna[markers.rna$p_val_adj < 0.05,]
```


```{r fig.height=20,fig.width=4}

differential.activity$TF <- plyr::mapvalues(x=differential.activity$gene,from = motif_tf_name$Motif,to = motif_tf_name$Gene..mouse.)

differential.activity.strong <- differential.activity[differential.activity$avg_diff > 0,]

differential.activity.strong <- differential.activity.strong[differential.activity.strong$TF %in% markers.rna$gene,]

length(unique(differential.activity.strong$gene))

h.clust <- hclust(dist(x = combined.metacells[["chromvar_pfm_cellranger"]]@data[unique(differential.activity.strong$gene),]))

combined.metacells[["chromvar_pfm_cellranger"]]@data -> combined.metacells[["chromvar_pfm_cellranger"]]@scale.data
Idents(combined.metacells) <- "celltype"

DoHeatmap(combined.metacells,assay = "chromvar_pfm_cellranger",features = rownames(combined.metacells[["chromvar_pfm_cellranger"]]@data[unique(differential.activity.strong$gene),])[h.clust$order])



# combined.metacells[["chromvar_pfm_cellranger"]]@scale.data <- combined.metacells[["chromvar_pfm_cellranger"]]@data
# h.clust <- hclust(dist(x = combined.metacells[["chromvar_pfm_cellranger"]]@data))
# 
# Idents(combined.metacells) <- "fine_celltype"
# DoHeatmap(combined.metacells,assay = "chromvar_pfm_cellranger",features = rownames(combined.metacells[["chromvar_pfm_cellranger"]])[h.clust$order])
```

# cross heatmap TF RNA - motif narrow peaks

```{r}
# motif_tf_name <- read.table("../../input/HOCCOMOCO_motifs/H12CORE_motifs.tsv",header = T,sep = '\t')
# rownames(motif_tf_name) <- motif_tf_name$Motif

DefaultAssay(combined.metacells) <- "chromvar_pfm"
Idents(combined.metacells) <- "celltype"

differential.activity <- FindAllMarkers(
  object = combined.metacells,
  only.pos = TRUE,
  mean.fxn = rowMeans, 
  fc.name = "avg_diff"
)

differential.activity <- differential.activity[differential.activity$p_val_adj< 0.05,]
differential.activity <- differential.activity[differential.activity$avg_diff>0,]

differential.activity <- differential.activity[order(differential.activity$avg_diff,decreasing = T),]

rownames(motif_tf_name) <- motif_tf_name$Motif

differential.activity$TF <- plyr::mapvalues(x=differential.activity$gene,from = motif_tf_name$Motif,to = motif_tf_name$Gene..mouse.)

head(differential.activity)

```




```{r fig.height=6,fig.width=4}

differential.activity$TF <- plyr::mapvalues(x=differential.activity$gene,from = motif_tf_name$Motif,to = motif_tf_name$Gene..mouse.)

differential.activity.strong <- differential.activity[differential.activity$avg_diff > 5,]

differential.activity.strong <- differential.activity.strong[differential.activity.strong$TF %in% markers.rna$gene,]

length(unique(differential.activity.strong$gene))

h.clust <- hclust(dist(x = combined.metacells[["chromvar_pfm"]]@data[unique(differential.activity.strong$gene),]))

combined.metacells[["chromvar_pfm"]]@data -> combined.metacells[["chromvar_pfm"]]@scale.data
Idents(combined.metacells) <- "celltype"

DoHeatmap(combined.metacells,assay = "chromvar_pfm",features = rownames(combined.metacells[["chromvar_pfm"]]@data[unique(differential.activity.strong$gene),])[h.clust$order])



# combined.metacells[["chromvar_pfm_cellranger"]]@scale.data <- combined.metacells[["chromvar_pfm_cellranger"]]@data
# h.clust <- hclust(dist(x = combined.metacells[["chromvar_pfm_cellranger"]]@data))
# 
# Idents(combined.metacells) <- "fine_celltype"
# DoHeatmap(combined.metacells,assay = "chromvar_pfm_cellranger",features = rownames(combined.metacells[["chromvar_pfm_cellranger"]])[h.clust$order])
```



## Analysis of Neutrophils subtype at the RNA level

```{r}
Idents(combined.metacells) <- "fine_celltype"

markers.rna.neutro <- FindAllMarkers(combined.metacells[,combined.metacells$fine_celltype %in% c("Neutro_inf_high","Neutro_inf_low","Neutro_Siglecf_high")],assay = "RNA",only.pos = T)

markers.rna.neutro <- markers.rna.neutro[markers.rna.neutro$p_val_adj < 0.05,]

markers.rna.neutro[markers.rna.neutro$cluster == "Neutro_inf_low",]

write.csv(markers.rna.neutro,"marker.rna.neutro.csv")
```

## Motif level


## More precise analysis in between Neutrophils subtypes
```{r}

neutro <- combined.metacells[,combined.metacells$fine_celltype %in% c("Neutro_inf_high","Neutro_inf_low","Neutro_Siglecf_high")]

DefaultAssay(neutro) <- "chromvar_pfm"

Idents(neutro) <- "fine_celltype"

differential.activity.neutro <- FindAllMarkers(
  object = neutro,
  only.pos = TRUE,
  mean.fxn = rowMeans, 
  fc.name = "avg_diff"
)

differential.activity.neutro <- differential.activity.neutro[differential.activity.neutro$p_val_adj< 0.05,]
differential.activity.neutro <- differential.activity.neutro[order(differential.activity.neutro$avg_diff,decreasing = T),]

#name.conversion <- combined.metacells[["peaks"]]@motifs@motif.names

# differential.activity.neutro$TF <- plyr::mapvalues(x=differential.activity.neutro$gene,
#                                                    from = names(unlist(combined.metacells[["peaks"]]@motifs@motif.names)),
#                                                    to = as.vector(unlist(combined.metacells[["peaks"]]@motifs@motif.names)))

head(differential.activity.neutro)

differential.activity.neutro

```


```{r fig.height=4,fig.width=4}
differential.activity.neutro$TF <- plyr::mapvalues(x=differential.activity.neutro$gene,from = motif_tf_name$Motif,to = motif_tf_name$Gene..mouse.)

differential.activity.neutro.strong <- differential.activity.neutro[differential.activity.neutro$avg_diff > 0,]

differential.activity.neutro.strong <- differential.activity.neutro.strong[differential.activity.neutro.strong$TF %in% markers.rna.neutro$gene,]

length(unique(differential.activity.neutro.strong$gene))


neutro <- ScaleData(neutro)

h.clust <- hclust(dist(x = neutro[["chromvar_pfm"]]@scale.data[unique(differential.activity.neutro.strong$gene),]))

Idents(neutro) <- "fine_celltype"
DoHeatmap(neutro,assay = "chromvar_pfm",features = rownames(neutro[["chromvar_pfm"]]@scale.data[unique(differential.activity.neutro.strong$gene),])[h.clust$order])

```

```{r}
VlnPlot(combined.metacells[,combined.metacells$fine_celltype %in% c("Neutro_inf_high","Neutro_inf_low","Neutro_Siglecf_high")],features = c("Ccl3","Cd53"))
```
```{r}
markers.rna.neutro <- FindAllMarkers(combined.metacells[,combined.metacells$fine_celltype %in% c("Neutro_inf_low","Neutro_Siglecf_high")],assay = "RNA",only.pos = T)

markers.rna.neutro <- markers.rna.neutro[markers.rna.neutro$p_val_adj < 0.05,]

markers.rna.neutro[markers.rna.neutro$cluster == "Neutro_inf_low",]
```
```{r}
FeaturePlot(combined.metacells[,combined.metacells$fine_celltype %in% c("Neutro_inf_high","Neutro_inf_low","Neutro_Siglecf_high")],features = c("Ccl3","Cd53","Siglecf","Nfkb1"),reduction = "wnn.umap")
```

```{r}
# peaks <- readRDS("../../../output/10xMultiomeProstateHan22/logNorm/immune.peaks.rds")
# 
# 
# macs2_counts <- FeatureMatrix(
#   fragments = Fragments(chrom_assay),
#   features = peaks,
#   cells = colnames(chrom_assay)
# )
# 
# macs2_counts <- readRDS("../macs2_counts_immune.rds")
# 
# combined.metacells[["peaks"]] <- CreateChromatinAssay(
#   counts = macs2_counts,
#   genome = 'mm10',
#   min.cells = 1,
#   fragments = Fragments(chrom_assay),
#   annotation = combined.metacells[["ATAC"]]@annotations
# )
```


## Short preprocessing of the new peak assay

```{r}
DefaultAssay(combined.metacells) <- "peaks"
DefaultAssay(combined.metacells) <- "peaks"
combined.metacells <- FindTopFeatures(combined.metacells, min.cutoff = "q0")
combined.metacells <- RunTFIDF(combined.metacells)
```


## Chromvar analysis

This is done using macs2 peaks.

```{r}
# 
# library(BiocParallel)
# register(MulticoreParam(4))
# 
# # add motif information
# pfm <- getMatrixSet(
#   x = JASPAR2022,
#   opts = list(collection = "CORE", tax_group = 'vertebrates', all_versions = FALSE)
# )
# 
# # add motif information
# combined.metacells <- AddMotifs(
#   object = combined.metacells,
#   genome = BSgenome.Mmusculus.UCSC.mm10,
#   pfm = pfm,
#   assay = "peaks"
# )
# DefaultAssay(combined.metacells) <- "peaks"
# # # Scan the DNA sequence of each peak for the presence of each motif, and create a Motif object
# # pwm_set <- getMatrixSet(x = JASPAR2022, opts = list(species = 10090, all_versions = FALSE))
# # motif.matrix <- CreateMotifMatrix(features = granges(combined.metacells), pwm = pwm_set, genome = BSgenome.Mmusculus.UCSC.mm10, use.counts = FALSE)
# # motif.object <- CreateMotifObject(data = motif.matrix, pwm = pwm_set)
# # combined.metacells <- SetAssayData(combined.metacells, assay = 'ATAC', slot = 'motifs', new.data = motif.object)
# 
# # Note that this step can take 30-60 minutes
# combined.metacells <- RunChromVAR(
#   object = combined.metacells,
#   genome = BSgenome.Mmusculus.UCSC.mm10
# )

DefaultAssay(combined.metacells) <- 'chromvar_pfm'

#saveRDS(combined.metacells.chromvar.peaks,"combined.metacells.chromvar.peaks.rds")
```


```{r}
Idents(combined.metacells) <- "fine_celltype"

differential.activity <- FindAllMarkers(
  object = combined.metacells,
  only.pos = TRUE,
  mean.fxn = rowMeans,
  fc.name = "avg_diff"
)

differential.activity <- differential.activity[differential.activity$p_val_adj< 0.05,]
differential.activity <- differential.activity[order(differential.activity$avg_diff,decreasing = T),]

#name.conversion <- combined.metacells[["peaks"]]@motifs@motif.names

differential.activity$TF <- plyr::mapvalues(x=differential.activity$gene,
                                            from = names(unlist(combined.metacells[["peaks"]]@motifs@motif.names)),
                                            to = as.vector(unlist(combined.metacells[["peaks"]]@motifs@motif.names)))

head(differential.activity)


#DefaultAssay(combined.metacells) <- "peaks"

MotifPlot(
  object = combined.metacells,
  motifs = head((differential.activity[differential.activity$cluster == "B cells","gene"])),assay = "peaks",
)

```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells,
        features = head((differential.activity[differential.activity$cluster == "B cells","gene"])),
        assay = "chromvar_pfm",pt.size = 0.01)
```

```{r}
MotifPlot(
  object = combined.metacells,
  motifs = head((differential.activity[differential.activity$cluster == "NKT","gene"]),n = 6),
  assay = "peaks",
)
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells,
        features = head((differential.activity[differential.activity$cluster == "NKT","gene"])),
        assay = "chromvar_pfm",pt.size = 0.01)
```


```{r fig.height=2,fig.width=6}
MotifPlot(
  object = combined.metacells,
  motifs = head((differential.activity[differential.activity$cluster == "gd_T","gene"]),n = 3),
  assay = "peaks",
)
```
```{r fig.height=2,fig.width=6}
VlnPlot(combined.metacells,
        features = head((differential.activity[differential.activity$cluster == "gd_T","gene"]),n=3),
        assay = "chromvar_pfm",pt.size = 0.01)
```

```{r}
MotifPlot(
  object = combined.metacells,
  motifs = head((differential.activity[differential.activity$cluster == "Macro_Trem2_high","gene"]),n = 6),
  assay = "peaks",
) #All AP-1 facotrs
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells,
        features = head((differential.activity[differential.activity$cluster == "Macro_Trem2_high","gene"])),
        assay = "chromvar_pfm",pt.size = 0.01)
```


```{r fig.height=4,fig.width=6}
MotifPlot(
  object = combined.metacells,
  motifs = head((differential.activity[differential.activity$cluster == "Neutro_Siglecf_high","gene"]),n = 4),
  assay = "peaks",
) 

VlnPlot(combined.metacells,
        features = head((differential.activity[differential.activity$cluster == "Neutro_Siglecf_high","gene"]),n=4),
        assay = "chromvar_pfm",pt.size = 0.01)

VlnPlot(combined.metacells,idents = c("Neutro_inf_low","Neutro_inf_high","Neutro_Siglecf_high"),
        features = head((differential.activity[differential.activity$cluster == "Neutro_Siglecf_high","gene"]),n=4),
        assay = "chromvar_pfm",pt.size = 0.01)
```

## More precise analysis in between Neutrophils subtypes
```{r}
differential.activity.neutro <- FindAllMarkers(
  object = combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Neutro")],
  only.pos = TRUE,
  mean.fxn = rowMeans,
  fc.name = "avg_diff"
)

differential.activity.neutro <- differential.activity.neutro[differential.activity.neutro$p_val_adj< 0.05,]
differential.activity.neutro <- differential.activity.neutro[order(differential.activity.neutro$avg_diff,decreasing = T),]

#name.conversion <- combined.metacells[["peaks"]]@motifs@motif.names

# differential.activity.neutro$TF <- plyr::mapvalues(x=differential.activity.neutro$gene,
#                                                    from = names(unlist(combined.metacells[["peaks"]]@motifs@motif.names)),
#                                                    to = as.vector(unlist(combined.metacells[["peaks"]]@motifs@motif.names)))

head(differential.activity.neutro)

differential.activity.neutro

```


```{r}
differential.activity.neutro[grepl(x = differential.activity.neutro$TF,pattern = "STA"),]
```

```{r }
MotifPlot(
  object = combined.metacells,
  motifs = head((differential.activity.neutro[differential.activity.neutro$cluster == "Neutro_Siglecf_high","gene"])),
  assay = "peaks"
)
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells,idents = c("Neutro_inf_low","Neutro_inf_high","Neutro_Siglecf_high"),
        features = head((differential.activity.neutro[differential.activity.neutro$cluster == "Neutro_Siglecf_high","gene"]),n=6),
        assay = "chromvar_pfm",pt.size = 0.01)
```

Interferon type 1 signature (out of curiosity)
```{r}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Neutro")],
        features = c("Ifitm1","Ifitm2","Siglec1"),
        assay = "RNA",pt.size = 0.01)
```

```{r}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Neutro")],
        features = c("Stat1","Stat2","Irf7"),
        assay = "RNA",pt.size = 0.01)
```


## More precise analysis in between Macro subtypes
```{r}
differential.activity.macro <- FindAllMarkers(
  object = combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
  only.pos = TRUE,
  mean.fxn = rowMeans,
  fc.name = "avg_diff"
)

differential.activity.macro <- differential.activity.macro[differential.activity.macro$p_val_adj< 0.05,]
differential.activity.macro <- differential.activity.macro[order(differential.activity.macro$avg_diff,decreasing = T),]

#name.conversion <- combined.metacells[["peaks"]]@motifs@motif.names

differential.activity.macro$TF <- plyr::mapvalues(x=differential.activity.macro$gene,
                                                  from = names(unlist(combined.metacells[["peaks"]]@motifs@motif.names)),
                                                  to = as.vector(unlist(combined.metacells[["peaks"]]@motifs@motif.names)))

head(differential.activity.macro)

differential.activity.macro

```



```{r }
MotifPlot(
  object = combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
  motifs = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Trem2_high","gene"])),
  assay = "peaks"
)
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
        features = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Trem2_high","gene"])),
        assay = "chromvar",pt.size = 0.01)
```
```{r }
MotifPlot(
  object = combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
  motifs = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Cd86_high","gene"])),
  assay = "peaks"
)
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
        features = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Cd86_high","gene"])),
        assay = "chromvar",pt.size = 0.01)
```

```{r }
MotifPlot(
  object = combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
  motifs = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Fn1_high","gene"])),
  assay = "peaks"
)
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
        features = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Fn1_high","gene"])),
        assay = "chromvar",pt.size = 0.01)
```
Interferon type 1 signature (out of curiosity)
```{r}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
        features = c("Ifitm1","Ifitm2","Siglec1"),
        assay = "RNA",pt.size = 0.01)
```

```{r}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
        features = c("Stat1","Stat2","Irf7"),
        assay = "RNA",pt.size = 0.01)
```



```{r }
MotifPlot(
  object = combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
  motifs = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Fn1_high","gene"])),
  assay = "peaks"
)
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
        features = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Fn1_high","gene"])),
        assay = "chromvar",pt.size = 0.01)
```


## analysis of CD8 exhaustion
```{r}

motif_exhaustion <- FindMarkers(  object = combined.metacells,ident.1 = "Tex_CD8",ident.2 = "Tnaive_CD8",
                                  mean.fxn = rowMeans, assay = "chromvar_pfm",
                                  fc.name = "avg_diff")

motif_exhaustion <- motif_exhaustion[motif_exhaustion$p_val_adj< 0.05,]


motif_exhaustion <- motif_exhaustion[order(motif_exhaustion$avg_diff,decreasing = T),]


motif_exhaustion$TF <- plyr::mapvalues(x=rownames(motif_exhaustion),
                                       from = names(unlist(combined.metacells[["peaks"]]@motifs@motif.names)),
                                       to = as.vector(unlist(combined.metacells[["peaks"]]@motifs@motif.names)))

# 
# head(motif_exhaustion,n=20)
# 
# tail(motif_exhaustion,n=20)
```


# cross heatmap TF RNA - motif

```{r}
rownames(motif_tf_name) <- motif_tf_name$Motif

differential.activity$TF <- plyr::mapvalues(x=differential.activity$gene,from = motif_tf_name$Motif,to = motif_tf_name$Gene..mouse.)

head(differential.activity)
```
```{r fig.height=20,fig.width=4}

combined.metacells[["chromvar_pfm"]]@scale.data <- combined.metacells[["chromvar_pfm"]]@data
h.clust <- hclust(dist(x = combined.metacells[["chromvar_pfm"]]@scale.data))

Idents(combined.metacells) <- "fine_celltype"
DoHeatmap(combined.metacells,assay = "chromvar_pfm",features = rownames(combined.metacells[["chromvar_pfm"]])[h.clust$order])
```






```{r fig.height=5,fig.width=4}
differential.activity.neutro$TF <- plyr::mapvalues(x=differential.activity.neutro$gene,from = motif_tf_name$Motif,to = motif_tf_name$Gene..mouse.)

differential.activity.neutro.strong <- differential.activity.neutro[differential.activity.neutro$avg_diff > 0,]

differential.activity.neutro.strong <- differential.activity.neutro.strong[differential.activity.neutro.strong$TF %in% markers.rna.neutro$gene,]

length(unique(differential.activity.neutro.strong$gene))

neutro <- combined.metacells[,combined.metacells$fine_celltype %in% c("Neutro_inf_high","Neutro_inf_low","Neutro_Siglecf_high")]

neutro <- ScaleData(neutro)

h.clust <- hclust(dist(x = neutro[["chromvar_pfm"]]@scale.data[unique(differential.activity.neutro.strong$gene),]))

Idents(neutro) <- "fine_celltype"
DoHeatmap(neutro,assay = "chromvar_pfm",features = rownames(neutro[["chromvar_pfm"]]@scale.data[unique(differential.activity.neutro.strong$gene),])[h.clust$order])

```
```{r}
VlnPlot(neutro,unique(differential.activity.neutro.strong$gene)[h.clust$order],stack = T) + NoLegend()

VlnPlot(neutro,unique(differential.activity.neutro.strong$TF)[h.clust$order],assay = "RNA",stack = T) + NoLegend()

```
```{r}

neutro$fine_celltype <- factor(neutro$fine_celltype,levels = c("Neutro_inf_low","Neutro_inf_high","Neutro_Siglecf_high"))

Idents(neutro) <- "fine_celltype"
VlnPlot(neutro,c("NFKB1.H12CORE.0.PS.A","Nfkb1"),pt.size = 0.01)

VlnPlot(neutro,c("NFKB2.H12CORE.0.PSM.A","Nfkb2"),pt.size = 0.01)

VlnPlot(neutro,c("RUNX3.H12CORE.0.P.B","rna_Runx3"),pt.size = 0.01)

VlnPlot(neutro,c("SPI1.H12CORE.0.P.B" ,"rna_Spi1"),pt.size = 0.01)

```

# Investigate motif

```{r}
motif_tf_name["TF7L1.H12CORE.0.PM.A",]

motif_family <- unique(motif_tf_name$TF.family)
for (m in motif_family) {
  detected.motifs <- rownames(motif_tf_name[motif_tf_name$TF.family == m,])[rownames(motif_tf_name[motif_tf_name$TF.family == m,]) %in% rownames(combined.metacells)]
  if (length(detected.motifs)> 0) {
    plot(MotifPlot(
      object = combined.metacells,
      motifs = detected.motifs,
      assay = "peaks",
    )) #
  }
}

```
```{r}
m <- "C4-GATA-related {2.2.1}"
detected.motifs <- rownames(motif_tf_name[motif_tf_name$TF.family == m,])[rownames(motif_tf_name[motif_tf_name$TF.family == m,]) %in% rownames(combined.metacells)]
if (length(detected.motifs)> 0) {
  plot(MotifPlot(
    object = combined.metacells,
    motifs = detected.motifs,
    assay = "peaks",
  )) #
}

```

