---
title: "Analysis of immune cells from prostate tumor microenvironment"
author: "Leonard Herault"
date: '2024-01-04'
output: html_document
---

## Workflow used

Multiomics metacell were identified in each sample using SCimplify by combining log norm RNA and cell ranger atac peaks (same peaks as in the orginal study).
RNA and ATAC modality were integrated separately using a similar workflow as in the original study at the single cell level.
Seurat RPCA was used to integrate RNA, Harmony for ATAC.
As in the original study, a WNN graph was computed (here for the metacells), using the 2 integrated modality.
Major cell type corresponding to original clusters were identified.

After this step a new peak calling was performed in each major type using macs2.
This allow us to use more precise and narrow peaks for downstream analysis of the ATAC modality (motif analysis, DA peaks)
**Note that here we won't use these new peaks to compute a new multimodal latent space.**

Here we analyzed more deeply the immune clusters of metacells.
First we will recompute a WNN for the immune metacells (from the corrected LSI + PCA computed for all metacells).


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Environment loading

```{r}
library(Seurat)
library(dplyr)
library(Matrix)
library(ggplot2)
library(cowplot)
library(EnsDb.Mmusculus.v79)
library(Signac)
library(S4Vectors)
library(patchwork)
library(JASPAR2022)
library(TFBSTools)
library(BSgenome.Mmusculus.UCSC.mm10)
library(SuperCellMultiomics)
```

## Loading of data

We load the integrated data of immune cells with 2 ATAC slot:

* ATAC : based on the second peak calling with mac2

```{r}
combined.metacells <- readRDS("../../output/10xMultiomeProstateHan22/logNorm/macs2_major_type/immune.combined.metacells.rds")
```


First LSI component is correlated with sequencing depth. As previously, we won't use it for computing the wnn 
```{r}
DepthCor(combined.metacells)
```

We compute the the new WNN for immune metacells.
We use this WNN for clustering at different resolution and UMAP projection.

```{r}
combined.metacells <- FindMultiModalNeighbors(combined.metacells, 
                                              reduction.list = list("integrated_pca", "integrated_lsi"), 
                                              dims.list = list(1:50, 2:50))

combined.metacells <- FindClusters(combined.metacells, 
                                   resolution = c(c(1:9)*0.1),
                                   graph.name = "wsnn") 

combined.metacells <- RunUMAP(combined.metacells,
                              nn.name = "weighted.nn", 
                              reduction.name = "wnn.umap", 
                              reduction.key = "wnnUMAP_")


combined.metacells <- RunUMAP(combined.metacells, 
                              reduction  = "integrated_lsi", 
                              reduction.name = "atac.umap", 
                              reduction.key = "atacUMAP_",
                              dims = c(2:50))

combined.metacells <- RunUMAP(combined.metacells, 
                              reduction  = "integrated_pca", 
                              reduction.name = "rna.umap", 
                              reduction.key = "rnaUMAP_",
                              dims = c(1:50))


```

PLot of the results

```{r fig.height= 2.5,fig.width=2.5}
DimPlot(combined.metacells,reduction = "wnn.umap")
DimPlot(combined.metacells,reduction = "wnn.umap",group.by = "celltype")
DimPlot(combined.metacells,reduction = "wnn.umap",group.by = "wsnn_res.0.3")
DimPlot(combined.metacells,reduction = "rna.umap",group.by = "wsnn_res.0.3")
DimPlot(combined.metacells,reduction = "atac.umap",group.by = "wsnn_res.0.3")

VlnPlot(combined.metacells,"ATAC.weight",sort = T,group.by = "wsnn_res.0.3")

DimPlot(combined.metacells,reduction = "wnn.umap",group.by = "wsnn_res.0.9",label = T)

DimPlot(combined.metacells,reduction = "wnn.umap",group.by = "wsnn_res.0.4",label = T)

```

Plot of major types and their markers

```{r}
DefaultAssay(combined.metacells) <- "RNA"
FeaturePlot(combined.metacells,c("S100a9","Cd3e","Cd19","C1qa"),reduction = "wnn.umap")
VlnPlot(combined.metacells,features = c("S100a9","Cd3e","Cd19","C1qa"),pt.size = 0.01,group.by = "celltype",ncol = 2)
```

We retain the 0.4 resolution separating DC (Ciita, Flt3) from macrophages.

```{r, fig.height=4,fig.width=3}
Idents(combined.metacells) <- "wsnn_res.0.4"

VlnPlot(combined.metacells,features = c("Cd8a","Cd4","Cd19",
                                        "Clec10a","Ciita","Flt3",
                                        "Trem2","Gpnmb","Lrp12",
                                        "Fn1","Cd86",
                                        "Cxcr2","Mreg"),pt.size = 0.001,ncol = 3)
```









```{r,}


```

We can make a marker analysis of this first clustering.
```{r}
DefaultAssay(combined.metacells) <- "RNA"
# markers <- FindAllMarkers(combined.metacells,only.pos = T)
# markers <- markers[markers$p_val_adj < 0.05,]
# head(markers)
```


## Finner annotation

We can 
# Neutrophils

```{r}
VlnPlot(combined.metacells[,combined.metacells$wsnn_res.0.4 %in% c(0,2,6)], features = c("Nfkb1","Hdc","Il1b","Siglecf","Trem1","Cxcr2"),group.by = "wsnn_res.0.4")
```



```{r}
FeaturePlot(combined.metacells[,combined.metacells$wsnn_res.0.4 %in% c(0,2,6)],
            features = c("Nfkb1","Hdc","Il1b","Siglecf","Trem1","Cxcr2","P2rx7","Mreg"),reduction = "wnn.umap")

```


```{r}

## NK and CD8 T cells
Idents(combined.metacells) <- 'wsnn_res.0.4'
combined.metacells <- FindSubCluster(combined.metacells,cluster = 5,resolution = 0.6,graph.name = "wsnn")
DimPlot(combined.metacells[,combined.metacells$wsnn_res.0.4 == 5],group.by = 'sub.cluster',reduction = "wnn.umap",label = T)

```
```{r fig.width=3,fig.height=3}
VlnPlot(combined.metacells[,combined.metacells$wsnn_res.0.4 %in% c(5)],features = c("Cd8a","Cd4","Cd3g","Tox","Tcf7","Il7r","Ncr1","Klrb1c", "Klrb1b"),group.by="sub.cluster")
```


```{r}
Idents(combined.metacells) <- "sub.cluster"

DimPlot(combined.metacells,reduction = "wnn.umap",label = T,repel = T)

```






```{r}
DimPlot(combined.metacells,reduction = "wnn.umap")
combined.metacells <- RenameIdents(combined.metacells,
                                   "0" = "Neutro_inf_low",
                                   "1" = "Macro_Fn1_high_DC",
                                   "2" = "Neutro_inf_high",
                                   "3" = "Macro_Cd86_high",
                                   "4" = "Macro_Trem2_high",
                                   "5_0" = "Tex_CD8",
                                   "5_1" = "Tnaive_CD8",
                                   "5_2" = "NKT",
                                   "6" = "Neutro_Siglecf_high",
                                   "7" = "CD4",
                                   "8" = "B cells"
)

combined.metacells$celltype.l2 <- Idents(combined.metacells)

DimPlot(combined.metacells,reduction = "wnn.umap",label = T,repel = T)

combined.metacells$fine_celltype = Idents(combined.metacells)
```
#Subdivide CD4

# CD4
```{r}
Idents(combined.metacells) <- "wsnn_res.0.4"

combined.metacells <- FindSubCluster(combined.metacells,cluster = 7,resolution = 0.8,graph.name = "wsnn")

DimPlot(combined.metacells[,combined.metacells$wsnn_res.0.4 == 7],reduction = "wnn.umap",group.by = "sub.cluster")

FeaturePlot(combined.metacells[,combined.metacells$wsnn_res.0.4 == 7],reduction = "wnn.umap",features  = c("Cd8a","Cd4"))
```
```{r}
FeatureScatter(combined.metacells[,combined.metacells$wsnn_res.0.4 == 7],feature1 = "Cd8a", feature2 = "Cd4",group.by = "sub.cluster")


```
```{r fig.height=3,fig.width=4}
supercell_FeatureFeaturePlot_Seurat(seurat.mc = combined.metacells[,combined.metacells$wsnn_res.0.4 == 7],feature_x = c("Cd4","Cd4"),feature_y = c("Cd8a","Cd8a"),assays = c("RNA","RNA"),is.normalized = T)
```



```{r}
Idents(combined.metacells) <- "sub.cluster"

VlnPlot(combined.metacells[,combined.metacells$wsnn_res.0.4 %in% c(7)],features = c("Cd8a","Runx3","Il7r","Tcf7","Cd4","Foxp3","Il2ra","Pdcd1","Trdc","Tcrg-C1","Tcrg-C2"),group.by = "sub.cluster")
```


```{r}
Idents(combined.metacells) <- "sub.cluster"
combined.metacells <- RenameIdents(combined.metacells,
                                   "7_0" = "Naive_T_cells",
                                   "7_1" = "T_reg",
                                   "7_2" = "gd_T"
)
levels(combined.metacells$fine_celltype) <- c(levels(combined.metacells$fine_celltype),c("Naive_T_cells","T_reg",'gd_T'))
combined.metacells$fine_celltype[combined.metacells$fine_celltype == "CD4"] <- Idents(combined.metacells[,combined.metacells$fine_celltype == "CD4"])

DimPlot(combined.metacells,reduction = "wnn.umap",label = T,repel = T,group.by = "fine_celltype")

```

# Get DC

```{r}
Idents(combined.metacells) <- 'wsnn_res.0.4'
combined.metacells <- FindSubCluster(combined.metacells,cluster = 1,resolution = 0.1,graph.name = "wsnn")
DimPlot(combined.metacells[,combined.metacells$wsnn_res.0.4 == 1],group.by = 'sub.cluster',reduction = "wnn.umap",label = T)

```
```{r}
VlnPlot(combined.metacells[,combined.metacells$wsnn_res.0.4 %in% c(1)],features = c("Clec10a","Ciita","Flt3","C1qa","Fn1"),group.by = "sub.cluster")

```
```{r}
Idents(combined.metacells) <- "sub.cluster"
combined.metacells <- RenameIdents(combined.metacells,
                                   "1_0" = "Macro_Fn1_high",
                                   "1_1" = "DC")
levels(combined.metacells$fine_celltype) <- c(levels(combined.metacells$fine_celltype),c("Macro_Fn1_high","DC"))
combined.metacells$fine_celltype[combined.metacells$wsnn_res.0.4 %in% c(1)] <- Idents(combined.metacells)[combined.metacells$wsnn_res.0.4 %in% c(1)]
```


```{r fig.height=2.5,fig.width=4}

mycolors <- c('#E5D2DD', '#53A85F', '#F1BB72', '#F3B1A0', '#D6E7A3', '#57C3F3', '#476D87',
              '#E95C59', '#E59CC4', '#AB3282', '#BD956A', '#8C549C',
              '#9FA3A8', '#58A4C3', "#b20000",'#E4C755', '#F7F398',
              '#AA9A59', '#E63863', '#E39A35', '#C1E6F3', '#6778AE', '#91D0BE', '#B53E2B',
              '#712820', '#DCC1DD', '#CCE0F5', '#CCC9E6', '#625D9E', '#68A180', '#3A6963',
              '#968175')

DimPlot(combined.metacells,reduction = "wnn.umap",label = T,repel = T,group.by = "celltype") + ggtitle("original celltype")



DimPlot(combined.metacells,reduction = "wnn.umap",label = T,repel = T, cols = mycolors,group.by = "fine_celltype")

```


```{r fig.height=5, fig.width=12}

DefaultAssay(combined.metacells) <- "RNA"
genes <- c("S100a9","Nfkb1","Siglecf","C1qa","Fn1","Cd86","Trem2","Flt3","Cd3g","Klrb1c","Cd8a","Tox","Tcf7","Cd4","Foxp3","Il2ra","Tcrg-C1","Cd19")

combined.metacells$fine_celltype <- factor(combined.metacells$fine_celltype,
                                           levels = c("","Neutro_inf_high","Neutro_inf_low","Neutro_Siglecf_high",
                                                      "Macro_Fn1_high","Macro_Cd86_high","Macro_Trem2_high",
                                                      "DC","NKT","Tex_CD8","Tnaive_CD8","Naive_T_cells",
                                                      "T_reg","CD4_CD25posFOXP3neg","gd_T","B cells")) 

VlnPlot(object = combined.metacells,features = genes,stack = T,group.by = "fine_celltype",fill.by= "ident",cols = mycolors,same.y.lims = F)  + NoLegend() + theme(axis.title.y = element_blank())
```

```{r}
Idents(combined.metacells) <- "fine_celltype"
supercell_FeatureFeaturePlot_Seurat(seurat.mc = combined.metacells[,combined.metacells$fine_celltype %in% c("T_reg","Tex_CD8","Tnaive_CD8","Naive_T_cells")],
                                    feature_x = c("Cd4","Cd4"),
                                    feature_y = c("Cd8a","Cd8a"),
                                    assays = c("RNA","RNA"),
                                    is.normalized = T,cluster = "fine_celltype")
```






## Analysis of Neutrophils subtype at the RNA level

```{r}
Idents(combined.metacells) <- "fine_celltype"

markers.rna.neutro <- FindAllMarkers(combined.metacells[,combined.metacells$fine_celltype %in% c("Neutro_inf_high","Neutro_inf_low","Neutro_Siglecf_high")],assay = "RNA",only.pos = T)

markers.rna.neutro <- markers.rna.neutro[markers.rna.neutro$p_val_adj < 0.05,]

markers.rna.neutro[markers.rna.neutro$cluster == "Neutro_inf_low",]
```

```{r}
VlnPlot(combined.metacells[,combined.metacells$fine_celltype %in% c("Neutro_inf_high","Neutro_inf_low","Neutro_Siglecf_high")],features = c("Ccl3","Cd53"))
```
```{r}
markers.rna.neutro <- FindAllMarkers(combined.metacells[,combined.metacells$fine_celltype %in% c("Neutro_inf_low","Neutro_Siglecf_high")],assay = "RNA",only.pos = T)

markers.rna.neutro <- markers.rna.neutro[markers.rna.neutro$p_val_adj < 0.05,]

markers.rna.neutro[markers.rna.neutro$cluster == "Neutro_inf_low",]
```
```{r}
FeaturePlot(combined.metacells[,combined.metacells$fine_celltype %in% c("Neutro_inf_high","Neutro_inf_low","Neutro_Siglecf_high")],features = c("Ccl3","Cd53","Siglecf","Nfkb1"),reduction = "wnn.umap")
```

```{r}
# peaks <- readRDS("../../../output/10xMultiomeProstateHan22/logNorm/immune.peaks.rds")
# 
# 
# macs2_counts <- FeatureMatrix(
#   fragments = Fragments(chrom_assay),
#   features = peaks,
#   cells = colnames(chrom_assay)
# )
# 
# macs2_counts <- readRDS("../macs2_counts_immune.rds")
# 
# combined.metacells[["peaks"]] <- CreateChromatinAssay(
#   counts = macs2_counts,
#   genome = 'mm10',
#   min.cells = 1,
#   fragments = Fragments(chrom_assay),
#   annotation = combined.metacells[["ATAC"]]@annotations
# )
```


## Short preprocessing of the new peak assay

```{r}
DefaultAssay(combined.metacells) <- "peaks"




DefaultAssay(combined.metacells) <- "peaks"
combined.metacells <- FindTopFeatures(combined.metacells, min.cutoff = "q0")
combined.metacells <- RunTFIDF(combined.metacells)
```


## Chromvar analysis

This is done using macs2 peaks.

```{r}

library(BiocParallel)
register(MulticoreParam(4))

# add motif information
pfm <- getMatrixSet(
  x = JASPAR2022,
  opts = list(collection = "CORE", tax_group = 'vertebrates', all_versions = FALSE)
)

# add motif information
combined.metacells <- AddMotifs(
  object = combined.metacells,
  genome = BSgenome.Mmusculus.UCSC.mm10,
  pfm = pfm,
  assay = "peaks"
)
DefaultAssay(combined.metacells) <- "peaks"
# # Scan the DNA sequence of each peak for the presence of each motif, and create a Motif object
# pwm_set <- getMatrixSet(x = JASPAR2022, opts = list(species = 10090, all_versions = FALSE))
# motif.matrix <- CreateMotifMatrix(features = granges(combined.metacells), pwm = pwm_set, genome = BSgenome.Mmusculus.UCSC.mm10, use.counts = FALSE)
# motif.object <- CreateMotifObject(data = motif.matrix, pwm = pwm_set)
# combined.metacells <- SetAssayData(combined.metacells, assay = 'ATAC', slot = 'motifs', new.data = motif.object)

# Note that this step can take 30-60 minutes
combined.metacells <- RunChromVAR(
  object = combined.metacells,
  genome = BSgenome.Mmusculus.UCSC.mm10
)

DefaultAssay(combined.metacells) <- 'chromvar'

#saveRDS(combined.metacells.chromvar.peaks,"combined.metacells.chromvar.peaks.rds")
```


```{r}
Idents(combined.metacells) <- "fine_celltype"

differential.activity <- FindAllMarkers(
  object = combined.metacells,
  only.pos = TRUE,
  mean.fxn = rowMeans,
  fc.name = "avg_diff"
)

differential.activity <- differential.activity[differential.activity$p_val_adj< 0.05,]
differential.activity <- differential.activity[order(differential.activity$avg_diff,decreasing = T),]

#name.conversion <- combined.metacells[["peaks"]]@motifs@motif.names

differential.activity$TF <- plyr::mapvalues(x=differential.activity$gene,
                                            from = names(unlist(combined.metacells[["peaks"]]@motifs@motif.names)),
                                            to = as.vector(unlist(combined.metacells[["peaks"]]@motifs@motif.names)))

head(differential.activity)


#DefaultAssay(combined.metacells) <- "peaks"

MotifPlot(
  object = combined.metacells,
  motifs = head((differential.activity[differential.activity$cluster == "B cells","gene"])),assay = "peaks",
)

```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells,
        features = head((differential.activity[differential.activity$cluster == "B cells","gene"])),
        assay = "chromvar",pt.size = 0.01)
```

```{r}
MotifPlot(
  object = combined.metacells,
  motifs = head((differential.activity[differential.activity$cluster == "NKT","gene"]),n = 5),
  assay = "peaks",
)
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells,
        features = head((differential.activity[differential.activity$cluster == "NKT","gene"])),
        assay = "chromvar",pt.size = 0.01)
```


```{r fig.height=2,fig.width=6}
MotifPlot(
  object = combined.metacells,
  motifs = head((differential.activity[differential.activity$cluster == "gd_T","gene"]),n = 3),
  assay = "peaks",
)
```
```{r fig.height=2,fig.width=6}
VlnPlot(combined.metacells,
        features = head((differential.activity[differential.activity$cluster == "gd_T","gene"]),n=3),
        assay = "chromvar",pt.size = 0.01)
```

```{r}
MotifPlot(
  object = combined.metacells,
  motifs = head((differential.activity[differential.activity$cluster == "Macro_Trem2_high","gene"]),n = 6),
  assay = "peaks",
) #All AP-1 facotrs
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells,
        features = head((differential.activity[differential.activity$cluster == "Macro_Trem2_high","gene"])),
        assay = "chromvar",pt.size = 0.01)
```


```{r fig.height=4,fig.width=6}
MotifPlot(
  object = combined.metacells,
  motifs = head((differential.activity[differential.activity$cluster == "Neutro_Siglecf_high","gene"]),n = 4),
  assay = "peaks",
) 

VlnPlot(combined.metacells,
        features = head((differential.activity[differential.activity$cluster == "Neutro_Siglecf_high","gene"]),n=4),
        assay = "chromvar",pt.size = 0.01)

VlnPlot(combined.metacells,idents = c("Neutro_inf_low","Neutro_inf_high","Neutro_Siglecf_high"),
        features = head((differential.activity[differential.activity$cluster == "Neutro_Siglecf_high","gene"]),n=4),
        assay = "chromvar",pt.size = 0.01)
```

## More precise analysis in between Neutrophils subtypes
```{r}
differential.activity.neutro <- FindAllMarkers(
  object = combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Neutro")],
  only.pos = TRUE,
  mean.fxn = rowMeans,
  fc.name = "avg_diff"
)

differential.activity.neutro <- differential.activity.neutro[differential.activity.neutro$p_val_adj< 0.05,]
differential.activity.neutro <- differential.activity.neutro[order(differential.activity.neutro$avg_diff,decreasing = T),]

#name.conversion <- combined.metacells[["peaks"]]@motifs@motif.names

differential.activity.neutro$TF <- plyr::mapvalues(x=differential.activity.neutro$gene,
                                                   from = names(unlist(combined.metacells[["peaks"]]@motifs@motif.names)),
                                                   to = as.vector(unlist(combined.metacells[["peaks"]]@motifs@motif.names)))

head(differential.activity.neutro)

differential.activity.neutro

```



```{r }
MotifPlot(
  object = combined.metacells,
  motifs = head((differential.activity.neutro[differential.activity.neutro$cluster == "Neutro_Siglecf_high","gene"])),
  assay = "peaks"
)
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells,idents = c("Neutro_inf_low","Neutro_inf_high","Neutro_Siglecf_high"),
        features = head((differential.activity.neutro[differential.activity.neutro$cluster == "Neutro_Siglecf_high","gene"]),n=6),
        assay = "chromvar",pt.size = 0.01)
```

Interferon type 1 signature (out of curiosity)
```{r}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Neutro")],
        features = c("Ifitm1","Ifitm2","Siglec1"),
        assay = "RNA",pt.size = 0.01)
```

```{r}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Neutro")],
        features = c("Stat1","Stat2","Irf7"),
        assay = "RNA",pt.size = 0.01)
```


## More precise analysis in between Macro subtypes
```{r}
differential.activity.macro <- FindAllMarkers(
  object = combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
  only.pos = TRUE,
  mean.fxn = rowMeans,
  fc.name = "avg_diff"
)

differential.activity.macro <- differential.activity.macro[differential.activity.macro$p_val_adj< 0.05,]
differential.activity.macro <- differential.activity.macro[order(differential.activity.macro$avg_diff,decreasing = T),]

#name.conversion <- combined.metacells[["peaks"]]@motifs@motif.names

differential.activity.macro$TF <- plyr::mapvalues(x=differential.activity.macro$gene,
                                                  from = names(unlist(combined.metacells[["peaks"]]@motifs@motif.names)),
                                                  to = as.vector(unlist(combined.metacells[["peaks"]]@motifs@motif.names)))

head(differential.activity.macro)

differential.activity.macro

```



```{r }
MotifPlot(
  object = combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
  motifs = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Trem2_high","gene"])),
  assay = "peaks"
)
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
        features = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Trem2_high","gene"])),
        assay = "chromvar",pt.size = 0.01)
```
```{r }
MotifPlot(
  object = combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
  motifs = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Cd86_high","gene"])),
  assay = "peaks"
)
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
        features = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Cd86_high","gene"])),
        assay = "chromvar",pt.size = 0.01)
```

```{r }
MotifPlot(
  object = combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
  motifs = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Fn1_high","gene"])),
  assay = "peaks"
)
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
        features = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Fn1_high","gene"])),
        assay = "chromvar",pt.size = 0.01)
```
Interferon type 1 signature (out of curiosity)
```{r}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
        features = c("Ifitm1","Ifitm2","Siglec1"),
        assay = "RNA",pt.size = 0.01)
```

```{r}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
        features = c("Stat1","Stat2","Irf7"),
        assay = "RNA",pt.size = 0.01)
```



```{r }
MotifPlot(
  object = combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
  motifs = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Fn1_high","gene"])),
  assay = "peaks"
)
```
```{r fig.height=4,fig.width=6}
VlnPlot(combined.metacells[,startsWith(as.vector(combined.metacells$fine_celltype),"Macro")],
        features = head((differential.activity.macro[differential.activity.macro$cluster == "Macro_Fn1_high","gene"])),
        assay = "chromvar",pt.size = 0.01)
```


## analysis of CD8 exhaustion
```{r}

motif_exhaustion <- FindMarkers(  object = combined.metacells,ident.1 = "Tex_CD8",ident.2 = "Tnaive_CD8",
                                  mean.fxn = rowMeans, assay = "chromvar",
                                  fc.name = "avg_diff")

motif_exhaustion <- motif_exhaustion[motif_exhaustion$p_val_adj< 0.05,]


motif_exhaustion <- motif_exhaustion[order(motif_exhaustion$avg_diff,decreasing = T),]


motif_exhaustion$TF <- plyr::mapvalues(x=rownames(motif_exhaustion),
                                       from = names(unlist(combined.metacells[["peaks"]]@motifs@motif.names)),
                                       to = as.vector(unlist(combined.metacells[["peaks"]]@motifs@motif.names)))


head(motif_exhaustion,n=20)

tail(motif_exhaustion,n=20)
```



