---
title: "Analysis of immune cells from prostate tumor microenvironment"
author: "Leonard Herault"
date: '2024-01-04'
output: html_document
---

## Workflow used

Multiomics metacell were identified in each sample using SCimplify by combining log norm RNA and cell ranger atac peaks (same peaks as in the orginal study).
RNA and ATAC modality were integrated separately using a similar workflow as in the original study at the single cell level.
Seurat RPCA was used to integrate RNA, Harmony for ATAC.
As in the original study, a WNN graph was computed (here for the metacells), using the 2 integrated modality.
Major cell type corresponding to original clusters were identified.

After this step a new peak calling was performed in each major type using macs2.
This allow us to use more precise and narrow peaks for downstream analysis of the ATAC modality (motif analysis, DA peaks)
**Note that here we won't use these new peaks to compute a new multimodal latent space.**

Here we analyzed more deeply the immune clusters of metacells.
First we will recompute a WNN for the immune metacells (from the corrected LSI + PCA computed for all metacells).


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Environment loading

```{r}
library(Seurat)
library(dplyr)
library(Matrix)
library(ggplot2)
library(cowplot)
library(EnsDb.Mmusculus.v79)
library(Signac)
library(S4Vectors)
library(patchwork)
#library(JASPAR2022)
library(TFBSTools)
library(BSgenome.Mmusculus.UCSC.mm10)
```

## Loading of data

We load the integrated data of immune cells with 2 ATAC slot:

* ATAC : based on cell ranger peaks, used for data integration and clustering
* peaks : based on the second peak calling with mac2, here only use for downstream analysis of the ATAC modality

```{r}
combined.metacells.all <- readRDS("../../output/10xMultiomeProstateHan22/logNorm/macs2_major_type/immune_hoccomoco_motifs/combined.metacells.with.macs.peak.rds")

combined.metacells.all <- FindMultiModalNeighbors(combined.metacells.all, 
                                              reduction.list = list("integrated_pca", "integrated_lsi"), 
                                              dims.list = list(1:50, 2:50))

combined.metacells.all <- FindClusters(combined.metacells.all, 
                                   resolution = c(c(1:9)*0.1),
                                   graph.name = "wsnn") 

combined.metacells.all <- RunUMAP(combined.metacells.all,
                              nn.name = "weighted.nn", 
                              reduction.name = "wnn.umap", 
                              reduction.key = "wnnUMAP_")


DimPlot(combined.metacells.all,reduction = "wnn.umap")


Idents(combined.metacells.all) <- "wsnn_res.0.4" 
DimPlot(combined.metacells.all,reduction = "wnn.umap", label = T)
DimPlot(combined.metacells.all,reduction = "wnn.umap", label = T,group.by = "celltype")

FeaturePlot(combined.metacells.all,"Siglecf")

combined.metacells <- combined.metacells.all[,combined.metacells.all$wsnn_res.0.4 == c(0,3,5)]


combined.metacells
DimPlot(combined.metacells,reduction = "wnn.umap", group.by = "wsnn_res.0.4")

```



```{r}
pfm <- readRDS("../../input/HOCCOMOCO_motifs/H12CORE_pfm.rds")

combined.metacells <- AddMotifs(
  object = combined.metacells,
  genome = BSgenome.Mmusculus.UCSC.mm10,
  pfm = pfm,
  assay = "peaks"
)

DefaultAssay(combined.metacells) <- "peaks"

combined.metacells <- RunChromVAR(
  object = combined.metacells,
  genome = BSgenome.Mmusculus.UCSC.mm10,
  new.assay.name = "chromvar_pfm"
)
```
```{r}
DimPlot(combined.metacells,reduction = "wnn.umap")
```

```{r}
# combined.metacells <- FindMultiModalNeighbors(combined.metacells, 
#                                               reduction.list = list("integrated_pca", "integrated_lsi"), 
#                                               dims.list = list(1:50, 2:50))
# 
# combined.metacells <- FindClusters(combined.metacells, 
#                                    resolution = c(c(1:5)*0.1),
#                                    graph.name = "wsnn") 

# combined.metacells <- RunUMAP(combined.metacells,
#                               nn.name = "weighted.nn", 
#                               reduction.name = "wnn.umap", 
#                               reduction.key = "wnnNeutroUMAP_")

Idents(combined.metacells) <- "wsnn_res.0.4" 


DimPlot(combined.metacells,reduction = "wnn.umap")

```


First LSI component is correlated with sequencing depth. As previously, we won't use it for computing the wnn 
```{r}
FeaturePlot(combined.metacells,"Siglecf")
```
```{r fig.height=1.5,fig.width=2.7}
combined.metacells$Siglecf_exp <- "Siglecf_low"
combined.metacells$Siglecf_exp[combined.metacells$wsnn_res.0.4 == 5] <- "Siglecf_high"
Idents(combined.metacells) <- "Siglecf_exp"
DimPlot(combined.metacells) + theme(legend.position = c(0.5,0.5))


motif_Siglecf_exp<- FindMarkers(  object = combined.metacells,ident.1 = "Siglecf_high",ident.2 = "Siglecf_low",
                                  mean.fxn = rowMeans, assay = "chromvar_pfm",
                                  fc.name = "avg_diff")

motif_Siglecf_exp <- motif_Siglecf_exp[motif_Siglecf_exp$p_val_adj< 0.05,]

motif_Siglecf_exp
write.csv(motif_Siglecf_exp,"motif_Siglecf_high_vs_low.csv")
```

# save
```{r}
saveRDS(combined.metacells,"neutro_prostate_han_2022_sobj.RDS")
```

```{r}
VlnPlot(combined.metacells,features = c("STA5A.H12CORE.0.P.B","rna_Siglecf"))
```
```{r fig.width=3,fig.height=2}
p1 <- FeaturePlot(
  object = combined.metacells,
  features = "STA5A.H12CORE.0.P.B",
  min.cutoff = 'q10',
  max.cutoff = 'q90',
) + theme_void() + xlim(c(-12.5,-5))


p2 <- FeaturePlot(
  object = combined.metacells,
  features = "STA5A.H12CORE.0.P.B",
  min.cutoff = 'q10',
  max.cutoff = 'q90',
) + theme_void() + xlim(c(-12.5,-5))

p2 <- FeaturePlot(
  object = combined.metacells,
  features = "rna_Siglecf",
  min.cutoff = 'q10',
  max.cutoff = 'q90',
)+ theme_void() + xlim(c(-12.5,-5))

p3 <- FeaturePlot(
  object = combined.metacells,
  features = "NFAT5.H12CORE.0.SM.B",
  min.cutoff = 'q10',
  max.cutoff = 'q90',
)+ theme_void() + xlim(c(-12.5,-5))

p4 <- FeaturePlot(
  object = combined.metacells,
  features = "RUNX3.H12CORE.0.P.B",
  min.cutoff = 'q10',
  max.cutoff = 'q90',
)+ theme_void() + xlim(c(-12.5,-5))


p5 <- FeaturePlot(
  object = combined.metacells,
  features = "SMAD4.H12CORE.0.P.B",
  min.cutoff = 'q10',
  max.cutoff = 'q90',
)+ theme_void() + xlim(c(-12.5,-5))



cowplot::plot_grid(p1 + ggtitle("motif_STAT5A"),
                   p3 + ggtitle("motif_NFAT5"),
                   p4 + ggtitle("Motif_RUNX3"),
                   p5 + ggtitle("motif_SMAD4"),
                   ncol = 2)
```
```{r fig.height=1,fig.width=1.5}
p2
```

```{r}
head(motif_Siglecf_exp[order(abs(motif_Siglecf_exp$avg_diff),decreasing = T),],n=50)

top50.motifs <- rownames(head(motif_Siglecf_exp[order(abs(motif_Siglecf_exp$avg_diff),decreasing = T),],n=50))

# top50.motifs <- rownames(head(motif_Siglecf_exp[order(abs(motif_Siglecf_exp$p_val_adj),decreasing = F),],n=60))

top50.motifs
```
```{r fig.height=7,fig.width=3}
combined.metacells[["chromvar_pfm"]]@scale.data <- combined.metacells[["chromvar_pfm"]]@data

h.clust <- hclust(dist(x = combined.metacells[["chromvar_pfm"]]@scale.data[top50.motifs,]))

top50.motifs.order <-  rownames(combined.metacells[["chromvar_pfm"]]@scale.data[top50.motifs,])[h.clust$order]

hm <- DoHeatmap(combined.metacells,assay = "chromvar_pfm",features = top50.motifs.order,group.colors = rev(c('#23452F','#9FA3A8')))

hm
```
```{r fig.height=2.5,fig.width=2}
hoccomoco_translation <- read.table('~/work/SuperCellMultiomicsAnalyses/input/HOCCOMOCO_motifs/H12CORE_motifs.tsv',sep = "\t",header = T)

hoccomoco_translation$Prot_mouse <- stringr::str_split_fixed(string = hoccomoco_translation$UniProt.ID..mouse.,pattern = "_",n = 2)[,1]

rownames(hoccomoco_translation) <- hoccomoco_translation$Motif

hm$data$Feature <- plyr::mapvalues(x = hm$data$Feature,
                                   from = levels(hm$data$Feature),
                                   to = hoccomoco_translation[levels(hm$data$Feature),"Prot_mouse"])

hm + scale_fill_gradient2( low = rev(c('#67a9cf','#2166ac')), mid = "white", high = rev(c('#ef8a62','#fddbc7')), midpoint = 0, guide = "colourbar", aesthetics = "fill")
```
```{r fig.height=1,fig.width=1.5}
DimPlot(combined.metacells,reduction = "wnn.umap",cols = rev(c('#23452F','#9FA3A8')) ) + xlim(c(-12.5,-5))

```

```{r}
gene_Siglecf_exp<- FindMarkers(  object = combined.metacells,
                                  ident.1 = "Siglecf_high",
                                  ident.2 = "Siglecf_low",
                                  assay = "RNA")

gene_Siglecf_exp <- gene_Siglecf_exp[gene_Siglecf_exp$p_val_adj< 0.05,]

gene_Siglecf_exp
write.csv(gene_Siglecf_exp,"genes_RNA_Siglecf_high_vs_low.csv")
```



```{r}
marker_rna_Siglecf_exp<- FindMarkers(  object = combined.metacells,ident.1 = "Siglecf_high",ident.2 = "Siglecf_low",
                                  mean.fxn = rowMeans, assay = "chromvar_pfm",
                                  fc.name = "avg_diff")
```

