---
title: "Figure1"
author: "Leonard Herault"
date: "`r Sys.Date()`"
output: html_document
---

SuperCellMulti identifies robust multiomics metacells increasing inter-modality consistency compared to single cells. 

# Package loading
```{r setup, include=FALSE}
library(SuperCellMultiomics)
library(Seurat)
library(ggplot2)
```

```{r}
library(Cairo)
options(bitmapType = "cairo")
```


## PBMC multiome results

```{r}
pbmc <- readRDS("../../output/pbmcMultiome/singlecells_analysis/seuratWNN.rds")


addCellTypePBMC <- function(pbmc) {
  pbmc$celltype <- pbmc$seurat_annotations
  
  pbmc$celltype[grepl(pattern = "CD8 TEM",x = pbmc$celltype)] <- "CD8 Mem"
  
  pbmc$celltype[grepl(pattern = "CD4 TEM",x = pbmc$celltype)] <- "CD4 Mem"
  pbmc$celltype[grepl(pattern = "CD4 TCM",x = pbmc$celltype)] <- "CD4 Mem"
  
  pbmc$celltype[grepl(pattern = "CD8 TEM",x = pbmc$celltype)] <- "CD8 Mem"
  
  pbmc$celltype[grepl(pattern = "Intermediate B",x = pbmc$celltype)] <- "B Interm"
  pbmc$celltype[grepl(pattern = "Naive B",x = pbmc$celltype)] <- "B Naive"
  pbmc$celltype[grepl(pattern = "Memory B",x = pbmc$celltype)] <- "B Mem"
  pbmc$celltype <- factor(pbmc$celltype,levels = c( "B Interm",  "B Mem"   ,
                                                    "B Naive" ,  "CD14 Mono",
                                                    "CD16 Mono" ,"CD4 Mem" ,
                                                    "CD4 Naive" ,"CD8 Mem"  ,
                                                    "CD8 Naive", "cDC"   ,
                                                    "gdT"  ,     "HSPC"  ,
                                                    "MAIT",      "NK" ,
                                                    "pDC" , "Plasma",     "Treg"  ))
  
  Idents(pbmc) <- "celltype"
  return(pbmc)
}


color.celltypes.pbmc <- c("CD14 Mono" =  "#F1BB72",
                          "CD16 Mono" = "#53A85F",
                          "CD4 Mem" = '#91D0BE',
                          "CD4 Naive" = "#F3B1A0",
                          "CD8 Effector" = "#AB3282",
                          "CD8 Mem" = "#BD956A",
                          "CD8 Naive" = "#8C549C",
                          "cDC" = "#9FA3A8",
                          "gdT" = "#E0D4CA",
                          "MAIT" = "#E4C755",
                          "Plasma" = "#ff6db6",
                          'B Mem' = "#F7F398",
                          "B Interm" = "#AA9A59",
                          "B Naive" = "#E63863",
                          "NK" = "#6778AE",
                          "pDC" = "#712820",
                          "Treg" ='#57C3F3',
                          "HSPC" = "#58A4C3")

pbmc <- addCellTypePBMC(pbmc)

# color <- c("CD4 Naive"="#999999","NK"="#004949","CD8 Naive"="#009292","CD14 Mono"="#ff6db6",
#            "gdT"="#490092", "CD4 Mem"="#006ddb","cDC"="#b66dff","Treg"="#6db6ff",
#            "B Interm"="#b6dbff","B Mem"= "#8494FF","B Naive" = "#00A9FF",
#            "CD16 Mono"="#920000","HSPC"="#924900","CD8 Mem"="#db6d00","pDC"="#24ff24", "MAIT"="#ffff6d","Plasma"="#ffb6db")
# 
# 
# show_col(color.celltypes)
DimPlot(pbmc,group.by = "celltype",cols = color.celltypes.pbmc,reduction = "wnn.umap")

```


```{r load_pbmcmc_g75}
pbmc.supercell.atac <- readRDS("../../output/pbmcMultiome/SuperCellATAC/g75/seurat.multiome.activities.rds")
pbmc.supercell.atac <- addCellTypePBMC(pbmc.supercell.atac)

pbmc.seacells.atac <- readRDS("../../output/pbmcMultiome//seacellsATAC//g75/seurat.multiome.activities.rds")
pbmc.seacells.atac <- addCellTypePBMC(pbmc.seacells.atac)

pbmc.seacells.rna <- readRDS("../../output/pbmcMultiome//seacellsRNA//g75/seurat.multiome.activities.rds")
pbmc.seacells.rna <- addCellTypePBMC(pbmc.seacells.rna)

pbmc.supercell.rna <- readRDS("../../output/pbmcMultiome//SuperCellRNA//g75/seurat.multiome.activities.rds")
pbmc.supercell.rna <- addCellTypePBMC(pbmc.supercell.rna)

pbmc.supercell.multi <- readRDS("../../output/pbmcMultiome//SuperCellMulti//g75/seurat.multiome.activities.rds")
pbmc.supercell.multi <- addCellTypePBMC(pbmc.supercell.multi)

pbmc.metacell.rna <- readRDS("../../output/pbmcMultiome/MetaCellRNA//g75/seurat.multiome.activities.rds")
pbmc.metacell.rna <- addCellTypePBMC(pbmc.metacell.rna)


```

```{r}
# source("../R/functions/metacellCompactnessSeparation.R")

if (!file.exists("metrics.pbmc.multiome.csv")) {
  metrics <- data.frame()
  # methods <- c('SuperCellMulti','SuperCellRNA',"SuperCellATAC","randomMetacells","seacellsRNA","seacellsATAC","MetaCellRNA")
  methods <- c('SuperCellMulti','SuperCellRNA',"SuperCellATAC","seacellsRNA","seacellsATAC","MetaCellRNA")
  #methods <- "seacellsATAC"
  
  for (g in c(10,20,50,75,100)){
    for (i in methods){
      file <- paste0("../../output/pbmcMultiome/",
                     i,"/g",
                     g,
                     "/seurat.multiome.mcMetrics.rds")
      if (file.exists(file)) {
        pbmc.mc <- readRDS(file)
        if (i == '') {i <- "MULTI"}
        pbmc.mc$input <- i
        pbmc.mc$gamma <- g
        ## Silhouette
        # pbmc.mc <- metacellSilhouetteSeurat(seurat.mc = pbmc.mc,seurat = pbmc,reduction.name.sc = "pca",single.cells.res = T,dims =  1:40)
        # pbmc.mc <- metacellSilhouetteSeurat(seurat.mc = pbmc.mc,seurat = pbmc,reduction.name.sc = "lsi",single.cells.res = T, dims = 2:40) 
        
        
        metrics <- rbind(metrics,pbmc.mc@meta.data)
      }
    }
    
    
  }
  
  #Set compactness to 0 (best score) for metacell of size 1
  # table(metrics[is.na(metrics$compactness_lsi),"gamma"])
  # table(metrics[is.na(metrics$compactness_lsi),"input"])
  
  
  #metrics$compactness_lsi[is.na(metrics$compactness_lsi)] <- 0
  
  #metrics$compactness_pca[is.na(metrics$compactness_pca)] <- 0
  
  
  metrics$gamma <- factor(as.character(metrics$gamma),levels =c(10,20,50,75,100))
  
  metrics$method <- plyr::mapvalues(x= metrics$input, 
                                    from = c('SuperCellMulti','SuperCellRNA',"SuperCellATAC","randomMetacells","seacellsRNA","seacellsATAC","MetaCellRNA"),
                                    to = c('SuperCell ATAC+RNA','SuperCell RNA',"SuperCell ATAC","Random None","SEACells RNA","SEACells ATAC","MetaCell2 RNA"))
  
  metrics$tool <- stringr::str_split_fixed(metrics$method,pattern = " ",n = 2)[,1]
  metrics$input <- stringr::str_split_fixed(metrics$method,pattern = " ",n = 2)[,2]
  
  
  metrics$input <- factor(as.character(metrics$input),levels = c("RNA","ATAC","ATAC+RNA","None"))
  
  method.levels <- c('SuperCell ATAC+RNA',"SuperCell ATAC","SEACells ATAC",
                     'SuperCell RNA',"SEACells RNA","MetaCell2 RNA","Random None")
  
  metrics$method <- factor(metrics$method,
                           levels = method.levels)
  
  metrics$purity <- metrics$seurat_annotations_purity # original anno
} else {
  metrics <- read.table("metrics.pbmc.multiome.csv")
  
  
}
method.levels <- c('SuperCell ATAC+RNA',"SuperCell ATAC","SEACells ATAC",
                   'SuperCell RNA',"SEACells RNA","MetaCell2 RNA","Random None")
metrics$method <- factor(metrics$method,
                         levels = method.levels)
```

## UMAPs
```{r}
library(ggpubr)
fig1B <- DimPlotSC(seurat = pbmc,
                   seurat.mc = pbmc.supercell.multi,
                   metacell.col = "celltype",
                   sc.col = "celltype",
                   mc.color = color.celltypes.pbmc ,
                   sc.color = color.celltypes.pbmc) + theme_classic()  +
  guides(fill=guide_legend(ncol =2,title = "Cell types",
                           override.aes = list(size=4)),
         colour = "none",
         size = guide_legend(title = "Size"))

legend.celltypes <- get_legend(fig1B,
                               position  = c(0.5,0)) 

umap.sc.multi <-  fig1B + NoLegend() +    scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),breaks = c(50,100,150,200))

umap.sc.rna <- DimPlotSC(seurat = pbmc,
                         seurat.mc = pbmc.supercell.rna,
                         metacell.col = "celltype",
                         sc.col = "celltype",
                         mc.color = color.celltypes.pbmc ,
                         sc.color = color.celltypes) + theme_classic() + NoLegend() +    scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),breaks = c(50,100,150,200))

umap.sc.atac <- DimPlotSC(seurat = pbmc,
                          seurat.mc = pbmc.supercell.atac,
                          metacell.col = "celltype",
                          sc.col = "celltype",
                          mc.color = color.celltypes.pbmc ,
                          sc.color = color.celltypes.pbmc) + theme_classic() +  NoLegend()  +    scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),breaks = c(50,100,150,200))

umap.sea.rna <- DimPlotSC(seurat = pbmc,
                          seurat.mc = pbmc.seacells.rna,
                          metacell.col = "celltype",
                          sc.col = "celltype",
                          mc.color = color.celltypes.pbmc ,
                          sc.color = color.celltypes.pbmc) + theme_classic()+  NoLegend() +    scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),breaks = c(50,100,150,200))

umap.sea.atac <- DimPlotSC(seurat = pbmc,
                           seurat.mc = pbmc.seacells.atac,
                           metacell.col = "celltype",
                           sc.col = "celltype",
                           mc.color = color.celltypes.pbmc ,
                           sc.color = color.celltypes.pbmc) + theme_classic()  + NoLegend() +    scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),breaks = c(50,100,150,200))

umap.mc.rna <- DimPlotSC(seurat = pbmc,
                         seurat.mc = pbmc.metacell.rna,
                         metacell.col = "celltype",
                         sc.col = "celltype",
                         mc.color = color.celltypes.pbmc ,
                         sc.color = color.celltypes.pbmc) + theme_classic() + NoLegend()  +    scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),breaks = c(50,100,150,200))

blank <- element_blank()
```


```{r fig.height=5,fig.width=7}
fig1B$layers[[1]] <- NULL

fig1B
```





## Fig 2A benchmark plot

set method color
```{r}
library(scales)
# library(ggthemes)

input.colors.10Xmultiome <- c( "#E69F00","#56B4E9","#009E73","darkgrey") #c(colorblind_pal()(8)[2:4],"darkgrey")


names(input.colors.10Xmultiome) <- c("ATAC","ATAC+RNA","RNA","None")
```






```{r}


# 
```


```{r fig.height=3,fig.width=3}
comparisons <- list(c("SuperCell ATAC+RNA","SuperCell ATAC"),
                    c('SuperCell ATAC+RNA',"SEACells ATAC"),
                    c('SuperCell ATAC+RNA','SuperCell RNA'),
                    c('SuperCell ATAC+RNA',"SEACells RNA"),
                    c('SuperCell ATAC+RNA',"MetaCell2 RNA"))

comparison.inter.modality <- list(c('SuperCell ATAC',"SEACells ATAC"),
                                  c('SuperCell RNA','SEACells RNA'),
                                  c('SuperCell RNA',"MetaCell2 RNA"))

library(ggsignif)
#metrics.df <- as.data.frame()

```




```{r fig.height=3,fig.width=3}
purity.pbmc.multiome.g75 <- ggplot(metrics[metrics$gamma %in% c(75),],aes(y=purity,x = method,fill = input)) + 
  geom_boxplot() + 
  #facet_wrap("gamma",nrow = 1) + 
  geom_signif(comparisons = comparisons,
              step_increase=0.225,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.225,map_signif_level=T,extend_line = -0.005,textsize = 3) +
  scale_y_continuous(breaks = c(0.2,0.6,1),limits = c(0.1,1.9)) + 
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + theme_bw() + theme(axis.title.x = element_blank())


purity.pbmc.multiome.g75 + NoLegend()
```

## Final figures

```{r fig.height=4,fig.width=4}
hline <- median(metrics[metrics$gamma %in% c(75) & metrics$method == "SuperCell ATAC+RNA","compactness_pca"])
compactness_pca.bmc.cite.g75 <- ggplot(metrics[metrics$gamma %in% c(75),],
                                       aes(y=compactness_pca,x = method,fill = input)) + 
  geom_boxplot() + scale_y_log10(limits = c(0.00001,500000))+  geom_hline(yintercept =hline,color = "darkblue",linetype = "longdash")  +
  geom_signif(comparisons = comparisons,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Compactness RNA") + theme_bw() + theme(axis.title.x = element_blank())


compactness_pca.bmc.cite.g75 + NoLegend()
```
```{r fig.height=4,fig.width=4}
hline <- median(metrics[metrics$gamma %in% c(75) & metrics$method == "SuperCell ATAC+RNA","compactness_lsi"])

compactness_lsi.bmc.cite.g75 <- ggplot(metrics[metrics$gamma %in% c(75),],aes(y=compactness_lsi,x = method,fill = input)) + 
  geom_boxplot() + scale_y_log10(limits = c(0.00001,500))+
  geom_hline(yintercept =hline,color = "darkblue",linetype = "longdash")  +
  geom_signif(comparisons = comparisons,step_increase=0.2,map_signif_level=T,extend_line = -0.005,textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.2,map_signif_level=T,extend_line = -0.005,textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Compactness ATAC") + theme(axis.title.x = element_blank())  + theme_bw() + theme(axis.title.x = element_blank())


compactness_lsi.bmc.cite.g75 + NoLegend()
```



```{r fig.height=4,fig.width=4}
separation_pca.g75 <- ggplot(metrics[metrics$gamma %in% c(75),],aes(y=separation_pca,x = method,fill = input)) + 
  geom_boxplot() + scale_y_log10(limits= c(0.005,10000))+
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Separation RNA") + theme(axis.title.x = element_blank())  + theme_bw() + theme(axis.title.x = element_blank())


separation_pca.g75 + NoLegend()
```



```{r fig.height=4,fig.width=4}
separation_lsi.g75 <- ggplot(metrics[metrics$gamma %in% c(75),],aes(y=separation_lsi,x = method,fill = input)) + 
  geom_boxplot() + scale_y_log10(limits = c(0.001,200))+
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Separation ATAC") + theme(axis.title.x = element_blank()) + theme_bw() + theme(axis.title.x = element_blank())


separation_lsi.g75 + NoLegend()
```




New version not reversed scaling without random.
We perform min max scaling of compactness/sepration including semi sup SuperCell runs.

```{r fig.height=4,fig.width=4}
library(dplyr)
bench.75.no.random <- metrics[metrics$gamma %in% c(75) & metrics$method != "Random None",]
bench.75.no.random$pct_known <- 0

semi.sup <- read.csv("../../output/pbmcMultiome/SuperCellMulti/testSemiSup/g75/results_test_semisup.csv",row.names = 1)
semi.sup$gamma <- 75
semi.sup$input <- "ATAC+RNA" 
semi.sup$tool <- "ssSuperCell" 
semi.sup$method <- "SuperCell ATAC+RNA" 

cn <- colnames(bench.75.no.random)[colnames(bench.75.no.random) %in% colnames(semi.sup)]

bench.75.no.random <- rbind(bench.75.no.random[,cn],semi.sup[,cn])

minMaxScaling <- function(x) {
  y <- (x-min(x))/(max(x)-min(x))
  return(y)
}

bench.75.no.random$compactness_pca_scaled <- minMaxScaling(bench.75.no.random$compactness_pca)
bench.75.no.random$compactness_lsi_scaled <- minMaxScaling(bench.75.no.random$compactness_lsi)

bench.75.no.random$multimodal_compactness <- (bench.75.no.random$compactness_pca_scaled + bench.75.no.random$compactness_lsi_scaled) / 2

limits <- bench.75.no.random[bench.75.no.random$tool != "ssSuperCell",]  %>%
  group_by(method) %>%
  summarize(
    ymin = quantile(multimodal_compactness, 0.25) - 1.5 * IQR(multimodal_compactness),
    ymax = quantile(multimodal_compactness, 0.75) + 1.5 * IQR(multimodal_compactness)
  ) %>%
  ungroup() %>%
  summarize(
    ymin = min(ymin),
    ymax = max(ymax)
  )
# 
# step_increase <- 0.075*0.25/(limits$ymax-limits$ymin)


multimodal_compactness.75 <- ggplot(bench.75.no.random[bench.75.no.random$tool != "ssSuperCell",],aes(y=multimodal_compactness,x = method,fill = input)) + 
  geom_boxplot(outlier.shape = NA) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Multimodal Compactness")  +  # Hides outliers
  coord_cartesian(ylim = c(-0.01,0.21)) + theme(axis.title.x = element_blank()) + 
  geom_signif(comparisons = comparisons,
              y_position = 0.08,
              step_increase=0.035,
              map_signif_level=T,
              extend_line = -0.005,
              tip_length = 0.01,
              textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,
              step_increase=0.035,
              map_signif_level=T,
              y_position = 0.08,
              tip_length = 0.01,
              extend_line = -0.005,textsize = 3)  + theme_bw() + theme(axis.title.x = element_blank())
multimodal_compactness.75


```



```{r fig.height=4,fig.width=4}

bench.75.no.random$separation_pca_norm <- (bench.75.no.random$separation_pca)
bench.75.no.random$separation_lsi_norm <- (bench.75.no.random$separation_lsi)
minMaxScaling <- function(x) {
  y <- (x-min(x))/(max(x)-min(x))
  return(y)
}

bench.75.no.random$separation_pca_scaled <- minMaxScaling(bench.75.no.random$separation_pca_norm)
bench.75.no.random$separation_lsi_scaled <- minMaxScaling(bench.75.no.random$separation_lsi_norm)

bench.75.no.random$multimodal_separation <- (bench.75.no.random$separation_pca_scaled + bench.75.no.random$separation_lsi_scaled) / 2



# limits <- bench.75.no.random[bench.75.no.random$method != "Random None",] %>%
#   group_by(method) %>%
#   summarize(
#     ymin = quantile(multimodal_separation, 0.25) - 1.5 * IQR(multimodal_separation),
#     ymax = quantile(multimodal_separation, 0.75) + 1.5 * IQR(multimodal_separation)
#   ) %>%
#   ungroup() %>%
#   summarize(
#     ymin = min(ymin),
#     ymax = max(ymax)
#   )
# step_increase <- 0.075*0.25/(limits$ymax-limits$ymin)


multimodal_separation.75 <- ggplot(bench.75.no.random[bench.75.no.random$tool != "ssSuperCell",],aes(y=multimodal_separation,x = method,fill = input)) + 
  geom_boxplot(outlier.shape = NA) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Multimodal Separation")  +  # Hides outliers
  coord_cartesian(ylim = c(0, 0.20)) + theme(axis.title.x = element_blank()) + 
  geom_signif(comparisons = comparisons,
              y_position = 0.065,
              step_increase=0.035,
              map_signif_level=T,
              extend_line = -0.005,
              tip_length = 0.01,
              textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,
              step_increase=0.035,
              map_signif_level=T,
              y_position = 0.065,
              tip_length = 0.01,
              extend_line = -0.005,textsize = 3)  + theme_bw() + theme(axis.title.x = element_blank())
multimodal_separation.75
# 
# plot_data <- ggplot_build(multimodal_separation.75)
# y_limits <- plot_data$layout$panel_params[[1]]$y.range
# 
# step_increase <-  .23*(1.4-1.1)
# 
# 
# sig.multimodal.separation.g75 <- ggplot(bench.75[bench.75$method != "Random None",],aes(y=multimodal_separation,x = method,fill = input)) + 
#   geom_boxplot(outlier.shape = NA) +
#   
#   geom_signif(comparisons = comparisons,step_increase=step_increase,map_signif_level=T,extend_line = -0.005,textsize = 3.5) +
#   geom_signif(comparisons = comparison.inter.modality,step_increase=step_increase,map_signif_level=T,extend_line = -0.005,textsize = 3.5) +
#   coord_cartesian(ylim = c(1.1, 1.4))  + theme_void() + NoLegend()
# 
# 
# full.multimodal.separation.g75 <- cowplot::plot_grid(sig.multimodal.separation.g75,multimodal_separation.75+ NoLegend(), rel_heights = c(0.2,0.8),align = "v",ncol = 1)
# 
# full.multimodal.separation.g75
```


```{r  fig.height=4,fig.width=4}




# limits <- bench.75[bench.75$method != "Random None",] %>%
#   group_by(method) %>%
#   summarize(
#     ymin = min(celltype.l2_purity),
#     ymax = 1
#   ) %>%
#   ungroup() %>%
#   summarize(
#     ymin = min(ymin),
#     ymax = max(ymax)
#   )
# step_increase <- 0.075*0.25/(limits$ymax-limits$ymin)

seurat_annotations_purity.g75 <- ggplot(bench.75.no.random[bench.75.no.random$tool != 'ssSuperCell',],aes(y=seurat_annotations_purity,x = method,fill = input)) + 
  geom_boxplot() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + 
  scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Purity") + 
  theme(axis.title.x = element_blank()) +
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,step_increase=0.125,
              map_signif_level=T,
              extend_line = -0.005,
              y_position = 1.02,
              tip_length = 0.03,
              textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality, y_position = 1.02,step_increase=0.125,map_signif_level=T,tip_length = 0.03,extend_line = -0.005,textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) +
  scale_y_continuous(breaks = c(0.2,0.6,1),limits = c(0.1,1.5))  + theme_bw() + theme(axis.title.x = element_blank())
seurat_annotations_purity.g75


# 
# 
# step_increase <- 0.23*(1.3-1.03)
# 
# sig.seurat_annotations.g75  <- ggplot(bench.75[bench.75$method != "Random None",],aes(y=seurat_annotations_purity,x = method,fill = input)) + 
#   geom_boxplot() +
#   #facet_wrap("gamma",nrow = 1) + 
#   #ylim(c(0,1.425)) + 
#   geom_signif(comparisons = comparisons,step_increase=step_increase,map_signif_level=T,extend_line = -0.005,textsize = 3.5)+
#   geom_signif(comparisons = comparison.inter.modality,step_increase=step_increase,map_signif_level=T,extend_line = -0.005,textsize = 3.5) +
#   scale_x_discrete(guide = guide_axis(angle = 60)) + 
#   theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Multimodal Compactness")  +  # Hides outliers
#   coord_cartesian(ylim = c(1.03, 1.3)) + theme_void()  + NoLegend()
# 
# # Hides outliers
# #coord_cartesian(ylim = c(0, limits$ymax))   # Sets y-axis limits
# 
# 
# full.seurat_annotations.g75 <-cowplot::plot_grid(sig.seurat_annotations.g75,seurat_annotations_purity.g75+ NoLegend(), rel_heights = c(0.2,0.8),align = "v",ncol = 1)
# full.seurat_annotations.g75
```

```{r  fig.height=4,fig.width=4}
size.g75 <- ggplot(bench.75.no.random[bench.75.no.random$tool != "ssSuperCell",],aes(y=size,x = method,fill = input)) + 
  geom_boxplot() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Size") + theme(axis.title.x = element_blank()) + NoLegend()  + theme_bw() + theme(axis.title.x = element_blank())
size.g75
```


## gamma 20
2 singleton not plotted (warnings)
```{r fig.height=4,fig.width=4}
bench.20 <- metrics[metrics$gamma == 20,]
bench.20$compactness_lsi[bench.20$size == 1] <- 0
bench.20$compactness_pca[bench.20$size == 1] <- 0

hline <- median(bench.20[ bench.20$method == "SuperCell ATAC+RNA","compactness_pca"])
compactness_pca.bmc.cite.g20 <- ggplot(bench.20,aes(y=compactness_pca,x = method,fill = input)) + 
  geom_boxplot() + scale_y_log10(limits = c(0.000001,1000000))+  geom_hline(yintercept =hline,color = "darkblue",linetype = "longdash")  +
  geom_signif(comparisons = comparisons,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Compactness RNA")  + theme_bw() + theme(axis.title.x = element_blank())


compactness_pca.bmc.cite.g20 + NoLegend()
```
```{r fig.height=4,fig.width=4}
hline <- median(bench.20[bench.20$method == "SuperCell ATAC+RNA","compactness_lsi"])

compactness_lsi.bmc.cite.g20 <- ggplot(bench.20,aes(y=compactness_lsi,x = method,fill = input)) + 
  geom_boxplot() + scale_y_log10(limits =  c(0.00001,1000))+
  geom_hline(yintercept =hline,color = "darkblue",linetype = "longdash")  +
  geom_signif(comparisons = comparisons,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Compactness ATAC") + theme(axis.title.x = element_blank())  + theme_bw() + theme(axis.title.x = element_blank())


compactness_lsi.bmc.cite.g20 + NoLegend()
```



```{r fig.height=4,fig.width=4}
separation_pca.g20 <- ggplot(bench.20,aes(y=separation_pca,x = method,fill = input)) + 
  geom_boxplot() + scale_y_log10(limits = c(0.0001,10000))+
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Separation RNA") + theme(axis.title.x = element_blank())  + theme_bw() + theme(axis.title.x = element_blank())


separation_pca.g20 + NoLegend()
```



```{r fig.height=4,fig.width=4}
separation_lsi.g20 <- ggplot(bench.20,aes(y=separation_lsi,x = method,fill = input)) + 
  geom_boxplot() + scale_y_log10(limits = c(0.001,500))+
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,step_increase=0.2,map_signif_level=T,extend_line = -0.005,textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.2,map_signif_level=T,extend_line = -0.005,textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Separation ATAC") + theme(axis.title.x = element_blank())  + theme_bw() + theme(axis.title.x = element_blank())


separation_lsi.g20 + NoLegend()
```



New version not reversed scaling without radom metacells

```{r  fig.height=4,fig.width=4}
bench.20.no.random <-  bench.20[bench.20$method != "Random None",]

bench.20.no.random$compactness_pca_scaled <- minMaxScaling(bench.20.no.random$compactness_pca)
bench.20.no.random$compactness_lsi_scaled <- minMaxScaling(bench.20.no.random$compactness_lsi)

bench.20.no.random$multimodal_compactness <- (bench.20.no.random$compactness_pca_scaled + bench.20.no.random$compactness_lsi_scaled) / 2


limits <- bench.20.no.random[bench.20.no.random$method != "Random None",] %>%
  group_by(method) %>%
  summarize(
    ymin = quantile(multimodal_compactness, 0.25) - 1.5 * IQR(multimodal_compactness),
    ymax = quantile(multimodal_compactness, 0.75) + 1.5 * IQR(multimodal_compactness)
  ) %>%
  ungroup() %>%
  summarize(
    ymin = min(ymin),
    ymax = max(ymax)
  )
# 

sig.multimodal.compactness.g20  <- ggplot(bench.20.no.random[bench.20.no.random$method != "Random None",],aes(y=multimodal_compactness,x = method,fill = input)) + 
  geom_boxplot(outlier.shape = NA) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Multimodal Compactness")  +  # Hides outliers
  coord_cartesian(ylim = c(-0.01,limits$ymax+0.055)) + theme(axis.title.x = element_blank()) + 
  geom_signif(comparisons = comparisons,
              y_position = 0.06,
              step_increase=0.025,
              map_signif_level=T,
              extend_line = -0.005,
              tip_length = 0.007,
              textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,
              step_increase=0.025,
              map_signif_level=T,
              y_position = 0.06,
              tip_length = 0.007,
              extend_line = -0.005,textsize = 3)  + theme_bw() + theme(axis.title.x = element_blank())

sig.multimodal.compactness.g20



```


```{r fig.height=4,fig.width=4}

bench.20.no.random$separation_pca_norm <- (bench.20.no.random$separation_pca)
bench.20.no.random$separation_lsi_norm <- (bench.20.no.random$separation_lsi)
minMaxScaling <- function(x) {
  y <- (x-min(x))/(max(x)-min(x))
  return(y)
}

bench.20.no.random$separation_pca_scaled <- minMaxScaling(bench.20.no.random$separation_pca_norm)
bench.20.no.random$separation_lsi_scaled <- minMaxScaling(bench.20.no.random$separation_lsi_norm)

bench.20.no.random$multimodal_separation <- (bench.20.no.random$separation_pca_scaled + bench.20.no.random$separation_lsi_scaled) / 2



# limits <- bench.20[bench.20$method != "Random None",] %>%
#   group_by(method) %>%
#   summarize(
#     ymin = quantile(multimodal_separation, 0.25) - 1.5 * IQR(multimodal_separation),
#     ymax = quantile(multimodal_separation, 0.75) + 1.5 * IQR(multimodal_separation)
#   ) %>%
#   ungroup() %>%
#   summarize(
#     ymin = min(ymin),
#     ymax = max(ymax)
#   )
# # step_increase <- 0.075*0.25/(limits$ymax-limits$ymin)
# 
# 
# multimodal_separation.20 <- ggplot(bench.20[bench.20$method != "Random None",],aes(y=multimodal_separation,x = method,fill = input)) + 
#   geom_boxplot(outlier.shape = NA) +
#   scale_x_discrete(guide = guide_axis(angle = 60)) + 
#   theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Multimodal Separation")  +  # Hides outliers
#   coord_cartesian(ylim = c(0, limits$ymax)) + theme(axis.title.x = element_blank())  # Sets y-axis limits
# 
# 
# plot_data <- ggplot_build(multimodal_separation.20)
# y_limits <- plot_data$layout$panel_params[[1]]$y.range
# 
# step_increase <-  .23*(1.2-0.8)
# 
# 
# sig.multimodal.separation.g20 <- ggplot(bench.20[bench.20$method != "Random None",],aes(y=multimodal_separation,x = method,fill = input)) + 
#   geom_boxplot(outlier.shape = NA) +
#   
#   geom_signif(comparisons = comparisons,step_increase=step_increase,map_signif_level=T,extend_line = -0.005,textsize = 3.5) +
#   geom_signif(comparisons = comparison.inter.modality,step_increase=step_increase,map_signif_level=T,extend_line = -0.005,textsize = 3.5) +
#   coord_cartesian(ylim = c(0.8, 1.2))  + theme_void() + NoLegend()
# 
# 
# full.multimodal.separation.g20 <- cowplot::plot_grid(sig.multimodal.separation.g20,multimodal_separation.20+ NoLegend(), rel_heights = c(0.2,0.8),align = "v",ncol = 1)
# 
# full.multimodal.separation.g20
```

```{r  fig.height=4,fig.width=4}

sig.multimodal.separation.g20 <- ggplot(bench.20.no.random[bench.20.no.random$method != "Random None",],aes(y=multimodal_separation,x = method,fill = input)) + 
  geom_boxplot(outlier.shape = NA) +
  geom_signif(comparisons = comparisons,step_increase=0.02,
              map_signif_level=T,tip_length = 0.003,extend_line = -0.005,textsize = 3,y_position= 0.07) +
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.02,tip_length = 0.003,map_signif_level=T,extend_line = -0.005,textsize = 3,y_position=0.07) +  # Hides outliers
  coord_cartesian(ylim = c(0, 0.16))+
  scale_x_discrete(guide = guide_axis(angle = 60)) + theme(axis.title.x = element_blank()) + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Multimodal Separation") + NoLegend()  + theme_bw() + theme(axis.title.x = element_blank())
sig.multimodal.separation.g20

```

```{r  fig.height=4,fig.width=4}




# limits <- bench.20[bench.20$method != "Random None",] %>%
#   group_by(method) %>%
#   summarize(
#     ymin = min(celltype.l2_purity),
#     ymax = 1
#   ) %>%
#   ungroup() %>%
#   summarize(
#     ymin = min(ymin),
#     ymax = max(ymax)
#   )
# step_increase <- 0.020*0.25/(limits$ymax-limits$ymin)

seurat_annotations_purity.g20 <- ggplot(bench.20[bench.20$method != "Random None",],aes(y=seurat_annotations_purity,x = method,fill = input)) + 
  geom_boxplot() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Purity") + theme(axis.title.x = element_blank())




step_increase <- 0.23*(1.3-1.03)

sig.seurat_annotations.g20 <- ggplot(bench.20[bench.20$method != "Random None",],aes(y=seurat_annotations_purity,x = method,fill = input)) + 
  geom_boxplot() +
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,step_increase=0.15,
              map_signif_level=T,
              extend_line = -0.005,
              y_position = 1.02,
              tip_length = 0.03,
              textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality, 
              y_position = 1.02,
              step_increase=0.15,
              map_signif_level=T,
              tip_length = 0.03,
              extend_line = -0.005,
              textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  scale_y_continuous(breaks = c(0.2,0.6,1),limits = c(0.2,1.55)) +
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Purity")+  NoLegend()    + theme_bw() + theme(axis.title.x = element_blank())
# Hides outliers
#coord_cartesian(ylim = c(0, limits$ymax))   # Sets y-axis limits

sig.seurat_annotations.g20
```

```{r  fig.height=4,fig.width=4}
size.g20 <- ggplot(bench.20[bench.20$method != "Random None",],aes(y=size,x = method,fill = input)) + 
  geom_boxplot() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Size") + theme(axis.title.x = element_blank()) + NoLegend()  + theme_bw() + theme(axis.title.x = element_blank())
size.g20
```





```{r fig.height=3,fig.width=4}
use.gamma = c(20,75) 

benchTable <- data.frame()
benchTable2 <- data.frame()


methodToBenchFiles <- c('seurat.multiome.mc.txt','seurat.multiome.mc.txt','seurat.multiome.mc.txt','seacellMemberships.txt',"seacellMemberships.txt","MetaCellMemberships.txt")
methodToTools <- c('SuperCell','SuperCell','SuperCell','SEACells',"SEACells","MetaCell")
names(methodToBenchFiles) <- c('SuperCellMulti','SuperCellRNA','SuperCellATAC',"seacellsATAC","seacellsRNA","MetaCellRNA")

preprocess.bench.rna <- read.table("../../benchmark/pbmcMultiome/singlecells_analysis/seurat.RNA.txt",header = T) 

preprocess.bench.atac <- read.table("../../benchmark/pbmcMultiome/singlecells_analysis/seurat.ATAC.txt",header = T) 

preprocess.bench.multi <- read.table("../../benchmark/pbmcMultiome/singlecells_analysis/seurat_multimodal.txt",header = T) 

for (g in c(use.gamma)){
  for (i in names(methodToBenchFiles) ){
    
    bench <- read.table(paste0("../../benchmark/pbmcMultiome/",
                               i,"/g",
                               g,"/",
                               methodToBenchFiles[i]),header = T)
    
    
    bench2 <- bench[c("s","max_rss","max_pss","cpu_time")]
    if (i != "MetaCellRNA") {
      if(endsWith(x = i,suffix = "RNA")) {
        preprocess <- preprocess.bench.rna
      }
      if(endsWith(x = i,suffix = "ATAC")) {
        preprocess <- preprocess.bench.atac
      }
      if(endsWith(x = i,suffix = "Multi")) {
        preprocess <- preprocess.bench.multi
      }
      
      bench2 <- colSums(rbind(bench2[c("s","cpu_time")],
                              preprocess[c("s","cpu_time")]))
      
      bench2$max_rss <- max(unlist(c(bench["max_rss"],preprocess["max_rss"])))
      bench2$max_rss <- max(unlist(c(bench["max_rss"],preprocess["max_rss"])))
    } else {
      bench2 <- bench[c("s","cpu_time","max_rss")]
    }
    bench$method <- i
    bench$gamma <- g
    bench2$method <- i
    bench2$gamma <- g
    
    benchTable <- rbind(benchTable,bench)
    benchTable2 <- rbind(benchTable2,bench2)
    
  }}

getBenchTable <- function(benchTable) {
  benchTable$gamma <- factor(benchTable$gamma)
  # benchTable <-  rbind(benchTable,c(rep(1,10),"Random","20"))
  # benchTable <-  rbind(benchTable,c(rep(1,10),"Random","75"))
  
  benchTable$method <- plyr::mapvalues(x= benchTable$method, 
                                       from = c('SuperCellMulti','SuperCellRNA',"SuperCellATAC",
                                                "seacellsRNA","seacellsATAC","MetaCellRNA"),
                                       to = c('SuperCell ATAC+RNA','SuperCell RNA',"SuperCell ATAC",
                                              "SEACells RNA","SEACells ATAC","MetaCell2 RNA"))
  
  benchTable$input <- stringr::str_split_fixed(benchTable$method,pattern = " ",n=2)[,2]
  
  benchTable$input <- factor(as.character(benchTable$input),levels = c('ATAC+RNA',"ATAC","RNA","None"))
  benchTable$method <- factor(benchTable$method,
                              levels = method.levels)
  
  benchTable$cpu_time <- as.numeric(benchTable$cpu_time )
  benchTable$s <- as.numeric(benchTable$s )
  benchTable$max_rss <- as.numeric(benchTable$max_rss )
  
  return(benchTable)
}

benchTable <- getBenchTable(benchTable)
benchTable2 <- getBenchTable(benchTable2)



multiome.cpu.time.plot.g75.id <- ggplot(benchTable[benchTable$gamma == 75,],aes(x = method,y = cpu_time/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("cpu time (min)") + 
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme_bw() + theme(axis.title.x = element_blank())


multiome.run.time.plot.g75.id <- ggplot(benchTable[benchTable$gamma == 75,],aes(x = method,y = s/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Runtime (min)") + 
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme_bw() + theme(axis.title.x = element_blank())


multiome.cpu.time.plot.g20.id <- ggplot(benchTable[ benchTable$gamma == 20,],aes(x = method,y = cpu_time/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_y_log10()   +
  ylab("cpu time (min)") + 
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme_bw() + theme(axis.title.x = element_blank())

multiome.run.time.plot.g20.id <- ggplot(benchTable[benchTable$gamma == 20,],aes(x = method,y = s/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Runtime (min)") + 
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme_bw() + theme(axis.title.x = element_blank())


```
With preprocessing for SuperCell and SEACells
```{r}
multiome.cpu.time.plot.g75 <- ggplot(benchTable2[benchTable2$gamma == 75,],aes(x = method,y = cpu_time/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("cpu time (min)") + 
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme_bw() + theme(axis.title.x = element_blank())


multiome.run.time.plot.g75 <- ggplot(benchTable2[benchTable2$gamma == 75,],aes(x = method,y = s/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Runtime (min)") + 
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme_bw() + theme(axis.title.x = element_blank())


multiome.cpu.time.plot.g20 <- ggplot(benchTable2[ benchTable2$gamma == 20,],aes(x = method,y = cpu_time/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))   +
  ylab("cpu time (min)") + 
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme_bw() + theme(axis.title.x = element_blank())

multiome.run.time.plot.g20 <- ggplot(benchTable2[benchTable2$gamma == 20,],aes(x = method,y = s/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Runtime (min)") + 
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme_bw() + theme(axis.title.x = element_blank())



multiome.cpu.time.plot.g75
multiome.run.time.plot.g75

multiome.cpu.time.plot.g20
multiome.run.time.plot.g20
```
Memory with preprocessing
```{r}
multiome.memory.plot.g75 <- ggplot(benchTable2[benchTable2$gamma == 75,],aes(x = method,y = max_rss/1024,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Memory (GB)") + 
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme_bw() + theme(axis.title.x = element_blank())


multiome.memory.plot.g75.id <- ggplot(benchTable[benchTable$gamma == 75,],aes(x = method,y = max_rss/1024,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Memory (GB)") + 
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme_bw() + theme(axis.title.x = element_blank())


multiome.memory.plot.g20 <- ggplot(benchTable2[ benchTable2$gamma == 20,],aes(x = method,y = max_rss/1024,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_y_log10()   +
  ylab("Memory (GB)") + 
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme_bw() + theme(axis.title.x = element_blank())

multiome.memory.plot.g20.id <- ggplot(benchTable[benchTable$gamma == 20,],aes(x = method,y = max_rss/1024,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Memory (GB)") + 
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme_bw() + theme(axis.title.x = element_blank())



multiome.memory.plot.g75
multiome.memory.plot.g75.id

multiome.memory.plot.g20
multiome.memory.plot.g20.id
```

Combined scalability plot g20
```{r}
benchTable2$workflow <- "with preprocessing"
benchTable$workflow <- "identification only"



benchTable2$workflow <- factor(benchTable2$workflow,levels = c("with preprocessing","identification only"))

multiome.memory.plot.g20 <- ggplot(benchTable2[benchTable2$gamma == 20,],
                                   aes(x = method,y = max_rss/1024,fill = input)) + 
  geom_bar(stat = "identity",col = "black",position = "dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Memory (GB)") + 
  scale_fill_manual(values = input.colors.10Xmultiome) + theme(axis.title.x = element_blank())  + theme_bw() + theme(axis.title.x = element_blank())

multiome.cpu.time.plot.g20 <- ggplot(benchTable2[ benchTable2$gamma == 20,],
                                     aes(x = method,y = cpu_time/60,fill = input)) + 
  geom_bar(stat = "identity",col = "black",position = "dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60)) +
  ylab("cpu time (min)") + 
  
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme(axis.title.x = element_blank())  + theme_bw() + theme(axis.title.x = element_blank())

multiome.run.time.plot.g20 <- ggplot(benchTable2[benchTable2$gamma == 20,],
                                     aes(x = method,y = s/60,fill = input)) + 
  geom_bar(stat = "identity",col = "black",position = "dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Runtime (min)") + 
  
  scale_fill_manual(values = input.colors.10Xmultiome) + theme(axis.title.x = element_blank())  + theme_bw() + theme(axis.title.x = element_blank())

multiome.cpu.time.plot.g20
multiome.run.time.plot.g20

multiome.memory.plot.g20

```



```{r}
benchTable2$workflow <- "with preprocessing"
benchTable$workflow <- "identification only"


benchTable2$workflow <- factor(benchTable2$workflow,levels = c("with preprocessing","identification only"))

multiome.memory.plot.g75 <- ggplot(benchTable2[benchTable2$gamma == 75,],
                                   aes(x = method,y = max_rss/1024,fill = input)) + 
  geom_bar(stat = "identity",col = "black",position = "dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Memory (GB)") + 
  scale_fill_manual(values = input.colors.10Xmultiome) + theme(axis.title.x = element_blank())  + theme_bw() + theme(axis.title.x = element_blank())

multiome.cpu.time.plot.g75 <- ggplot(benchTable2[ benchTable2$gamma == 75,],
                                     aes(x = method,y = cpu_time/60,fill = input)) + 
  geom_bar(stat = "identity",col = "black",position = "dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))   +
  ylab("cpu time (min)") + 
  
  scale_fill_manual(values = input.colors.10Xmultiome)  + theme(axis.title.x = element_blank())  + theme_bw() + theme(axis.title.x = element_blank())

multiome.run.time.plot.g75 <- ggplot(benchTable2[benchTable2$gamma == 75,],
                                     aes(x = method,y = s/60,fill = input)) + 
  geom_bar(stat = "identity",col = "black",position = "dodge") +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Runtime (min)") + 
  scale_fill_manual(values = input.colors.10Xmultiome) + theme(axis.title.x = element_blank())  + theme_bw() + theme(axis.title.x = element_blank())

multiome.cpu.time.plot.g75
multiome.run.time.plot.g75

multiome.memory.plot.g75

```



Making Fig1 BCD
```{r fig.height=5,fig.width=3}
library(patchwork)
sig.seurat_annotations.g75 <- purity.pbmc.multiome.g75  + theme(axis.text.x = element_blank()) +  NoLegend()

sig.multimodal.compactness.g75 <-  multimodal_compactness.75 + NoLegend() +
  theme(axis.title.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60)) 

comp.pur.g75 <- sig.seurat_annotations.g75 / sig.multimodal.compactness.g75 + plot_layout(heights = c(1, 1))

comp.pur.g75
```

```{r  fig.height=5,fig.width=3}
leg.input <- get_legend(multiome.run.time.plot.g75 + theme(legend.position = "right"))
sep.g75 <- multimodal_separation.75+ NoLegend() +
  theme(axis.text.x = element_blank(),axis.title.x = element_blank()) 

multiome.run.time.plot.g75 <-  multiome.run.time.plot.g75  +
  theme(axis.title.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60)) 

sep.runtime.g75 <- sep.g75 / multiome.run.time.plot.g75 + plot_layout(heights = c(1, 1))
sep.runtime.g75

```

```{r fig.height=5,fig.width=5}


multiome.memory.plot.g75 <-  multiome.memory.plot.g75  +
  theme(axis.title.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60))   + theme_bw() + theme(axis.title.x = element_blank()) + 
  theme(legend.spacing.y = unit(-0.25, "line"))

multiome.memory.plot.g75
```




Sparsity reduction
```{r  fig.height=5,fig.width=2.5}
pbmc$resolution <- "Single-cells"
pbmc.supercell.multi$resolution <- "Metacells"
meta.sc.mc <- rbind(pbmc@meta.data[,c("nCount_RNA","nFeature_RNA","nCount_ATAC","nFeature_ATAC","resolution")],
                    pbmc.supercell.multi@meta.data[,c("nCount_RNA","nFeature_RNA","nCount_ATAC","nFeature_ATAC","resolution")])

meta.sc.mc$resolution <- factor(meta.sc.mc$resolution,levels = c("Metacells","Single-cells"))

nFeature_RNA <- ggplot(meta.sc.mc,aes(x=resolution,y=nFeature_RNA,fill = resolution)) + geom_violin(scale = "width")  + theme_bw() + theme(axis.title.x = element_blank(),axis.text.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  scale_fill_manual(values = c("#56B4E9","#D55E00")) #colorblind_pal()(8)[c(3,7)]


nFeature_ATAC <- ggplot(meta.sc.mc,aes(x=resolution,y=nFeature_ATAC,fill = resolution)) + geom_violin(scale = "width") + theme_bw() + theme(axis.title.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_fill_manual(values = c("#56B4E9","#D55E00")) #colorblind_pal()(8)[c(3,7)] 

sparsity.reduction.g75 <- cowplot::plot_grid(nFeature_RNA+ NoLegend(),nFeature_ATAC+ NoLegend(),ncol = 1)
sparsity.reduction.g75

```

```{r  fig.height=5,fig.width=2.5}

nCount_RNA <- ggplot(meta.sc.mc,aes(x=resolution,y=nCount_RNA,fill = resolution)) + geom_violin(scale = "width")  + theme_bw() + theme(axis.title.x = element_blank(),
                                                                                                                                       axis.text.x = element_blank())  +
  scale_y_log10() + 
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_fill_manual(values = c("#56B4E9","#D55E00"))  
nCount_ATAC <- ggplot(meta.sc.mc,aes(x=resolution,y=nCount_ATAC,fill = resolution)) + geom_violin(scale = "width")+ theme_bw()  + theme(axis.title.x = element_blank()) + scale_y_log10() + 
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_fill_manual(values = c("#56B4E9","#D55E00"))

sparsity.reduction.counts.g20 <- wrap_plots(nCount_RNA+ NoLegend(),nCount_ATAC+ NoLegend(),ncol = 1)

sparsity.reduction.counts.g20
```
```{r}
nFeature_RNA <- nFeature_RNA  + NoLegend() + theme_bw() +
  theme(axis.text.x = element_blank(),axis.title.x = element_blank()) + ylab("Detected Genes")   + NoLegend()

nFeature_ATAC <-  nFeature_ATAC  + theme_bw() +
  theme(axis.title.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60))+ ylab("Detected Peaks")  + NoLegend()

sparsity.reduction.g20 <- nFeature_RNA / nFeature_ATAC + plot_layout(heights = c(1, 1))

sparsity.reduction.g20
```

```{r  fig.height=5.25,fig.width=13.5}

Fig2ABC <- cowplot::plot_grid(fig1B+theme(plot.margin = unit(c(80,0,80,0),units = "pt")),
                              wrap_plots(nFeature_RNA, sig.seurat_annotations.g75, sep.g75, guide_area() ,
                                         nFeature_ATAC,sig.multimodal.compactness.g75,
                                         multiome.cpu.time.plot.g75 ,
                                         nrow = 2,ncol = 4,guides = "collect")  & 
                                theme(legend.spacing.y = unit(-0.35, "line")),
                              nrow = 1,
                              rel_widths = c(3,4.5))



Fig2ABC
```


```{r}
pdf(file = "Fig2ABC.pdf",height = 5.25,width=13.5)
Fig2ABC
dev.off()
```


# FigS1A
```{r fig.height=10,fig.width=11}
# umap.sc <- DimPlot(pbmc,group.by = "celltype",cols = color.celltypes.pbmc,reduction = "wnn.umap") + theme_classic() + ggtitle("Single cells") + NoLegend()
# umap.sc

umap.sc <- umap.sc.multi
umap.sc$layers[[2]] <- NULL

legend.celltypes <- ggpubr::get_legend(fig1B + theme(
  # legend.position = "bottom",        # Position legend at the bottom
  legend.box = "horizontal"# One column for shapes
) +guides(
  fill = guide_legend(ncol =2,title = "Cell types",
                      override.aes = list(size=4)),  # One column for colors
  size = guide_legend(ncol = 1))  +    scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),breaks = c(50,100,150,200)))


figS1A <- cowplot::plot_grid(umap.sc.multi + ggtitle("SuperCell ATAC+RNA"),
                             umap.sc.atac + ggtitle("SuperCell ATAC") ,
                             umap.sc.rna + ggtitle("SuperCell RNA"),
                             umap.sc + ggtitle("Single-cells"),
                             umap.sea.atac + ggtitle("SEACells ATAC"), 
                             umap.sea.rna + ggtitle("SEACells RNA"),
                             legend.celltypes,blank,
                             umap.mc.rna + ggtitle("MetaCell2 RNA")
)
figS1A



```

```{r}
pdf(file = "figS1A.pdf",height = 11,width=11)
figS1A
dev.off()
```


```{r fig.height=12,fig.width=5}
figS1B <- cowplot::plot_grid(cowplot::plot_grid(compactness_pca.bmc.cite.g75+ 
                                                  NoLegend() + 
                                                  theme(axis.title.x = element_blank()) +
                                                  scale_x_discrete(guide = guide_axis(angle = 60)),
                                                
                                                compactness_lsi.bmc.cite.g75 + NoLegend() + theme(axis.title.x = element_blank()) +
                                                  scale_x_discrete(guide = guide_axis(angle = 60)),
                                                separation_pca.g75 + NoLegend() + theme(axis.title.x = element_blank()) +
                                                  scale_x_discrete(guide = guide_axis(angle = 60)),
                                                separation_lsi.g75 + NoLegend() + theme(axis.title.x = element_blank()) +
                                                  scale_x_discrete(guide = guide_axis(angle = 60)), 
                                                size.g75 + NoLegend() + theme(axis.title.x = element_blank()) +scale_x_discrete(guide = guide_axis(angle = 60)),
                                                multiome.memory.plot.g75 + NoLegend() +scale_x_discrete(guide = guide_axis(angle = 60)),
                                                ncol = 2),get_legend(multiome.memory.plot.g20),ncol = 1,rel_heights = c(14,3))

figS1B
```
```{r}
pdf(file = "figS1B.pdf",height = 12,width=5)
figS1B
dev.off()
```








```{r}
pbmc.supercell.multi.g20 <- readRDS("../../output/pbmcMultiome//SuperCellMulti//g20/seurat.multiome.activities.rds")

figSupCov <- DimPlotSC(seurat = pbmc,
                       seurat.mc = pbmc.supercell.multi.g20,
                       metacell.col = "celltype",
                       sc.col = "celltype",
                       mc.color = color.celltypes.pbmc ,
                       sc.color = color.celltypes.pbmc) + theme_classic()  +
  guides(fill=guide_legend(ncol =2,title = "Cell types",
                           override.aes = list(size=4)),
         colour = "none",
         size = guide_legend(title = "Size"))

figSupCov$layers[[1]] <- NULL

figSupCov
```

Sparsity reduction g75
```{r  fig.height=5,fig.width=2.5}
pbmc$resolution <- "Single-cells"
pbmc.supercell.multi.g20$resolution <- "Metacells"
meta.sc.mc <- rbind(pbmc@meta.data[,c("nCount_RNA","nFeature_RNA","nCount_ATAC","nFeature_ATAC","resolution")],
                    pbmc.supercell.multi.g20@meta.data[,c("nCount_RNA","nFeature_RNA","nCount_ATAC","nFeature_ATAC","resolution")])

meta.sc.mc$resolution <- factor(meta.sc.mc$resolution,levels = c("Metacells","Single-cells"))

nFeature_RNA <- ggplot(meta.sc.mc,aes(x=resolution,y=nFeature_RNA,fill = resolution)) + geom_violin(scale = "width") + theme_bw() + theme(axis.title.x = element_blank(),
                                                                                                                                          axis.text.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  scale_fill_manual(values = c("#56B4E9","#D55E00")) +  NoLegend()


nFeature_ATAC <- ggplot(meta.sc.mc,aes(x=resolution,y=nFeature_ATAC,fill = resolution)) + geom_violin(scale = "width") + theme_bw() + theme(axis.title.x = element_blank(),
                                                                                                                                            axis.text.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_fill_manual(values = c("#56B4E9","#D55E00")) + NoLegend()

sparsity.reduction.g20 <- cowplot::plot_grid(nFeature_RNA+ NoLegend(),nFeature_ATAC+ NoLegend(),ncol = 1)


```

```{r  fig.height=5,fig.width=2.5}

nCount_RNA <- ggplot(meta.sc.mc,aes(x=resolution,y=nCount_RNA,fill = resolution)) + geom_violin(scale = "width")  + theme_bw() + theme(axis.title.x = element_blank(),
                                                                                                                                       axis.text.x = element_blank())  + scale_y_log10() + 
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_fill_manual(values = c("#56B4E9","#D55E00")) + NoLegend()
nCount_ATAC <- ggplot(meta.sc.mc,aes(x=resolution,y=nCount_ATAC,fill = resolution)) + geom_violin(scale = "width")  + theme_bw() + theme(axis.title.x = element_blank()) + scale_y_log10() + 
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_fill_manual(values = c("#56B4E9","#D55E00")) + NoLegend()

sparsity.reduction.counts.g20 <- wrap_plots(nCount_RNA+ NoLegend(),nCount_ATAC+ NoLegend(),ncol = 1)


```

```{r}
nFeature_RNA <- nFeature_RNA  + NoLegend()  + theme_bw() +
  theme(axis.text.x = element_blank(),axis.title.x = element_blank()) + ylab("Detected Genes") + NoLegend()

nFeature_ATAC <-  nFeature_ATAC  + theme_bw() +
  theme(axis.title.x = element_blank())  + NoLegend() + 
  scale_x_discrete(guide = guide_axis(angle = 60)) + ylab("Detected Peaks")


sparsity.reduction.g20 <- nFeature_RNA / nFeature_ATAC + plot_layout(heights = c(1, 1))  + NoLegend()

```
```{r fig.height=5,fig.width=9}
figS1C <- cowplot::plot_grid(figSupCov+theme(plot.margin = unit(c(50,50,50,25),units = "pt")),
                             wrap_plots(nFeature_RNA, nFeature_ATAC,ncol = 1),rel_widths = c(3,1))

figS1C
```
```{r}
pdf(file = "figS1C.pdf",height = 5,width=9)
figS1C
dev.off()
```
```{r}

```

Metcalls2 outliers
```{r fig.height= 2.5,fig.width=2}
pbmc.metacell.rna.g75 <- readRDS("../../output/pbmcMultiome/MetaCellRNA//g75/seurat.multiome.mc.rds")
outliers.mc2 <- data.frame("outliers" = c(length(which(is.na(pbmc.metacell.rna@misc$membership))),
                                          length(which(is.na(pbmc.metacell.rna.g75@misc$membership)))),
                           "graining_level" = c("20","75"))

outliers.mc2$perc.outliers <-label_percent()(outliers.mc2$outliers/ncol(pbmc))
outliers.mc2

outliers.mc2 <- ggplot(outliers.mc2,aes( x= graining_level, y = outliers)) + geom_bar(stat = "identity", position="dodge") + ylab("MetaCell2 outliers") + xlab("graining level") + geom_text(aes(label = perc.outliers),col = "red")
outliers.mc2
```
```{r}
# pdf(file = "figS1E.pdf",height = 2.5,width=2)
# outliers.mc2
# dev.off()
```


```{r  fig.height=6.5,fig.width=14}
figS1D <- cowplot::plot_grid(sig.seurat_annotations.g20+ NoLegend() + theme(axis.title.x = element_blank())+
                               scale_x_discrete(guide = guide_axis(angle = 60)),
                             sig.multimodal.compactness.g20+ NoLegend() + theme(axis.title.x = element_blank())+
                               scale_x_discrete(guide = guide_axis(angle = 60)),
                             sig.multimodal.separation.g20+ NoLegend() + theme(axis.title.x = element_blank())+
                               scale_x_discrete(guide = guide_axis(angle = 60)),
                             size.g20 + NoLegend() + theme(axis.title.x = element_blank())+
                               scale_x_discrete(guide = guide_axis(angle = 60)),
                             compactness_pca.bmc.cite.g20+ NoLegend() + theme(axis.title.x = element_blank())+
                               scale_x_discrete(guide = guide_axis(angle = 60)),
                             compactness_lsi.bmc.cite.g20 + NoLegend() + theme(axis.title.x = element_blank())+
                               scale_x_discrete(guide = guide_axis(angle = 60)),
                             separation_pca.g20 + NoLegend() + theme(axis.title.x = element_blank())+
                               scale_x_discrete(guide = guide_axis(angle = 60)),
                             separation_lsi.g20 + NoLegend() + theme(axis.title.x = element_blank())+
                               scale_x_discrete(guide = guide_axis(angle = 60)),
                             multiome.cpu.time.plot.g20+ theme(axis.title.x = element_blank()) + NoLegend()+ scale_x_discrete(guide = guide_axis(angle = 60)),
                             multiome.memory.plot.g20+ theme(axis.title.x = element_blank())+ NoLegend()+ scale_x_discrete(guide = guide_axis(angle = 60))
                             ,leg.input,
                             byrow = F,nrow = 2)

figS1D
```


```{r}
pdf(file = "figS1GH.pdf",height = 6.5,width=14)
figS1D
dev.off()
```


## Semi sup res



```{r}
semi.sup <- read.csv("../../output/pbmcMultiome/SuperCellMulti/testSemiSup/g75/results_test_semisup.csv")




semi.sup.purity <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = seurat_annotations_purity)) + geom_boxplot()
semi.sup.size <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = size)) + geom_boxplot()
compactness.pca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = compactness_pca)) + geom_boxplot()
separation.pca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = separation_pca)) + geom_boxplot()
compactness.lsi <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = compactness_lsi)) + geom_boxplot()
separation.lsi <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = separation_lsi)) + geom_boxplot()

patchwork::wrap_plots(semi.sup.purity , semi.sup.size,
                      compactness.pca , separation.pca,
                      compactness.lsi , separation.lsi)

```

```{r}
bench.75.no.random.semi.sup <- bench.75.no.random[bench.75.no.random$tool == "ssSuperCell",]

bench.75.no.random.semi.sup$pct_known <- factor(paste0(as.character(bench.75.no.random.semi.sup$pct_known),"%"), levels = rev(c("100%","75%","50%","25%","0%") ))

```


```{r fig.height=4,fig.width=4}

comparisons.semi.sup <- list(
  c("0%","25%"),
  c("0%","50%"),
  c("0%","75%"),
  c("0%","100%")
)


purity.pbmc.multiome.g75.semi.sup <- ggplot(bench.75.no.random.semi.sup,
                                            aes(y=seurat_annotations_purity,x = pct_known,fill = input)) + 
  geom_boxplot()  + theme_bw()  + 
  geom_signif(comparisons = comparisons.semi.sup,
              step_increase=0.125,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3)+
  scale_y_continuous(breaks = c(0.4,0.6,0.8,1),limits = c(0.4,1.25)) + 
  
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + theme_bw() + xlab("Annotated cells") +ylab("Purity") + NoLegend()


purity.pbmc.multiome.g75.semi.sup 
```
```{r fig.width=4, fig.height=4}

size.pbmc.multiome.g75.semi.sup <- ggplot(bench.75.no.random.semi.sup,
                                          aes(y=size,x = pct_known,fill = input)) + 
  geom_boxplot() + theme_bw()  + 
  geom_signif(comparisons = comparisons.semi.sup,
              step_increase=0.125,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3)+
  ylim(c(0,525))+
  
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + xlab("Annotated cells") + NoLegend()


size.pbmc.multiome.g75.semi.sup
```

```{r fig.height=4,fig.width=4}

multimodal_compactness.75.semi.sup <- ggplot(bench.75.no.random.semi.sup,aes(y=multimodal_compactness,x = pct_known,fill = input)) + 
  geom_boxplot(outlier.shape = NA)  + theme_bw() + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Multimodal Compactness")  +  # Hides outliers
  coord_cartesian(ylim = c(-0.01,0.135))   + NoLegend() + 
  geom_signif(comparisons = comparisons.semi.sup,
              y_position = 0.08,
              step_increase=0.035,
              map_signif_level=T,
              extend_line = -0.005,
              tip_length = 0.01,
              textsize = 3) + xlab("Annotated cells")
multimodal_compactness.75.semi.sup

```
```{r fig.height=4,fig.width=4}
multimodal_separation.75.semi.sup <- ggplot(bench.75.no.random.semi.sup,aes(y=multimodal_separation,x = pct_known,fill = input)) + 
  geom_boxplot(outlier.shape = NA) +theme_bw() +
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.10Xmultiome) + ylab("Multimodal Separation")  +  # Hides outliers
  coord_cartesian(ylim = c(0, 0.15))+ NoLegend() + 
  geom_signif(comparisons = comparisons.semi.sup,
              y_position = 0.06,
              step_increase=0.025,
              map_signif_level=T,
              extend_line = -0.005,
              tip_length = 0.007,
              textsize = 3) + xlab("Annotated cells")
multimodal_separation.75.semi.sup
```
```{r fig.height=2.75,fig.width = 7}
wrap_plots(purity.pbmc.multiome.g75.semi.sup,multimodal_compactness.75.semi.sup,multimodal_separation.75.semi.sup,nrow = 1)

pdf("fig2I_semi_sup.pdf",height = 2.75,width = 7)
wrap_plots(purity.pbmc.multiome.g75.semi.sup,multimodal_compactness.75.semi.sup,multimodal_separation.75.semi.sup,nrow = 1)
dev.off()
```


```{r fig.height=4,fig.width=18}
plot.list <- list()
for (p in c(100,75,50,25,0)) {
  sobj <- readRDS(paste0("../../output/pbmcMultiome/SuperCellMulti/testSemiSup/g75/guiding_label_",p,"_pct_hiddenseurat.mc.rds"))
  sobj <- addCellTypePBMC(sobj)
  plot.list[[paste0("pct_",p)]] <- DimPlotSC(seurat = pbmc,
                                             seurat.mc = sobj,
                                             metacell.col = "celltype",
                                             sc.col = "celltype",
                                             mc.color = color.celltypes.pbmc ,
                                             sc.color = color.celltypes) + theme_classic() + ggtitle(label = "SuperCell ATAC+RNA",
                                                                                                     subtitle = paste0(100-p, "% annotated cells")) + 
    scale_size(limits = c(0,max(bench.75.no.random.semi.sup$size)),breaks = c(50,100,150,200))  +
    guides(fill=guide_legend(ncol =2,title = "Cell types",
                             override.aes = list(size=4)),
           colour = "none",
           size = guide_legend(title = "Size"))
  
  
}

wrap_plots(plot.list[[2]],plot.list[[3]],plot.list[[4]],plot.list[[5]],guide_area(),guides = "collect",nrow = 1)

pdf("figS3_semi_sup.pdf", height = 4,width = 18)
wrap_plots(plot.list[[2]],plot.list[[3]],plot.list[[4]],plot.list[[5]],guide_area(),guides = "collect",nrow = 1)
dev.off()
```




```{r}
semi.sup <- read.csv("../../output/pbmcMultiome/SuperCellMulti/testSemiSup/g20/results_test_semisup.csv")
semi.sup.purity <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = seurat_annotations_purity)) + geom_boxplot()
semi.sup.size <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = size)) + geom_boxplot()
compactness.pca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = compactness_pca)) + geom_boxplot()
separation.pca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = separation_pca)) + geom_boxplot()
compactness.lsi <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = compactness_lsi)) + geom_boxplot()
separation.lsi <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = separation_lsi)) + geom_boxplot()

patchwork::wrap_plots(semi.sup.purity , semi.sup.size,
                      compactness.pca , separation.pca,
                      compactness.lsi , separation.lsi)

```






