```{r}
{library(Seurat)
  library(dplyr)
  library(Matrix)
  library(ggplot2)
  library(cowplot)
  library(EnsDb.Mmusculus.v79)
  library(Signac)
  library(S4Vectors)
  library(patchwork)
  set.seed(1234)}

```
Get files
```{r}
metacells.files <- list.files("../../../output/10xMultiomeProstateHan22/",recursive = T,pattern = "metacells.rds",full.names = T,include.dirs = T)
```


```{r}
metacell.objs <- lapply(metacells.files, FUN = function(x){ 
  x <- readRDS(x)
  DefaultAssay(x) <- "RNA"
  x[["ATAC"]] <- NULL
  return(x)
}
)
```

Same strategy as in the original study
1 - integrate RNA,
2 - discard low qual cluster
3 - integrate ATAC/RNA on remaining cells
4 - multimodal wnn

Integrating RNA assay
```{r}
metacell.objs <- lapply(X = metacell.objs, FUN = function(x) {
  x <- FindVariableFeatures(x)
})

features <- SelectIntegrationFeatures(object.list = metacell.objs)
metacell.objs <- lapply(X = metacell.objs, FUN = function(x) {
  x <- NormalizeData(x, verbose = FALSE)
  x <- ScaleData(x, features = features, verbose = FALSE)
  x <- RunPCA(x, features = features, verbose = FALSE)
})


names <- sapply(metacell.objs, function(x) {unique(x@meta.data$orig.ident)})
```

```{r}

references <- which(startsWith(names,"WT_"))
anchors <- FindIntegrationAnchors(object.list = metacell.objs, 
                                  #reference = references, 
                                  reduction = "rpca",
                                  dims = 1:50)

#all pairwise anchors
# anchors <- FindIntegrationAnchors(object.list = rna.All.combined.list, reduction = "rpca",
#                                   dims = 1:50)

#This step would waste much time
rna.All.combined.integrated <- IntegrateData(anchorset = anchors, dims = 1:50,k.weight = 50)
#rm(metacell.objs,anchors)
gc()
DefaultAssay(rna.All.combined.integrated) <- "integrated"
rna.All.combined.integrated <- ScaleData(rna.All.combined.integrated, verbose = FALSE)
rna.All.combined.integrated <- RunPCA(rna.All.combined.integrated, verbose = FALSE)
rna.All.combined.integrated <- RunUMAP(rna.All.combined.integrated, dims = 1:50)
rna.All.combined.integrated <- FindNeighbors(rna.All.combined.integrated, dims = 1:50)
rna.All.combined.integrated <- FindClusters(rna.All.combined.integrated, resolution = 0.4)
```

```{r}
UMAPPlot(rna.All.combined.integrated,label = T)

DefaultAssay(rna.All.combined.integrated) <- "RNA"
FeaturePlot(rna.All.combined.integrated,features = c("Ebf1","Igkc","Plp1"))
```
```{r}
VlnPlot(rna.All.combined.integrated,features = c("nFeature_RNA"),pt.size = 0.001,log = T)
VlnPlot(rna.All.combined.integrated,features = c("nCount_RNA"),pt.size = 0.001,log = T)

# rna.All.combined.integrated <- FindSubCluster(object = rna.All.combined.integrated,
#                                               cluster = 0,
#                                               resolution = 0.2,
#                                               graph.name = "integrated_snn")
# 
# Idents(rna.All.combined.integrated) <- "sub.cluster"
# UMAPPlot(rna.All.combined.integrated,label = T,group.by = "sub.cluster")
# VlnPlot(rna.All.combined.integrated,features = c("nFeature_RNA"),pt.size = 0.001,log = T)
# VlnPlot(rna.All.combined.integrated,features = c("nCount_RNA"),pt.size = 0.001,log = T)
```
```{r}
DefaultAssay(rna.All.combined.integrated) <- "RNA"

VlnPlot(rna.All.combined.integrated,"Ptprc")
```


```{r}
DefaultAssay(rna.All.combined.integrated) <- "RNA"
markersLowQual <- FindMarkers(rna.All.combined.integrated,ident.1 = 2,only.pos = T)

head(markersLowQual,n=20)
```

Clean data analysis

```{r}
df <- rna.All.combined.integrated@meta.data %>%
  group_by(integrated_snn_res.0.4) %>%
  summarise(medNF = median(nFeature_RNA))

lowQualClust <- df$integrated_snn_res.0.4[which.min(df$medNF)]


rna.All.combined.integrated <- subset(rna.All.combined.integrated,idents = lowQualClust,invert = T)
```


```{r}
metacell.objs <- SplitObject(rna.All.combined.integrated,split.by = "orig.ident")
references <- which(startsWith(names,"WT_"))

metacell.objs <- lapply(X = metacell.objs, FUN = function(x) {
  x <- FindVariableFeatures(x)
})

features <- SelectIntegrationFeatures(object.list = metacell.objs)
metacell.objs <- lapply(X = metacell.objs, FUN = function(x) {
  x <- NormalizeData(x, verbose = FALSE)
  x <- ScaleData(x, features = features, verbose = FALSE)
  x <- RunPCA(x, features = features, verbose = FALSE)
})



anchors <- FindIntegrationAnchors(object.list = metacell.objs, 
                                  #reference = references, 
                                  reduction = "rpca",
                                  dims = 1:50)

#all pairwise anchors
# anchors <- FindIntegrationAnchors(object.list = rna.All.combined.list, reduction = "rpca",
#                                   dims = 1:50)

#This step would waste much time
rna.All.combined.integrated <- IntegrateData(anchorset = anchors, dims = 1:50)
#rm(metacell.objs,anchors)
gc()
DefaultAssay(rna.All.combined.integrated) <- "integrated"
rna.All.combined.integrated <- ScaleData(rna.All.combined.integrated, verbose = FALSE)
rna.All.combined.integrated <- RunPCA(rna.All.combined.integrated, verbose = FALSE)
rna.All.combined.integrated <- RunUMAP(rna.All.combined.integrated, dims = 1:50)
rna.All.combined.integrated <- FindNeighbors(rna.All.combined.integrated, dims = 1:50)
rna.All.combined.integrated <- FindClusters(rna.All.combined.integrated, resolution = 0.2)
```

```{r}
UMAPPlot(rna.All.combined.integrated,label = T)
```
```{r}
VlnPlot(rna.All.combined.integrated,features = c("nFeature_RNA"),pt.size = 0.001,log = T)
VlnPlot(rna.All.combined.integrated,features = c("nCount_RNA"),pt.size = 0.001,log = T)

# rna.All.combined.integrated <- FindSubCluster(object = rna.All.combined.integrated,
#                                               cluster = 0,
#                                               resolution = 0.2,
#                                               graph.name = "integrated_snn")
# 
# Idents(rna.All.combined.integrated) <- "sub.cluster"
# UMAPPlot(rna.All.combined.integrated,label = T,group.by = "sub.cluster")
# VlnPlot(rna.All.combined.integrated,features = c("nFeature_RNA"),pt.size = 0.001,log = T)
# VlnPlot(rna.All.combined.integrated,features = c("nCount_RNA"),pt.size = 0.001,log = T)
```


#Luminal
```{r}
DefaultAssay(rna.All.combined.integrated) <- "RNA"

VlnPlot(rna.All.combined.integrated,features = c("Krt19","Nupr1","Lmo7","Ceacam1"),ncol = 2,pt.size = 0,assay = "RNA")

```
# Neuroendocrine
```{r }
VlnPlot(rna.All.combined.integrated,features = c("Chga","Nrxn1","Hcn1","Fgf14"),ncol = 2,pt.size = 0,assay = "RNA")
```
# Basal
```{r }
VlnPlot(rna.All.combined.integrated,features = c("Krt14","Krt15","Krt5","Krt17"),ncol = 2,pt.size = 0,assay = "RNA")
```

# seminal vesicle
```{r fig.height= 3, fig.width= 3.25}
VlnPlot(rna.All.combined.integrated,features = c("Svs5","Svs2","Cdo1","Fyb2"),ncol = 2,pt.size = 0,assay = "RNA")
```

# Mesenchymal 1

```{r}
VlnPlot(rna.All.combined.integrated,features = c("Col1a2","Apod","Dcn","Serping1"),ncol = 2,pt.size = 0,assay = "RNA")

```
# Mesenchymal 2
```{r}
VlnPlot(rna.All.combined.integrated,features = c("Col1a2","Apod","Flt1","Serping1"),ncol = 2,pt.size = 0,assay = "RNA")

```
# Endothelial 1

```{r }
VlnPlot(rna.All.combined.integrated,features = c("Pecam1","Emcn","Selp","Flt1"),ncol = 2,pt.size = 0,assay = "RNA")

```

# Neutrophil

```{r}
VlnPlot(rna.All.combined.integrated,features = c("S1009a","Clec4d","Cxcl2","Acod1"),ncol = 2,pt.size = 0,assay = "RNA")
```

# Macrophage
```{r}
VlnPlot(rna.All.combined.integrated,features = c("Cd74","Cd86","Cybb","Col1a"),ncol = 2,pt.size = 0,assay = "RNA")

```
# T cell

```{r }
VlnPlot(rna.All.combined.integrated,features = c("Skap1","Itk","Ptpn22","Cd3e"),ncol = 2,pt.size = 0,assay = "RNA")

```
# B cell
```{r}
VlnPlot(rna.All.combined.integrated,features = c("Igkc","Ebf1","Mef2c","Bank1"),ncol = 2,pt.size = 0,assay = "RNA")
FeaturePlot(rna.All.combined.integrated,features = c("Igkc","Ebf1","Mef2c","Bank1"))

```

# Neuroendocrine
```{r }
VlnPlot(rna.All.combined.integrated,features = c("Cadm2","Kcnb2","Kcnip4","Cntn4"),ncol = 2,pt.size = 0,assay = "RNA")
```
# Neuron
```{r }
VlnPlot(rna.All.combined.integrated,features = c("Plp1"),ncol = 2,pt.size = 0,assay = "RNA")
FeaturePlot(rna.All.combined.integrated,c("Plp1"))
```


```{r}
VlnPlot(rna.All.combined.integrated,"Ptprc",assay = "RNA")
```
```{r}
markers13 <- FindMarkers(rna.All.combined.integrated,ident.1 = 13,only.pos = T)
markers13 <- markers13[markers13$p_val_adj < 0.05,]
```

```{r}
rna.All.combined.integrated@meta.data$mc_name <- colnames(rna.All.combined.integrated)




saveRDS(rna.All.combined.integrated,"../../../output/10xMultiomeProstateHan22/rna.All.combined.integrated.rds")
remove(metacell.objs)
remove(anchors)
gc()
```

```{r}
rna.All.combined.integrated <- readRDS("../../../output/10xMultiomeProstateHan22/rna.All.combined.integrated.rds")
```

## Adding ATAC data

```{r}

```
```{r}
rna.All.combined.integrated@meta.data$mc_name <- colnames(rna.All.combined.integrated)
rna.All.combined.integrated@meta.data$mc_name <- stringr::str_split_fixed(rna.All.combined.integrated@meta.data$mc_name,"_",n=2)[,1]
rna.All.combined.integrated@meta.data$mc_name <- paste(rna.All.combined.integrated$orig.ident,rna.All.combined.integrated$mc_name,sep = "_")
rna.All.combined.integrated <- RenameCells(rna.All.combined.integrated,new.names =  rna.All.combined.integrated$mc_name )
# metacell.objs.atac <- lapply(metacells.files, FUN = function(x){ 
#   x <- readRDS(x)
#   x <- RenameCells(x,add.cell.id = unique(x$orig.ident))
#   x <- x[,colnames(x) %in% colnames(rna.All.combined.integrated)]
#   x[["RNA"]] <- NULL
#   return(x)
# }
# )

kept.cells <- colnames(rna.All.combined.integrated)
saveRDS(kept.cells,"../../../output/kept_cells.rds")
remove(rna.All.combined.integrated)
gc()
```

```{r}
# metacells.files <- rev(list.files("../../../output/10xMultiomeProstateHan22/",recursive = T,pattern = "metacells.rds",full.names = T,include.dirs = T))
# kept.cells <- as.vector(readRDS("../../../output/kept_cells.rds"))


# metacell.objs.atac <- lapply(metacells.files,function(x) {
#   x <- readRDS(x)
#   smp <- unique(x$orig.ident)
#   print(smp)
#   x <- RenameCells(x,add.cell.id = unique(x$orig.ident))
#   x <- x[,colnames(x) %in% kept.cells]
#   x[["RNA"]] <- NULL
#   gc()
#   return(x)
# })
# atac.prostate.merge <- merge(metacell.objs.atac[[1]],metacell.objs.atac[2:15])
# 
# atac.prostate.merge <- merge(metacell.objs.atac[[1]],metacell.objs.atac[2:5])
# gc()
# metacell.objs.atac <- metacell.objs.atac[6:15]
# gc()
# atac.prostate.merge.2 <- merge(metacell.objs.atac[[1]],metacell.objs.atac[2:5])
# gc()
# metacell.objs.atac <- metacell.objs.atac[6:10]
# gc()
# atac.prostate.merge.3 <- merge(metacell.objs.atac[[1]],metacell.objs.atac[2:5])
# gc()
# remove(metacell.objs.atac)
# atac.prostate.merge <- merge(atac.prostate.merge,atac.prostate.merge.2)
# saveRDS(atac.prostate.merge ,"../../../output/10xMultiomeProstateHan22/atac.prostate.merge")

atac.prostate.merge <- readRDS("../../../output/10xMultiomeProstateHan22/atac.prostate.merge.rds")
rna.All.combined.integrated <- readRDS("../../../output/10xMultiomeProstateHan22/rna.All.combined.integrated.rds")
rna.All.combined.integrated@meta.data$mc_name <- colnames(rna.All.combined.integrated)
rna.All.combined.integrated@meta.data$mc_name <- stringr::str_split_fixed(rna.All.combined.integrated@meta.data$mc_name,"_",n=2)[,1]
rna.All.combined.integrated@meta.data$mc_name <- paste(rna.All.combined.integrated$orig.ident,rna.All.combined.integrated$mc_name,sep = "_")
rna.All.combined.integrated <- RenameCells(rna.All.combined.integrated,new.names =  rna.All.combined.integrated$mc_name )
```


```{r}

#################add ATAC assay to RNA assay
rna.All.combined.integrated[["ATAC"]]<- atac.prostate.merge[["ATAC"]] # killed on laptop
remove(atac.prostate.merge)
gc()
DefaultAssay(rna.All.combined.integrated) <- "ATAC"
rna.All.combined.integrated <- RunTFIDF(rna.All.combined.integrated)
rna.All.combined.integrated <- FindTopFeatures(rna.All.combined.integrated, min.cutoff = 'q0')
rna.All.combined.integrated <- RunSVD(rna.All.combined.integrated)

DefaultAssay(rna.All.combined.integrated) <- "ATAC"
rna.All.combined.integrated <- harmony::RunHarmony(
  object = rna.All.combined.integrated,
  group.by.vars = 'orig.ident',
  reduction = 'lsi',
  assay.use = 'ATAC',
  project.dim = FALSE
)
```

```{r}
combined.metacells <- readRDS("../../../output/10xMultiomeProstateHan22/combinedMetacells.rds")


combined.metacells <- RunUMAP(combined.metacells, nn.name = "weighted.nn", reduction.name = "wnn.umap", reduction.key = "wnnUMAP_")
combined.metacells <- FindClusters(combined.metacells, resolution = 0.1,graph.name = "wsnn") 

DimPlot(combined.metacells,reduction ="wnn.umap",label = T)
```
```{r}
DefaultAssay(combined.metacells) <- "RNA"
FeaturePlot(combined.metacells,reduction ="wnn.umap",features = c("Bank1","Igkc","Ebf1","Plp1"))
```
```{r}
VlnPlot(combined.metacells,"Ptprc",assay = "RNA")

```


# Neutrophil

```{r}
VlnPlot(combined.metacells,features = c("S1009a","Clec4d","Cxcl2","Acod1"),ncol = 2,pt.size = 0,assay = "RNA")
```

# Macrophage
```{r}
VlnPlot(combined.metacells,features = c("Cd74","Cd86","Cybb","Col1a"),ncol = 2,pt.size = 0,assay = "RNA")

```
# T cell

```{r }
VlnPlot(combined.metacells,features = c("Skap1","Itk","Ptpn22","Cd3e","Tox","Cd8a"),ncol = 2,pt.size = 0,assay = "RNA")
```
# B cells

```{r}
VlnPlot(combined.metacells,features = c("Bank1","Igkc","Ebf1"))

```


```{r}
table(combined.metacells$wsnn_res.0.1)
```
```{r}
DefaultAssay(combined.metacells) <- "ATAC"
CoveragePlot(
  object = combined.metacells,
  group.by = 'wsnn_res.0.1',
  region = "chr14-99700000-99760000"
)
```


