---
title: "Figure1"
author: "Leonard Herault"
date: "`r Sys.Date()`"
output: html_document
---

SuperCellMulti identifies robust multiomics metacells increasing inter-modality consistency compared to single cells. 

# Package loading
```{r setup, include=FALSE}
library(SuperCell)
library(Seurat)
library(ggplot2)
library(scales)
```

```{r}
library(Cairo)
options(bitmapType = "cairo")
```




## Bone marrow cite seq results

Single cells
```{r single-cell loading}
bm <- readRDS("../../../output/bmCiteSeq/singlecells_analysis/seuratWNN.rds")
bm




addCellType <- function(bm) {
  bm$celltype <- as.vector(bm$celltype.l2)
  bm$celltype[startsWith(bm$celltype,"Prog_B")] <- "Prog_B"
  bm$celltype[startsWith(bm$celltype,"CD8 Effector")] <- "CD8 Effector"
  bm$celltype[startsWith(bm$celltype,"CD8 Memory")] <- "CD8 Mem"
  # bm$celltype[startsWith(bm$celltype,"CD8 ")] <- "CD8"
  # bm$celltype[startsWith(bm$celltype,"CD4 ")] <- "CD4"
  bm$celltype[bm$celltype == "Naive B"] <- "B Naive"
  bm$celltype[bm$celltype == "Memory B"] <- "B Mem"
  bm$celltype[bm$celltype == "CD4 Memory"] <- "CD4 Mem"
  bm$celltype[bm$celltype == "Plasmablast"] <- "Plasma"
  
  
  #bm$celltype[endsWith(bm$celltype,"Mono")] <- "Mono"
  
  bm$celltype[startsWith(bm$celltype,"CD56 bright NK")] <- "NK"
  bm$celltype[startsWith(bm$celltype,"Prog_Mk")] <- "MEP"
  bm$celltype[startsWith(bm$celltype,"Prog_RBC")] <- "MEP"
  bm$celltype.l2 <- factor(bm$celltype.l2) 
  bm$celltype <- factor(bm$celltype) 
  
  return(bm)
}

bm <- addCellType(bm)

colors  <- c('#E5D2DD', '#53A85F', '#F1BB72', '#F3B1A0', '#D6E7A3', '#57C3F3', '#476D87',
             '#E95C59', '#E59CC4', '#AB3282', '#BD956A', '#8C549C',
             '#9FA3A8', '#E0D4CA', '#5F3D69', '#58A4C3', "#b20000",'#E4C755', '#F7F398',
             '#AA9A59', '#E63863', '#E39A35', '#C1E6F3', '#6778AE', '#91D0BE', '#B53E2B',
             '#712820', '#DCC1DD', '#CCE0F5', '#CCC9E6', '#625D9E', '#68A180', '#3A6963',
             '#968175')

show_col(colors)



color.celltypes.bm  <- c("MEP" = '#D6E7A3',
                         "gdT" = '#E95C59',
                         "GMP" = '#476D87',
                         "LMPP" = '#3A6963',
                         "Prog_DC" =  '#625D9E', 
                         'Prog_B' = "#AA9A59",
                         "CD14 Mono" =  "#F1BB72",
                         "CD16 Mono" = "#53A85F",
                         "CD4 Mem" = '#91D0BE',
                         "CD4 Naive" = "#F3B1A0",
                         "CD8 Effector" = "#AB3282",
                         "CD8 Mem" = "#BD956A",
                         "CD8 Naive" = "#8C549C",
                         "cDC2" = "#9FA3A8",
                         "gdT" = "#E0D4CA",
                         "MAIT" = "#E4C755",
                         "Plasma" = "#ff6db6",
                         'B Mem' = "#F7F398",
                         "B Naive" = "#E63863",
                         "NK" = "#6778AE",
                         "pDC" = "#712820",
                         "Treg" ='#57C3F3',
                         "HSC" = "#58A4C3")

# 
# color.celltypes.l2 <- colors[1:length(unique(bm$celltype.l2))]
# bm$celltype.l2 <- factor(bm$celltype.l2) 
# 
# 
# names(color.celltypes.l2) <- levels(bm$celltype.l2)
# 
# color.celltypes <- c(na.exclude(color.celltypes.l2[levels(bm$celltype)]),
#                      "MEP" = "#b20000",
#                      "CD4" =  '#F1BB72',
#                      "CD8 Effector" = '#57C3F3',
#                      'CD8 Memory' = '#E95C59',
#                      "Prog_B" ='#C1E6F3')
# 
# bm$celltype <- factor(bm$celltype) 
# 
# 
# names(color.celltypes) <- levels(bm$celltype)
# names(color.celltypes.l2) <- levels(bm$celltype.l2)



```

```{r control_single_cell}
DimPlot(bm,group.by = "celltype.l2",cols = colors)
DimPlot(bm,group.by = "celltype",cols = color.celltypes.bm)


```



# Metacalls on single cell WNN UMAP

```{r load_mc_g75}
bm.supercell.adt <- readRDS("../../../output/bmCiteSeq//SuperCellADT/g75/seurat.cite.mc.rds")
bm.supercell.adt <- addCellType(bm.supercell.adt)

bm.seacells.adt <- readRDS("../../../output/bmCiteSeq/seacellsADT//g75/seurat.cite.mc.rds")
bm.seacells.adt <- addCellType(bm.seacells.adt)

bm.seacells.rna <- readRDS("../../../output/bmCiteSeq/seacellsRNA//g75/seurat.cite.mc.rds")
bm.seacells.rna <- addCellType(bm.seacells.rna)

bm.supercell.rna <- readRDS("../../../output/bmCiteSeq/SuperCellRNA//g75/seurat.cite.mc.rds")
bm.supercell.rna <- addCellType(bm.supercell.rna)

bm.supercell.multi <- readRDS("../../../output/bmCiteSeq//SuperCellMulti//g75/seurat.cite.mc.rds")
bm.supercell.multi <- addCellType(bm.supercell.multi)

bm.metacell.rna <- readRDS("../../../output/bmCiteSeq/MetaCellRNA//g75/seurat.cite.mc.rds")
bm.metacell.rna <- addCellType(bm.metacell.rna)


```



```{r}
cn <- c(colnames(bm.supercell.multi@meta.data)[!colnames(bm.supercell.multi@meta.data) %in% c("innerNormVar","celltype")],"input","gamma")
metrics <- data.frame()

for (g in c(20,50,75,100)){
  # for (i in c('SuperCellMulti','SuperCellRNA',"SuperCellADT","randomMetacells","seacellsRNA","seacellsADT","MetaCellRNA")){
  for (i in c('SuperCellMulti','SuperCellRNA',"SuperCellADT","seacellsRNA","seacellsADT","MetaCellRNA")){  
    file <- paste0("../../../output/bmCiteSeq/",
                   i,"/g",
                   g,
                   "/seurat.cite.mc.rds")
    if (file.exists(file)) {
      pbmc.mc <- readRDS(file)
      if (i == '') {i <- "MULTI"}
      pbmc.mc@meta.data$input <- i
      pbmc.mc@meta.data$gamma <- g
      metrics <- rbind(metrics,pbmc.mc@meta.data[,cn])
    }
  }
  
  
}
```

```{r}
library(ggpubr)
fig1.A <- DimPlotSC(seurat = bm,
                    seurat.mc = bm.supercell.multi,
                    metacell.col = "celltype",
                    sc.col = "celltype",
                    mc.color = color.celltypes.bm ,
                    sc.color = color.celltypes.bm) + theme_classic()  +
  guides(fill=guide_legend(ncol =2,title = "Cell types",
                           override.aes = list(size=4)),
         colour = "none",
         size = guide_legend(title = "Size"))



umap.sc.multi <-  fig1.A + NoLegend() +scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),
                                                  breaks = c(100,200,300,400))

legend.celltypes <- ggpubr::get_legend(fig1.A+scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),
                                                         breaks = c(100,200,300,400)),
                                       position  = c(0.5,0)) 

umap.sc.rna <- DimPlotSC(seurat = bm,
                         seurat.mc = bm.supercell.rna,
                         metacell.col = "celltype",
                         sc.col = "celltype",
                         mc.color = color.celltypes.bm ,
                         sc.color = color.celltypes.bm) + theme_classic() + NoLegend() +scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),
                                                                                                   breaks = c(100,200,300,400))
umap.sc.adt <- DimPlotSC(seurat = bm,
                         seurat.mc = bm.supercell.adt,
                         metacell.col = "celltype",
                         sc.col = "celltype",
                         mc.color = color.celltypes.bm ,
                         sc.color = color.celltypes.bm) + theme_classic() + NoLegend() +scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),
                                                                                                   breaks = c(100,200,300,400))
umap.sea.rna <- DimPlotSC(seurat = bm,
                          seurat.mc = bm.seacells.rna,
                          metacell.col = "celltype",
                          sc.col = "celltype",
                          mc.color = color.celltypes.bm ,
                          sc.color = color.celltypes.bm) + theme_classic() + NoLegend() +scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),
                                                                                                    breaks = c(100,200,300,400))
umap.sea.adt <- DimPlotSC(seurat = bm,
                          seurat.mc = bm.seacells.adt,
                          metacell.col = "celltype",
                          sc.col = "celltype",
                          mc.color = color.celltypes.bm ,
                          sc.color = color.celltypes.bm) + theme_classic() + NoLegend() +scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),
                                                                                                    breaks = c(100,200,300,400))
umap.mc.rna <- DimPlotSC(seurat = bm,
                         seurat.mc = bm.metacell.rna,
                         metacell.col = "celltype",
                         sc.col = "celltype",
                         mc.color = color.celltypes.bm ,
                         sc.color = color.celltypes.bm) + theme_classic() + NoLegend() +scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),
                                                                                                   breaks = c(100,200,300,400))
blank <- element_blank()
```


```{r fig.height=5,fig.width=7}
fig1.A$layers[[1]] <- NULL
fig1.A
```


## Supplementary fig1F

```{r fig.height=10,fig.width=11}

cowplot::plot_grid(umap.sc.multi + ggtitle("SuperCell Protein+RNA"),umap.sc.adt + ggtitle("SuperCell Protein") ,umap.sc.rna + ggtitle("SuperCell RNA"),
                   legend.celltypes,umap.sea.adt + ggtitle("SEACells Protein"), umap.sea.rna + ggtitle("SEACells RNA"),
                   blank,blank,umap.mc.rna + ggtitle("MetaCell2 RNA")
)
```
```{r fig.height=10,fig.width=11}
# umap.sc <- DimPlot(pbmc,group.by = "celltype",cols = color.celltypes.pbmc,reduction = "wnn.umap") + theme_classic() + ggtitle("Single cells") + NoLegend()
# umap.sc

umap.sc <- umap.sc.multi
umap.sc$layers[[2]] <- NULL

legend.celltypes <- ggpubr::get_legend(fig1.A +scale_size(limits = c(0,max(metrics$size[metrics$gamma == 75])),
                                                          breaks = c(100,200,300,400)) + theme(
                                                            # legend.position = "bottom",        # Position legend at the bottom
                                                            legend.box = "horizontal"# One column for shapes
                                                          ) +guides(
                                                            fill = guide_legend(ncol =2,title = "Cell types",
                                                                                override.aes = list(size=4)),  # One column for colors
                                                            size = guide_legend(ncol = 1)
                                                          ))

figS2A <- cowplot::plot_grid(umap.sc.multi + ggtitle("SuperCell Protein+RNA"),
                             umap.sc.adt + ggtitle("SuperCell Protein") ,
                             umap.sc.rna + ggtitle("SuperCell RNA"),
                             umap.sc + ggtitle("Single-cells"),
                             umap.sea.adt + ggtitle("SEACells Protein"), 
                             umap.sea.rna + ggtitle("SEACells RNA"),
                             legend.celltypes,blank,
                             umap.mc.rna + ggtitle("MetaCell2 RNA")
)
figS2A
```
```{r}
dir.create("../../../pdf_files/FigS2/", recursive = T, showWarnings = F )
pdf(file = "../../../pdf_files/FigS2/figS2A.pdf",height = 11,width=11)
figS2A
dev.off()
```
## Fig 2A benchmark plot

set method color
```{r}
library(scales)
# library(ggthemes)

input.colors.cite <- c("#E69F00","#56B4E9","#009E73","darkgrey") #colorblind_pal()(8)[2:4]


names(input.colors.cite) <- c("Protein","Protein+RNA","RNA","None")
```





```{r}
#Set compactness to 0 (best score) for metacell of size 1
table(metrics[is.na(metrics$compactness_apca),"gamma"])
table(metrics[is.na(metrics$compactness_pca),"input"])


#metrics$compactness_lsi[is.na(metrics$compactness_lsi)] <- 0

#metrics$compactness_pca[is.na(metrics$compactness_pca)] <- 0


metrics$gamma <- factor(as.character(metrics$gamma),levels =c(20,50,75,100))

metrics$method <- plyr::mapvalues(x= metrics$input, 
                                  from = c('SuperCellMulti','SuperCellRNA',"SuperCellADT","randomMetacells","seacellsRNA","seacellsADT","MetaCellRNA"),
                                  to = c('SuperCell Protein+RNA','SuperCell RNA',"SuperCell Protein","Random None","SEACells RNA","SEACells Protein","MetaCell2 RNA"))

metrics$tool <- stringr::str_split_fixed(metrics$method,pattern = " ",n = 2)[,1]
metrics$input <- stringr::str_split_fixed(metrics$method,pattern = " ",n = 2)[,2]


metrics$input <- factor(as.character(metrics$input),levels = c("RNA","Protein","Protein+RNA","None"))

method.levels <- c('SuperCell Protein+RNA',"SuperCell Protein","SEACells Protein",
                   'SuperCell RNA',"SEACells RNA","MetaCell2 RNA","Random None")

metrics$method <- factor(metrics$method,
                         levels = method.levels)
# 
```


```{r fig.height=4,fig.width=4}
comparisons <- list(c('SuperCell Protein+RNA',"SuperCell Protein"),
                    c('SuperCell Protein+RNA',"SEACells Protein"),
                    c('SuperCell Protein+RNA','SuperCell RNA'),
                    c('SuperCell Protein+RNA',"SEACells RNA"),
                    c('SuperCell Protein+RNA',"MetaCell2 RNA"))

comparison.inter.modality <- list(c('SuperCell Protein',"SEACells Protein"),
                                  c('SuperCell RNA','SEACells RNA'),
                                  c('SuperCell RNA',"MetaCell2 RNA"))

library(ggsignif)
metrics$purity <- metrics$celltype.l2_purity
purity.bmc.cite.g20 <- ggplot(metrics[metrics$gamma %in% c(20),],aes(y=purity,x = method,fill = input)) +
  geom_boxplot() + theme_bw() +
  #facet_wrap("gamma",nrow = 1) + 
  scale_y_continuous(limits = c(0.1,1.5),breaks = c(0.2,0.6,1)) + 
  geom_signif(comparisons = comparisons,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 2)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 2) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom") + scale_fill_manual(values = input.colors.cite)

purity.bmc.cite.g20 + NoLegend()
```
```{r fig.height=4,fig.width=4}
purity.bmc.cite.g75 <- ggplot(metrics[metrics$gamma %in% c(75),],aes(y=purity,x = method,fill = input)) + 
  geom_boxplot() + theme_bw() +
  #facet_wrap("gamma",nrow = 1) + 
  scale_y_continuous(limits = c(0.1,1.5),breaks = c(0.2,0.6,1)) + 
  geom_signif(comparisons = comparisons,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 2)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 2) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite)


purity.bmc.cite.g75 + NoLegend()
```


```{r fig.height=4,fig.width=4}
use.gamma = c(20,75) 

benchTable <- data.frame()
methodToBenchFiles <- c('seurat.cite.mc.txt','seurat.cite.mc.txt','seurat.cite.mc.txt','seacellMemberships.txt',"seacellMemberships.txt","MetaCellMemberships.txt")
methodToTools <- c('SuperCell','SuperCell','SuperCell','SEACells',"SEACells","MetaCell")
names(methodToBenchFiles) <- c('SuperCellMulti','SuperCellRNA','SuperCellADT',"seacellsADT","seacellsRNA","MetaCellRNA")

for (g in c(use.gamma)){
  for (i in names(methodToBenchFiles) ){
    bench <- read.table(paste0("../../../benchmark/bmCiteSeq/",
                               i,"/g",
                               g,"/",
                               "/benchIdentification.txt"),header = T)
    
    bench$method <- i
    bench$gamma <- g
    benchTable <- rbind(benchTable,bench)
    
  }}

# ggplot(benchTable,aes(x = method,y = cpu_time, fill= method)) + geom_bar(stat = "identity") +
#   scale_x_discrete(guide = guide_axis(angle = 60))+ ylab("cpu time (s)")+ NoLegend() +
#   ggplot(benchTable,aes(x = method,y = max_pss/1024, fill= method)) + geom_bar(stat = "identity") + ylab("memory (GB)") +
#   scale_x_discrete(guide = guide_axis(angle = 60))
# 
# 
#  +
#   ggplot(benchTable,aes(x = method,y = s, fill= method)) + geom_bar(stat = "identity") +
#   scale_x_discrete(guide = guide_axis(angle = 60))+ ylab("Runtime (s)")+ NoLegend()

benchTable$gamma <- factor(benchTable$gamma)
benchTable <-  rbind(benchTable,c(rep(1,10),"Random","20"))
benchTable <-  rbind(benchTable,c(rep(1,10),"Random","75"))

benchTable$method <- plyr::mapvalues(x= benchTable$method, 
                                     from = c('SuperCellMulti','SuperCellRNA',"SuperCellADT",
                                              "Random","seacellsRNA","seacellsADT","MetaCellRNA"),
                                     to = c('SuperCell Protein+RNA','SuperCell RNA',"SuperCell Protein",
                                            "Random None","SEACells RNA","SEACells Protein","MetaCell2 RNA"))

benchTable$input <- stringr::str_split_fixed(benchTable$method,pattern = " ",n=2)[,2]

benchTable$input <- factor(as.character(benchTable$input),levels = c('Protein+RNA',"Protein","RNA","None"))


benchTable$method <- factor(benchTable$method,
                            levels = method.levels)

benchTable$cpu_time <- as.numeric(benchTable$cpu_time )


cpu.time.plot.g75 <- ggplot(benchTable[benchTable$gamma == 75 & benchTable$method != "Random None",],aes(x = method,y = cpu_time,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_y_log10()  +
  ylab("cpu time (s)") + 
  scale_fill_manual(values = input.colors.cite) + theme(axis.title.x = element_blank())


cpu.time.plot.g20 <- ggplot(benchTable[ benchTable$gamma == 20 & benchTable$method != "Random None",],aes(x = method,y = cpu_time,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_y_log10()   +
  ylab("cpu time (s)") + 
  scale_fill_manual(values = input.colors.cite)+ theme(axis.title.x = element_blank())

# cpu.time.plot <- ggplot(benchTable[benchTable$method != "Random None" & g == 75,],aes(x = method,y = cpu_time,fill = input)) + 
#   geom_bar(stat = "identity", position="dodge") +
#   scale_x_discrete(guide = guide_axis(angle = 60)) +
#   ylab("cpu time (s)") + 
#   theme(legend.position = c(0.8,0.6),
#         axis.title.x = element_blank(),
#         axis.text.x = element_blank()) + 
#   scale_fill_manual(values = input.colors.cite)

cpu.time.plot.g75 + NoLegend()

cpu.time.plot.g20 + NoLegend()

```

```{r fig.height=4,fig.width=4}


cpu.time.plot.g75 <- ggplot(benchTable[benchTable$gamma == 75 & benchTable$method != "Random None",],aes(x = method,y = cpu_time,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_y_log10()  +
  ylab("cpu time (s)") + 
  scale_fill_manual(values = input.colors.cite) + theme(axis.title.x = element_blank())


cpu.time.plot.g20 <- ggplot(benchTable[ benchTable$gamma == 20 & benchTable$method != "Random None",],aes(x = method,y = cpu_time,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_y_log10()   +
  ylab("cpu time (s)") + 
  scale_fill_manual(values = input.colors.cite)+ theme(axis.title.x = element_blank())



cpu.time.plot.g75 + NoLegend()

cpu.time.plot.g20 + NoLegend()
```
```{r fig.height=4,fig.width=4}


mem.plot.g75 <- ggplot(benchTable[benchTable$gamma == 75 & benchTable$method != "Random None",],aes(x = method,y = as.numeric(max_rss)/1024,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_y_log10()  +
  ylab("Memory (Gb)") + 
  scale_fill_manual(values = input.colors.cite) + theme(axis.title.x = element_blank())


mem.plot.g20 <- ggplot(benchTable[ benchTable$gamma == 20 & benchTable$method != "Random None",],aes(x = method,y = as.numeric(max_rss)/1024,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_y_log10()   +
  ylab("Memory (Gb)") + 
  scale_fill_manual(values = input.colors.cite) + 
  scale_fill_manual(values = input.colors.cite)+ theme(axis.title.x = element_blank())


mem.plot.g75 + NoLegend()

mem.plot.g20 + NoLegend()
```
## With preprocessing
```{r fig.height=3,fig.width=4}
use.gamma = c(20,75) 

benchTable <- data.frame()
benchTable2 <- data.frame()


methodToBenchFiles <- c('benchIdentification.txt','benchIdentification.txt','benchIdentification.txt','benchIdentification.txt',"benchIdentification.txt","benchIdentification.txt")
methodToTools <- c('SuperCell','SuperCell','SuperCell','SEACells',"SEACells","MetaCell")
names(methodToBenchFiles) <- c('SuperCellMulti','SuperCellRNA','SuperCellADT',"seacellsADT","seacellsRNA","MetaCellRNA")

preprocess.bench.rna <- read.table("../../../benchmark/bmCiteSeq/singlecells_analysis/seurat.RNA.txt",header = T) 

preprocess.bench.atac <- read.table("../../../benchmark/bmCiteSeq/singlecells_analysis/seurat.ADT.txt",header = T) 

preprocess.bench.multi <- read.table("../../../benchmark/bmCiteSeq/singlecells_analysis/seurat_multimodal.txt",header = T) 



for (g in c(use.gamma)){
  for (i in names(methodToBenchFiles) ){
    
    bench <- read.table(paste0("../../../benchmark/bmCiteSeq/",
                               i,"/g",
                               g,"/",
                               methodToBenchFiles[i]),header = T)
    
    
    bench2 <- bench[c("s","max_rss","max_pss","cpu_time")]
    if (i != "MetaCellRNA") {
      if(endsWith(x = i,suffix = "RNA")) {
        preprocess <- preprocess.bench.rna
      }
      if(endsWith(x = i,suffix = "ATAC")) {
        preprocess <- preprocess.bench.atac
      }
      if(endsWith(x = i,suffix = "Multi")) {
        preprocess <- preprocess.bench.multi
      }
      
      bench2 <- colSums(rbind(bench2[c("s","cpu_time")],
                              preprocess[c("s","cpu_time")]))
      
      bench2$max_rss <- max(unlist(c(bench["max_rss"],preprocess["max_rss"])))
      bench2$max_rss <- max(unlist(c(bench["max_rss"],preprocess["max_rss"])))
    } else {
      bench2 <- bench[c("s","cpu_time","max_rss")]
    }
    bench$method <- i
    bench$gamma <- g
    bench2$method <- i
    bench2$gamma <- g
    
    benchTable <- rbind(benchTable,bench)
    benchTable2 <- rbind(benchTable2,bench2)
    
  }}

getBenchTable <- function(benchTable) {
  benchTable$gamma <- factor(benchTable$gamma)
  # benchTable <-  rbind(benchTable,c(rep(1,10),"Random","20"))
  # benchTable <-  rbind(benchTable,c(rep(1,10),"Random","75"))
  
  benchTable$method <- plyr::mapvalues(x= benchTable$method, 
                                       from = c('SuperCellMulti','SuperCellRNA',"SuperCellADT",
                                                "seacellsRNA","seacellsADT","MetaCellRNA"),
                                       to = c('SuperCell Protein+RNA','SuperCell RNA',"SuperCell Protein",
                                              "SEACells RNA","SEACells Protein","MetaCell2 RNA"))
  
  benchTable$input <- stringr::str_split_fixed(benchTable$method,pattern = " ",n=2)[,2]
  
  benchTable$input <- factor(as.character(benchTable$input),levels = c('Protein+RNA',"Protein","RNA","None"))
  benchTable$method <- factor(benchTable$method,
                              levels = method.levels)
  
  benchTable$cpu_time <- as.numeric(benchTable$cpu_time )
  benchTable$s <- as.numeric(benchTable$s )
  benchTable$max_rss <- as.numeric(benchTable$max_rss )
  
  return(benchTable)
}

benchTable <- getBenchTable(benchTable)
benchTable2 <- getBenchTable(benchTable2)



cite.cpu.time.plot.g75.id <- ggplot(benchTable[benchTable$gamma == 75,],aes(x = method,y = cpu_time,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("cpu time (s)") + 
  scale_fill_manual(values = input.colors.cite)


cite.run.time.plot.g75.id <- ggplot(benchTable[benchTable$gamma == 75,],aes(x = method,y = s/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Runtime (min)") + 
  scale_fill_manual(values = input.colors.cite)


cite.cpu.time.plot.g20.id <- ggplot(benchTable[ benchTable$gamma == 20,],aes(x = method,y = cpu_time,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_y_log10()   +
  ylab("cpu time (s)") + 
  scale_fill_manual(values = input.colors.cite)

cite.run.time.plot.g20.id <- ggplot(benchTable[benchTable$gamma == 20,],aes(x = method,y = s/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Runtime (min)") + 
  scale_fill_manual(values = input.colors.cite)



```
With preprocessing for SuperCell and SEACells
```{r}
cite.cpu.time.plot.g75 <- ggplot(benchTable2[benchTable2$gamma == 75,],aes(x = method,y = cpu_time/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60))  + scale_y_log10()   +
  ylab("cpu time (min)") + 
  scale_fill_manual(values = input.colors.cite)


cite.run.time.plot.g75 <- ggplot(benchTable2[benchTable2$gamma == 75,],aes(x = method,y = s/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60))  + scale_y_log10()   +
  ylab("Runtime (min)") + 
  scale_fill_manual(values = input.colors.cite)


cite.cpu.time.plot.g20 <- ggplot(benchTable2[ benchTable2$gamma == 20,],aes(x = method,y = cpu_time/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_y_log10()   +
  ylab("cpu time (min)") + 
  scale_fill_manual(values = input.colors.cite)

cite.run.time.plot.g20 <- ggplot(benchTable2[benchTable2$gamma == 20,],aes(x = method,y = s/60,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() + scale_y_log10()   +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Runtime (min)") + 
  scale_fill_manual(values = input.colors.cite)

input.colors.cite

cite.cpu.time.plot.g75
cite.run.time.plot.g75

cite.cpu.time.plot.g20
cite.run.time.plot.g20
```
Memory with preprocessing
```{r}
cite.memory.plot.g75 <- ggplot(benchTable2[benchTable2$gamma == 75,],aes(x = method,y = max_rss/1024,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Memory (GB)") + 
  scale_fill_manual(values = input.colors.cite)


cite.memory.plot.g75.id <- ggplot(benchTable[benchTable$gamma == 75,],aes(x = method,y = max_rss/1024,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Memory (GB)") + 
  scale_fill_manual(values = input.colors.cite)


cite.memory.plot.g20 <- ggplot(benchTable2[ benchTable2$gamma == 20,],aes(x = method,y = max_rss/1024,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_y_log10()   +
  ylab("Memory (GB)") + 
  scale_fill_manual(values = input.colors.cite)

cite.memory.plot.g20.id <- ggplot(benchTable[benchTable$gamma == 20,],aes(x = method,y = max_rss/1024,fill = input)) + 
  geom_bar(stat = "identity", position="dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Memory (GB)") + 
  scale_fill_manual(values = input.colors.cite)



cite.memory.plot.g75
cite.memory.plot.g75.id

cite.memory.plot.g20
cite.memory.plot.g20.id
```

Combined scalability plot g20
```{r}
benchTable2$workflow <- "with preprocessing"
benchTable$workflow <- "identification only"





benchTable2$workflow <- factor(benchTable2$workflow,levels = c("with preprocessing","identification only"))

cite.memory.plot.g20 <- ggplot(benchTable2[benchTable2$gamma == 20,],
                               aes(x = method,y = max_rss/1024,fill = input)) + 
  geom_bar(stat = "identity",col = "black",position = "dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Memory (GB)") + 

  scale_fill_manual(values = input.colors.cite) + theme(axis.title.x = element_blank())

cite.cpu.time.plot.g20 <- ggplot(benchTable2[ benchTable2$gamma == 20,],
                                 aes(x = method,y = cpu_time/60,fill = input)) + 
  geom_bar(stat = "identity",col = "black",position = "dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_y_log10()   +
  ylab("cpu time (min)") + 

  scale_fill_manual(values = input.colors.cite)  + theme(axis.title.x = element_blank())

cite.run.time.plot.g20 <- ggplot(benchTable2[benchTable2$gamma == 20,],
                                 aes(x = method,y = s/60,fill = input)) + 
  geom_bar(stat = "identity",col = "black",position = "dodge") + theme_bw() + scale_y_log10()   +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Runtime (min)") + 
  
  scale_fill_manual(values = input.colors.cite) + theme(axis.title.x = element_blank())

cite.cpu.time.plot.g20
cite.run.time.plot.g20

cite.memory.plot.g20

```

at gamma 75

```{r}
benchTable2$workflow <- "with preprocessing"
benchTable$workflow <- "identification only"



benchTable2$workflow <- factor(benchTable2$workflow,levels = c("with preprocessing","identification only"))

cite.memory.plot.g75 <- ggplot(benchTable2[benchTable2$gamma == 75,],
                               aes(x = method,y = max_rss/1024,fill = input)) + 
  geom_bar(stat = "identity",col = "black",position = "dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60))  +
  ylab("Memory (GB)") + 
  
  scale_fill_manual(values = input.colors.cite) + theme(axis.title.x = element_blank())

cite.cpu.time.plot.g75 <- ggplot(benchTable2[ benchTable2$gamma == 75,],
                                 aes(x = method,y = cpu_time/60,fill = input)) + 
  geom_bar(stat = "identity",col = "black",position = "dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + scale_y_log10()   +
  ylab("cpu time (min)") + 
  
  scale_fill_manual(values = input.colors.cite)  + theme(axis.title.x = element_blank())

cite.run.time.plot.g75 <- ggplot(benchTable2[benchTable2$gamma == 75,],
                                 aes(x = method,y = s/60,fill = input)) + 
  geom_bar(stat = "identity",col = "black",position = "dodge") + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60))  + scale_y_log10()   +
  ylab("Runtime (min)") + 

  scale_fill_manual(values = input.colors.cite) + theme(axis.title.x = element_blank())

cite.cpu.time.plot.g75
cite.run.time.plot.g75

cite.memory.plot.g75

```




```{r fig.height=4,fig.width=4}
hline <- median(metrics[metrics$gamma %in% c(75) & metrics$method == "SuperCell Protein+RNA","compactness_pca"])
compactness_pca.bmc.cite.g75 <- ggplot(metrics[metrics$gamma %in% c(75),],aes(y=compactness_pca,x = method,fill = input)) + 
  geom_boxplot() + theme_bw() + 
  scale_y_log10(limits = c(0.00001,20000))+  geom_hline(yintercept =hline,color = "darkblue",linetype = "longdash")  +
  geom_signif(comparisons = comparisons,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 2)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 2) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Compactness RNA")


compactness_pca.bmc.cite.g75 + NoLegend()
```
```{r fig.height=4,fig.width=4}
hline <- median(metrics[metrics$gamma %in% c(75) & metrics$method == "SuperCell Protein+RNA","compactness_pca"])

compactness_apca.bmc.cite.g75 <- ggplot(metrics[metrics$gamma %in% c(75),],aes(y=compactness_apca,x = method,fill = input)) + 
  geom_boxplot() +theme_bw()+
  geom_boxplot() + scale_y_log10(limits = c(0.000001,30000))+  geom_hline(yintercept =hline,color = "darkblue",linetype = "longdash")  +
  geom_signif(comparisons = comparisons,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 2)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 2) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Compactness Prot.") + theme(axis.title.x = element_blank())


compactness_apca.bmc.cite.g75 + NoLegend()
```



```{r fig.height=4,fig.width=4}
separation_pca.g75 <- ggplot(metrics[metrics$gamma %in% c(75),],aes(y=separation_pca,x = method,fill = input)) + 
  geom_boxplot() + theme_bw() + scale_y_log10(limits = c(0.0005,2000))+
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 2)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 2) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Separation RNA") + theme(axis.title.x = element_blank())


separation_pca.g75 + NoLegend()
```



```{r fig.height=4,fig.width=4}
separation_apca.g75 <- ggplot(metrics[metrics$gamma %in% c(75),],aes(y=separation_apca,x = method,fill = input)) + 
  geom_boxplot() + theme_bw() +  scale_y_log10(limits = c(0.001,500))+
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 2)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 2) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Separation Prot.") + theme(axis.title.x = element_blank())


separation_apca.g75 + NoLegend()
```


New version no reversed, scaling without random

```{r fig.width=4,fig.height=4}
library(dplyr)
bench.75.no.random <- metrics[metrics$gamma %in% c(75) & metrics$method != "Random None",]
bench.75.no.random$pct_known <- 0

# add semi sup tests for scaling comp/sep
semi.sup.multi <- read.csv("../../../output/bmCiteSeq//SuperCellMulti/testSemiSup/g75/results_test_semisup.csv",row.names = 1)
semi.sup.multi$gamma <- 75
semi.sup.multi$input <- "Protein+RNA" 
semi.sup.multi$tool <- "ssSuperCell" 
semi.sup.multi$method <- "SuperCell Protein+RNA" 

semi.sup.rna <- read.csv("../../../output/bmCiteSeq//SuperCellRNA//testSemiSup/g75/results_test_semisup.csv",row.names = 1)
semi.sup.rna$gamma <- 75
semi.sup.rna$input <- "RNA" 
semi.sup.rna$tool <- "ssSuperCell" 
semi.sup.rna$method <- "SuperCell RNA" 

cn <- colnames(bench.75.no.random)[colnames(bench.75.no.random) %in% colnames(semi.sup.multi)]

bench.75.no.random <- rbind(bench.75.no.random[,cn],semi.sup.multi[,cn],semi.sup.rna[,cn])



minMaxScaling <- function(x) {
  y <- (x-min(x))/(max(x)-min(x))
  return(y)
}

bench.75.no.random$compactness_pca_scaled <- minMaxScaling(bench.75.no.random$compactness_pca)
bench.75.no.random$compactness_apca_scaled <- minMaxScaling(bench.75.no.random$compactness_apca)

bench.75.no.random$multimodal_compactness <- (bench.75.no.random$compactness_pca_scaled + bench.75.no.random$compactness_apca_scaled) / 2


bench.75.no.random$separation_pca_norm <- (bench.75.no.random$separation_pca)
bench.75.no.random$separation_apca_norm <- (bench.75.no.random$separation_apca)

bench.75.no.random$separation_pca_scaled <- minMaxScaling(bench.75.no.random$separation_pca_norm)
bench.75.no.random$separation_apca_scaled <- minMaxScaling(bench.75.no.random$separation_apca_norm)

bench.75.no.random$multimodal_separation <- (bench.75.no.random$separation_pca_scaled + bench.75.no.random$separation_apca_scaled) / 2

# limits <- bench.75.no.random[bench.75.no.random$method != "Random None",] %>%
#   group_by(method) %>%
#   summarize(
#     ymin = quantile(multimodal_compactness, 0.25) - 1.5 * IQR(multimodal_compactness),
#     ymax = quantile(multimodal_compactness, 0.75) + 1.5 * IQR(multimodal_compactness)
#   ) %>%
#   ungroup() %>%
#   summarize(
#     ymin = min(ymin),
#     ymax = max(ymax)
#   )
#
# step_increase <- 0.075*0.25/(limits$ymax-limits$ymin)

bench.75.unsup <- bench.75.no.random[bench.75.no.random$tool != "ssSuperCell",]

sig.multimodal.compactness.g75  <- ggplot(bench.75.unsup,aes(y=multimodal_compactness,x = method,fill = input)) +
  geom_boxplot(outlier.shape = NA) + theme_bw() +
  #facet_wrap("gamma",nrow = 1) +
  #ylim(c(0,1.425)) +
  geom_signif(comparisons = comparisons,
              y_position = 0.08,
              step_increase=0.03,
              tip_length = 0.007,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,
              y_position = 0.08,
              step_increase=0.03,
              tip_length = 0.007,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) +
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Multimodal Compactness") +  # Hides outliers
  coord_cartesian(ylim = c(0, 0.245))


sig.multimodal.compactness.g75
```




```{r fig.height=4,fig.width=4}



sig.multimodal.separation.g75 <- ggplot(bench.75.unsup,aes(y=multimodal_separation,x = method,fill = input)) + 
  geom_boxplot(outlier.shape = NA)  + theme_bw() +
  
  geom_signif(comparisons = comparisons,
              step_increase=0.03,
              tip_length = 0.007,
              map_signif_level=T,
              extend_line = -0.005,textsize = 3,
              y_position = 0.1) +
  geom_signif(comparisons = comparison.inter.modality,
              step_increase=0.03,
              tip_length = 0.007,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3,
              y_position = 0.1) +
  scale_x_discrete(guide = guide_axis(angle = 60))  + scale_fill_manual(values = input.colors.cite) + ylab("Multimodal Separation")  +  # Hides outliers
  coord_cartesian(ylim = c(0, 0.25)) 
#coord_cartesian(ylim = c(0.82, 1.23))  + theme_void() + NoLegend()
sig.multimodal.separation.g75

# full.multimodal.separation.g75 <- cowplot::plot_grid(sig.multimodal.separation.g75,multimodal_separation.75+ NoLegend(), rel_heights = c(0.2,0.8),align = "v",ncol = 1)
# 
# full.multimodal.separation.g75
```



```{r  fig.height=4,fig.width=4}




sig.celltype.l2_purity.g75  <- ggplot(bench.75.unsup,aes(y=celltype.l2_purity,x = method,fill = input)) + 
  geom_boxplot()  + theme_bw() +
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,
              step_increase=0.2,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,
              step_increase=0.2,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Purity")  +
  scale_y_continuous(limits = c(0.15,1.75),breaks =c(0.4,0.7,1))

sig.celltype.l2_purity.g75
# Hides outliers
#coord_cartesian(ylim = c(0, limits$ymax))   # Sets y-axis limits


# full.celltype.l2_purity.g75 <-cowplot::plot_grid(sig.celltype.l2_purity.g75,celltype.l2_purity.g75+ NoLegend(), rel_heights = c(0.2,0.8),align = "v",ncol = 1)
# full.celltype.l2_purity.g75
```

```{r  fig.height=4,fig.width=4}
size.g75 <- ggplot(bench.75.unsup,aes(y=size,x = method,fill = input)) + 
  geom_boxplot()  + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Size") + theme(axis.title.x = element_blank()) + NoLegend()
size.g75
```



gamma 75 whole process

```{r fig.height=5,fig.width=3}
library(patchwork)
cowplot::plot_grid(cite.run.time.plot.g75 + NoLegend(),cite.memory.plot.g20+ NoLegend(),ncol=1)

cite.run.time.plot.g75 <- cite.run.time.plot.g75 + NoLegend() +
  theme(axis.title.x = element_blank()) +
  scale_x_discrete(guide = guide_axis(angle = 60)) # Remove x-axis text/ticks

cite.memory.plot.g75 <- cite.memory.plot.g75 +
  theme(axis.title.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60)) 

# Combine plots in a single column with same width
# scalability.g75 <- cite.run.time.plot.g75 / cite.memory.plot.g75 + plot_layout(heights = c(1, 1))
# scalability.g75
```




```{r fig.height=5,fig.width=3}
sig.celltype.l2_purity.g75 <- sig.celltype.l2_purity.g75  + NoLegend() +
  theme(axis.text.x = element_blank(),axis.title.x = element_blank()) 

sig.multimodal.compactness.g75 <-  sig.multimodal.compactness.g75 + NoLegend() +
  theme(axis.title.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60)) 

comp.pur.g75 <- sig.celltype.l2_purity.g75 / sig.multimodal.compactness.g75 + plot_layout(heights = c(1, 1))

comp.pur.g75
```

```{r  fig.height=5,fig.width=3}
leg.input <- get_legend(cite.run.time.plot.g75 + theme(legend.position = "right"))

sig.multimodal.separation.g75 <- sig.multimodal.separation.g75 + NoLegend() +
  theme(axis.text.x = element_blank(),axis.title.x = element_blank()) 

# sep.g75 <-  sig.multimodal.separation.g75 + NoLegend() +
#   theme(axis.title.x = element_blank())  +
#   scale_x_discrete(guide = guide_axis(angle = 60)) 
# sep.g75<- sep.g75 / leg.input + plot_layout(heights = c(1, 1))
# sep.g75

```
```{r fig.height=6,fig.width=9}
# plot.main.g75 <- cowplot::plot_grid(comp.pur.g75,sep.g75,scalability.g75,nrow = 1)
# plot.main.g75
```

Sparsity reduction
```{r  fig.height=5,fig.width=2.5}
bm$resolution <- "Single-cells"
bm.supercell.multi$resolution <- "Metacells"
meta.sc.mc <- rbind(bm@meta.data[,c("nCount_RNA","nFeature_RNA","nCount_ADT","nFeature_ADT","resolution")],
                    bm.supercell.multi@meta.data[,c("nCount_RNA","nFeature_RNA","nCount_ADT","nFeature_ADT","resolution")])

meta.sc.mc$resolution <- factor(meta.sc.mc$resolution,levels = c("Metacells","Single-cells"))

meta.sc.mc$resolution <- factor(meta.sc.mc$resolution,levels = c("Metacells","Single-cells"))

nFeature_RNA <- ggplot(meta.sc.mc,aes(x=resolution,y=nFeature_RNA,fill = resolution)) + geom_violin(scale = "width") + theme_bw() + theme(axis.title.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  scale_fill_manual(values = c("#56B4E9", "#D55E00")) #colorblind_pal()(8)[c(3,7)]


nCount_RNA <- ggplot(meta.sc.mc,aes(x=resolution,y=nCount_RNA,fill = resolution)) + geom_violin(scale = "width") + theme_bw() +  theme(axis.title.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  scale_fill_manual(values = c("#56B4E9", "#D55E00")) #colorblind_pal()(8)[c(3,7)]

sparsity.reduction.g75 <- cowplot::plot_grid(nFeature_RNA+ NoLegend(),nCount_RNA+ NoLegend(),ncol = 1)
sparsity.reduction.g75
```


```{r}
nFeature_RNA <- nFeature_RNA  + NoLegend() +
  theme(axis.text.x = element_blank(),axis.title.x = element_blank()) + ylab("Detected Genes")

nCount_RNA <-  nCount_RNA + NoLegend() + scale_y_log10() + 
  theme(axis.title.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60))+ ylab("RNA Counts (UMI)")

sparsity.reduction.g75 <- nFeature_RNA / nCount_RNA + plot_layout(heights = c(1, 1))

sparsity.reduction.g75
```

```{r fig.height=5.25,fig.width=13.75}
Fig2DEF <- cowplot::plot_grid(fig1.A+theme(plot.margin = unit(c(80,0,80,0),units = "pt")),
                              wrap_plots(nFeature_RNA, 
                                         sig.celltype.l2_purity.g75, 
                                         sig.multimodal.separation.g75, 
                                         guide_area(),
                                         nCount_RNA,sig.multimodal.compactness.g75,
                                         cite.cpu.time.plot.g75,
                                         nrow = 2,ncol = 4,guides = "collect")& 
                                theme(legend.spacing.y = unit(-0.35, "line")),
                              nrow = 1,
                              rel_widths = c(3,4.5))
Fig2DEF
```


```{r}
dir.create("../../../pdf_files/Fig2/", recursive = T, showWarnings = F )
pdf("../../../pdf_files/Fig2/fig2DEF.pdf",height = 5.25,width = 13.75)
Fig2DEF
dev.off()
```




```{r fig.height=12,fig.width=5}
figS2B <- cowplot::plot_grid(cowplot::plot_grid(compactness_pca.bmc.cite.g75+ NoLegend() + 
                                                    theme(axis.title.x = element_blank()),
                                                compactness_apca.bmc.cite.g75 + 
                                                  NoLegend() + 
                                                  theme(axis.title.x = element_blank()),
                                                separation_pca.g75 + 
                                                  NoLegend() + 
                                                  theme(axis.title.x = element_blank()),
                                                separation_apca.g75 + 
                                                  NoLegend() + 
                                                  theme(axis.title.x = element_blank()), 
                                                
                                                size.g75 + NoLegend() + theme(axis.title.x = element_blank()),
                                                cite.memory.plot.g75 + 
                                                  NoLegend() + 
                                                  theme(axis.title.x = element_blank())+
                                                  scale_x_discrete(guide = guide_axis(angle = 60)),
                                                ncol = 2),
                             get_legend(cite.memory.plot.g75),ncol = 1,rel_heights = c(14,3))

figS2B

```


```{r fig.height=12,fig.width=5}
# figS2B <- cowplot::plot_grid(cowplot::plot_grid(compactness_pca.bmc.cite.g75+ 
#                                         NoLegend() + 
#                                         theme(axis.title.x = element_blank()) +
#                                         scale_x_discrete(guide = guide_axis(angle = 60)),
#                                       
#                                       compactness_lsi.bmc.cite. + NoLegend() + theme(axis.title.x = element_blank()) +
#                                         scale_x_discrete(guide = guide_axis(angle = 60)),
#                                       size.g20 + NoLegend() + theme(axis.title.x = element_blank()) +
#                                         scale_x_discrete(guide = guide_axis(angle = 60)),
#                                       separation_pca.g20 + NoLegend() + theme(axis.title.x = element_blank()) +
#                                         scale_x_discrete(guide = guide_axis(angle = 60)),
#                                       separation_lsi.g20 + NoLegend() + theme(axis.title.x = element_blank()) +
#                                         scale_x_discrete(guide = guide_axis(angle = 60)), 
#                                       multiome.cpu.time.plot.g20 + NoLegend() +
#                                         scale_x_discrete(guide = guide_axis(angle = 60)),ncol = 2),get_legend(cite.memory.plot.g75),ncol = 1,rel_heights = c(14,3))
# 
# figS1B
```
```{r}
pdf(file = "../../../pdf_files/FigS2/figS2B_g75.pdf",height = 12,width=5)
figS2B
dev.off()
```
```{r}
bench.20 <- metrics[metrics$gamma %in% c(20),]
table(bench.20$size == 1,bench.20$method)
```

Set a compactness of 0 for singleton gives
Warning: Removed 79 rows containing non-finite outside the scale range (`stat_signif()`) correspond to singletons.

```{r fig.height=4,fig.width=4}


bench.20$compactness_apca[bench.20$size == 1] <- 0
bench.20$compactness_pca[bench.20$size == 1] <- 0


hline <- median(bench.20[bench.20$gamma %in% c(20) & bench.20$method == "SuperCell Protein+RNA","compactness_pca"])
compactness_pca.bmc.cite.g20 <- ggplot(bench.20[bench.20$gamma %in% c(20),],aes(y=compactness_pca,x = method,fill = input)) + 
  geom_boxplot() + theme_bw() +
  scale_y_log10(limits =c(0.000001, 120000))+
  geom_hline(yintercept =hline,color = "darkblue",linetype = "longdash")  +
  geom_signif(comparisons = comparisons,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Compactness RNA")


compactness_pca.bmc.cite.g20 + NoLegend()
```
```{r fig.height=4,fig.width=4}
hline <- median(bench.20[(bench.20$gamma %in% c(20) & bench.20$method == "SuperCell Protein+RNA") ,"compactness_apca"])

compactness_apca.bmc.cite.g20 <- ggplot(bench.20[bench.20$gamma %in% c(20),],aes(y=compactness_apca,x = method,fill = input)) + 
  geom_boxplot() + theme_bw() +scale_y_log10(limits =c(0.000001, 120000))+  
  geom_hline(yintercept =hline,color = "darkblue",linetype = "longdash")  +
  geom_signif(comparisons = comparisons,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.15,map_signif_level=T,extend_line = -0.005,textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Compactness Prot.") + theme(axis.title.x = element_blank())


compactness_apca.bmc.cite.g20 + NoLegend()
```



```{r fig.height=4,fig.width=4}
separation_pca.g20 <- ggplot(bench.20[bench.20$gamma %in% c(20),],aes(y=separation_pca,x = method,fill = input)) + 
  geom_boxplot() + theme_bw() + scale_y_log10(limits =c(0.0005, 1200))+
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,step_increase=0.125,map_signif_level=T,extend_line = -0.005,textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Separation RNA") + theme(axis.title.x = element_blank())


separation_pca.g20 + NoLegend()
```



```{r fig.height=4,fig.width=4}
separation_apca.g20 <- ggplot(bench.20[bench.20$gamma %in% c(20),],aes(y=separation_apca,x = method,fill = input)) + 
  geom_boxplot() + theme_bw() + scale_y_log10(limits =c(0.001, 1200))+
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,step_increase=0.125,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,
              step_increase=0.125,
              map_signif_level=T,
              extend_line = -0.005,textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Separation Prot.") + theme(axis.title.x = element_blank()) 


separation_apca.g20 + NoLegend()
```


```{r fig.height=4,fig.width=4}
library(dplyr)

bench.20.no.random <-  bench.20[bench.20$method != "Random None",]
minMaxScaling <- function(x) {
  y <- (x-min(x))/(max(x)-min(x))
  return(y)
}

bench.20.no.random$compactness_pca_scaled <- minMaxScaling(bench.20.no.random$compactness_pca)
bench.20.no.random$compactness_apca_scaled <- minMaxScaling(bench.20.no.random$compactness_apca)

bench.20.no.random$multimodal_compactness <- (bench.20.no.random$compactness_pca_scaled + bench.20.no.random$compactness_apca_scaled) / 2


sig.multimodal.compactness.g20  <- ggplot(bench.20.no.random,aes(y=multimodal_compactness,x = method,fill = input)) + 
  geom_boxplot(outlier.shape = NA) + theme_bw() +
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,
              step_increase=0.025,
              y_position = 0.12,
              tip_length = 0.007,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,
              step_increase=0.025,
              y_position = 0.12,
              map_signif_level=T,
              tip_length = 0.007,
              extend_line = -0.005,
              textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Multimodal Compactness")  +  # Hides outliers
  coord_cartesian(ylim = c(0, 0.25))  + NoLegend()
sig.multimodal.compactness.g20

# multimodal_compactness.20 <- ggplot(bench.20[bench.20$method != "Random None",],aes(y=multimodal_compactness,x = method,fill = input)) + 
#   geom_boxplot(outlier.shape = NA) +
#   scale_x_discrete(guide = guide_axis(angle = 60)) + 
#   theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Multimodal Compactness")  +  # Hides outliers
#   coord_cartesian(ylim = c(limits$ymin,1.001)) + theme(axis.title.x = element_blank())
# 
# multimodal.compactness.g20 <- cowplot::plot_grid(sig,multimodal_compactness.20+ NoLegend(), rel_heights = c(0.2,0.8),align = "v",ncol = 1)
# multimodal.compactness.g20

```

```{r fig.height=4,fig.width=4}

bench.20.no.random$separation_pca_norm <- (bench.20.no.random$separation_pca)
bench.20.no.random$separation_apca_norm <- (bench.20.no.random$separation_apca)
minMaxScaling <- function(x) {
  y <- (x-min(x))/(max(x)-min(x))
  return(y)
}

bench.20.no.random$separation_pca_scaled <- minMaxScaling(bench.20.no.random$separation_pca_norm)
bench.20.no.random$separation_apca_scaled <- minMaxScaling(bench.20.no.random$separation_apca_norm)

bench.20.no.random$multimodal_separation <- (bench.20.no.random$separation_pca_scaled + bench.20.no.random$separation_apca_scaled) / 2


sig.multimodal.separation.g20 <- ggplot(bench.20.no.random,aes(y=multimodal_separation,x = method,fill = input)) + 
  geom_boxplot(outlier.shape = NA) + theme_bw() +
  
  geom_signif(comparisons = comparisons,
              step_increase=0.0125,
              tip_length = 0.003,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3,
              y_position = 0.03) +
  geom_signif(comparisons = comparison.inter.modality,
              step_increase=0.0125,
              tip_length = 0.003,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3,
              y_position = 0.03) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Multimodal Compactness")  +
  coord_cartesian(ylim = c(0, 0.1))  + NoLegend()
sig.multimodal.separation.g20

# multimodal_separation.20 <- ggplot(bench.20[bench.20$method != "Random None",],aes(y=multimodal_separation,x = method,fill = input)) + 
#   geom_boxplot(outlier.shape = NA) +
#   scale_x_discrete(guide = guide_axis(angle = 60)) + 
#   theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Multimodal Separation")  +  # Hides outliers
#   coord_cartesian(ylim = c(0, limits$ymax)) + theme(axis.title.x = element_blank())  # Sets y-axis limits
# 
# 
# multimodal.separation.g20 <- cowplot::plot_grid(sig,multimodal_separation.20+ NoLegend(), rel_heights = c(0.2,0.8),align = "v",ncol = 1)
# 
# multimodal.separation.g20

```



```{r  fig.height=4,fig.width=4}




# limits <- bench.75[bench.75$method != "Random None",] %>%
#   group_by(method) %>%
#   summarize(
#     ymin = min(celltype.l2_purity),
#     ymax = 1
#   ) %>%
#   ungroup() %>%
#   summarize(
#     ymin = min(ymin),
#     ymax = max(ymax)
#   )
# step_increase <- 0.075*0.25/(limits$ymax-limits$ymin)

celltype.l2_purity.g20 <- ggplot(bench.20.no.random,aes(y=celltype.l2_purity,x = method,fill = input)) + 
  geom_boxplot() + theme_bw() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Purity") + theme(axis.title.x = element_blank())


plot_data <- ggplot_build(celltype.l2_purity.g20)
y_limits <- plot_data$layout$panel_params[[1]]$y.range

# step_increase <-  (3*0.075*0.25)/(y_limits[2]-y_limits[1])
step_increase <-  .23*(1.3-1.02)
sig.celltype.l2_purity.g20  <- ggplot(bench.20[bench.20$method != "Random None",],aes(y=celltype.l2_purity,x = method,fill = input)) + 
  geom_boxplot() + theme_bw() +
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,
              step_increase=0.13,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,
              step_increase=0.13,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Purity")  +  # Hides outliers
  NoLegend() + scale_y_continuous(limits = c(0.15,1.55),breaks = c(0.2,0.6,1))
sig.celltype.l2_purity.g20

# Hides outliers
#coord_cartesian(ylim = c(0, limits$ymax))   # Sets y-axis limits

# 
# celltype.l2_purity.g20 <-cowplot::plot_grid(sig,celltype.l2_purity.g20+ NoLegend(), rel_heights = c(0.2,0.8),align = "v",ncol = 1)
# celltype.l2_purity.g20
```

```{r  fig.height=4,fig.width=4}
size.g20 <- ggplot(bench.20[bench.20$method != "Random None",],aes(y=size,x = method,fill = input)) + 
  geom_boxplot() + theme_bw() + 
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Size") + theme(axis.title.x = element_blank()) + NoLegend()
size.g20
```

## Fig

```{r  fig.height=6.5,fig.width=14}
figS2EF <- cowplot::plot_grid(purity.bmc.cite.g20+ NoLegend() + theme(axis.title.x = element_blank()),
                             sig.multimodal.compactness.g20+ NoLegend() + theme(axis.title.x = element_blank()),
                             sig.multimodal.separation.g20+ NoLegend() + theme(axis.title.x = element_blank()),
                             size.g20 + NoLegend() + theme(axis.title.x = element_blank()),
                             compactness_pca.bmc.cite.g20+ NoLegend() + theme(axis.title.x = element_blank()),
                             compactness_apca.bmc.cite.g20 + NoLegend() + theme(axis.title.x = element_blank()),
                             separation_pca.g20 + NoLegend() + theme(axis.title.x = element_blank()),
                             separation_apca.g20 + NoLegend() + theme(axis.title.x = element_blank()),
                             cite.cpu.time.plot.g20+ theme(axis.title.x = element_blank()) + NoLegend(),
                             cite.memory.plot.g20+ theme(axis.title.x = element_blank())+ NoLegend(),
                             leg.input,
                             byrow = F,nrow = 2)
figS2EF
```


```{r fig.height=6.5,fig.width=14}
pdf(file = "../../../pdf_files/FigS2/figS2EF_g20.pdf",height = 6.5,width=14)
figS2EF
dev.off()
```


```{r}
bm.supercell.multi.g20 <- readRDS("../../../output/bmCiteSeq//SuperCellMulti//g20/seurat.cite.mc.rds")
bm.supercell.multi.g20 <- addCellType(bm.supercell.multi.g20)
figSupCov <- DimPlotSC(seurat = bm,
                       seurat.mc = bm.supercell.multi.g20,
                       metacell.col = "celltype",
                       sc.col = "celltype",
                       mc.color = color.celltypes.bm,
                       sc.color = color.celltypes.bm) + theme_classic()  +
  guides(fill=guide_legend(ncol =2,title = "Cell types",
                           override.aes = list(size=4)),
         colour = "none",
         size = guide_legend(title = "Size"))

figSupCov
```

Sparsity reduction g20
```{r  fig.height=5,fig.width=2.5}
bm$resolution <- "Single-cells"
bm.supercell.multi.g20$resolution <- "Metacells"
meta.sc.mc <- rbind(bm@meta.data[,c("nCount_RNA","nFeature_RNA","resolution")],
                    bm.supercell.multi.g20@meta.data[,c("nCount_RNA","nFeature_RNA","resolution")])

meta.sc.mc$resolution <- factor(meta.sc.mc$resolution,levels = c("Metacells","Single-cells"))

nFeature_RNA <- ggplot(meta.sc.mc,aes(x=resolution,y=nFeature_RNA,fill = resolution)) + geom_violin(scale = "width") + theme_bw() + 
  theme(axis.title.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  scale_fill_manual(values = c("#56B4E9", "#D55E00")) #colorblind_pal()(8)[c(3,7)]


nCount_RNA <- ggplot(meta.sc.mc,aes(x=resolution,y=nCount_RNA,fill = resolution)) + geom_violin(scale = "width")  + theme_bw() + 
  theme(axis.title.x = element_blank())  + scale_y_log10() +
  scale_x_discrete(guide = guide_axis(angle = 60)) + 
  scale_fill_manual(values = c("#56B4E9", "#D55E00")) #colorblind_pal()(8)[c(3,7)]


sparsity.reduction.counts.g20 <- wrap_plots(nCount_RNA+ NoLegend(),nCount_RNA+ NoLegend(),ncol = 1)

sparsity.reduction.counts.g20
```


```{r}
nFeature_RNA <- nFeature_RNA  + NoLegend() +
  theme(axis.text.x = element_blank(),axis.title.x = element_blank()) + ylab("Detected Genes")

nCount_RNA <-  nCount_RNA + NoLegend() +
  theme(axis.title.x = element_blank())  +
  scale_x_discrete(guide = guide_axis(angle = 60))+ ylab("RNA Counts (UMI)")

sparsity.reduction.g20 <- nFeature_RNA / nCount_RNA + plot_layout(heights = c(1, 1))
sparsity.reduction.g20

```
```{r fig.height=5,fig.width=9}
figS2CD <- cowplot::plot_grid(figSupCov+theme(plot.margin = unit(c(50,25,50,25),units = "pt")),
                             wrap_plots(nFeature_RNA, nCount_RNA,ncol = 1),rel_widths = c(3,1))

figS2CD
```
```{r}
pdf(file = "../../../pdf_files/FigS2/figS2CD.pdf",height = 5,width=9)
figS2CD
dev.off()
```






## Anti correlation

```{r fig.height=5,fig.width=7}
acr.prot.sc <- FeatureScatter(bm[,bm$celltype.l1 %in% "T cell" ],"adt_CD8a","adt_CD4",group.by = "celltype", cols = color.celltypes.bm,plot.cor = F) + xlab("Prot. CD8A") + ylab("Prot. CD4")

DefaultAssay(bm.supercell.multi) <- "ADT"
bm.supercell.multi <- NormalizeData(bm.supercell.multi,normalization.method = "CLR",margin = 2)

acr.prot.supercell.multi <- FeatureScatter.SuperCell(bm.supercell.multi[,bm.supercell.multi$celltype.l1 %in% "T cell" ],
                                                     "adt_CD8a","adt_CD4",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("Prot. CD8A") + ylab("Prot. CD4")  + ggtitle(label = "SuperCell",subtitle = "Protein + RNA")  + theme_classic()  


DefaultAssay(bm.supercell.rna) <- "ADT"
bm.supercell.rna <- NormalizeData(bm.supercell.rna,normalization.method = "CLR",margin = 2)

acr.prot.supercell.rna <- FeatureScatter.SuperCell(bm.supercell.rna[,bm.supercell.rna$celltype.l1 %in% "T cell" ],
                                                   "adt_CD8a","adt_CD4",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("Prot. CD8A") + ylab("Prot. CD4") + ggtitle(label = "SuperCell",subtitle = "RNA")  + theme_classic()  + NoLegend() 


DefaultAssay(bm.supercell.adt) <- "ADT"
bm.supercell.adt <- NormalizeData(bm.supercell.adt,normalization.method = "CLR",margin = 2)

acr.prot.supercell.prot <- FeatureScatter.SuperCell(bm.supercell.adt[,bm.supercell.adt$celltype.l1 %in% "T cell" ],
                                                    "adt_CD8a","adt_CD4",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("Prot. CD8A") + ylab("Prot. CD4") + ggtitle(label = "SuperCell",subtitle = "Protein")  + theme_classic()  + NoLegend() 


DefaultAssay(bm.seacells.rna) <- "ADT"
bm.seacells.rna <- NormalizeData(bm.seacells.rna,normalization.method = "CLR",margin = 2)

acr.prot.seacells.rna <- FeatureScatter.SuperCell(bm.seacells.rna[,bm.seacells.rna$celltype.l1 %in% "T cell" ],
                                                  "adt_CD8a","adt_CD4",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("Prot. CD8A") + ylab("Prot. CD4") + ggtitle(label = "SEACells",subtitle = "RNA")  + theme_classic()  + NoLegend() 


DefaultAssay(bm.seacells.adt) <- "ADT"
bm.seacells.adt <- NormalizeData(bm.seacells.adt,normalization.method = "CLR",margin = 2)

acr.prot.seacells.prot <- FeatureScatter.SuperCell(bm.seacells.adt[,bm.seacells.adt$celltype.l1 %in% "T cell" ],
                                                   "adt_CD8a","adt_CD4",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("Prot. CD8A") + ylab("Prot. CD4")  + ggtitle(label = "SEACells",subtitle = "Protein") + theme_classic()  + NoLegend() 



DefaultAssay(bm.metacell.rna) <- "ADT"
bm.metacell.rna <- NormalizeData(bm.metacell.rna,normalization.method = "CLR",margin = 2)

acr.prot.metacell.rna <- FeatureScatter.SuperCell(bm.metacell.rna[,bm.metacell.rna$celltype.l1 %in% "T cell" ],
                                                  "adt_CD8a","adt_CD4",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("Prot. CD8A") + ylab("Prot. CD4")+ ggtitle(label = "MetaCell2",subtitle = "RNA") + theme_classic()  + NoLegend() 



cowplot::plot_grid(acr.prot.supercell.multi + NoLegend(),acr.prot.supercell.prot,acr.prot.seacells.prot,
                   acr.prot.supercell.rna,acr.prot.seacells.rna,acr.prot.metacell.rna)


```

```{r fig.height=5,fig.width=10}
acr.prot.supercell.multi + 
  guides(colour = "none",
         fill = guide_legend(ncol =2,title = "Cell types",
                             override.aes = list(size=4)))

fig2G <- wrap_plots(acr.prot.sc + ggtitle("Single-cells") + theme_classic() + NoLegend(),
                    acr.prot.supercell.multi + 
                      guides( fill = guide_legend(ncol =2,title = "Cell types",
                                                  override.aes = list(size=4)),  # One column for colors
                              size = "none")+ theme(legend.key.size = unit(1, 'lines')),acr.prot.supercell.prot,acr.prot.seacells.prot,
                    guide_area(),acr.prot.supercell.rna,acr.prot.seacells.rna,acr.prot.metacell.rna,guides = "collect",nrow = 2)
fig2G
```



RNA progenitors

```{r fig.height=5,fig.width=7}
acr.prot.sc <- FeatureScatter(bm[,bm$celltype.l1 %in%  "Progenitor cells" ],"rna_FLT3","rna_GATA1",group.by = "celltype", cols = color.celltypes.bm,plot.cor = F) + xlab("RNA FLT3") + ylab("RNA GATA1") + theme_classic() + ggtitle("Single-cells")

DefaultAssay(bm.supercell.multi) <- "RNA"
bm.supercell.multi <- NormalizeData(bm.supercell.multi)

acr.prot.supercell.multi <- FeatureScatter.SuperCell(bm.supercell.multi[,bm.supercell.multi$celltype.l1 %in%  "Progenitor cells" ],
                                                     "rna_FLT3","rna_GATA1",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("RNA FLT3") + ylab("RNA GATA1")  + ggtitle(label = "SuperCell",subtitle = "Protein + RNA")  + theme_classic()  


DefaultAssay(bm.supercell.rna) <- "RNA"
bm.supercell.rna <- NormalizeData(bm.supercell.rna)

acr.prot.supercell.rna <- FeatureScatter.SuperCell(bm.supercell.rna[,bm.supercell.rna$celltype.l1 %in%  "Progenitor cells" ],
                                                   "rna_FLT3","rna_GATA1",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("RNA FLT3") + ylab("RNA GATA1") + ggtitle(label = "SuperCell",subtitle = "RNA")  + theme_classic()  + NoLegend() 


DefaultAssay(bm.supercell.adt) <- "RNA"
bm.supercell.adt <- NormalizeData(bm.supercell.adt)

acr.prot.supercell.prot <- FeatureScatter.SuperCell(bm.supercell.adt[,bm.supercell.adt$celltype.l1 %in%  "Progenitor cells" ],
                                                    "rna_FLT3","rna_GATA1",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("RNA FLT3") + ylab("RNA GATA1") + ggtitle(label = "SuperCell",subtitle = "Protein")  + theme_classic()  + NoLegend() 


DefaultAssay(bm.seacells.rna) <- "RNA"
bm.seacells.rna <- NormalizeData(bm.seacells.rna)

acr.prot.seacells.rna <- FeatureScatter.SuperCell(bm.seacells.rna[,bm.seacells.rna$celltype.l1 %in%  "Progenitor cells" ],
                                                  "rna_FLT3","rna_GATA1",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("RNA FLT3") + ylab("RNA GATA1") + ggtitle(label = "SEACells",subtitle = "RNA")  + theme_classic()  + NoLegend() 


DefaultAssay(bm.seacells.adt) <- "RNA"
bm.seacells.adt <- NormalizeData(bm.seacells.adt)

acr.prot.seacells.prot <- FeatureScatter.SuperCell(bm.seacells.adt[,bm.seacells.adt$celltype.l1 %in%  "Progenitor cells" ],
                                                   "rna_FLT3","rna_GATA1",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("RNA FLT3") + ylab("RNA GATA1")  + ggtitle(label = "SEACells",subtitle = "Protein") + theme_classic()  + NoLegend() 



DefaultAssay(bm.metacell.rna) <- "RNA"
bm.metacell.rna <- NormalizeData(bm.metacell.rna)

acr.prot.metacell.rna <- FeatureScatter.SuperCell(bm.metacell.rna[,bm.metacell.rna$celltype.l1 %in%  "Progenitor cells" ],
                                                  "rna_FLT3","rna_GATA1",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("RNA FLT3") + ylab("RNA GATA1")+ ggtitle(label = "MetaCell2",subtitle = "RNA") + theme_classic()  + NoLegend() 



cowplot::plot_grid(acr.prot.supercell.multi + NoLegend(),acr.prot.supercell.prot,acr.prot.seacells.prot,
                   acr.prot.supercell.rna,acr.prot.seacells.rna,acr.prot.metacell.rna)


```

```{r fig.height=5,fig.width=10}
acr.prot.supercell.multi + 
  guides(colour = "none",
         fill = guide_legend(ncol =2,title = "Cell types",
                             override.aes = list(size=4)))

fig2H <- wrap_plots(acr.prot.sc + ggtitle("Single-cells") + theme_classic() + NoLegend(),
                    acr.prot.supercell.multi + 
                      guides( fill = guide_legend(ncol =2,title = "Cell types",
                                                  override.aes = list(size=4)),  # One column for colors
                              size = "none")+ theme(legend.key.size = unit(1, 'lines')),acr.prot.supercell.prot,acr.prot.seacells.prot,
                    guide_area(),acr.prot.supercell.rna,acr.prot.seacells.rna,acr.prot.metacell.rna,guides = "collect",nrow = 2)
fig2H
```


```{r fig.height=5,fig.width=17.5}
fig2GH <- cowplot::plot_grid(fig2G,fig2H)
fig2GH
```

```{r}
pdf("../../../pdf_files/Fig2/fig2GH.pdf",height = 5,width = 17.5)
fig2GH
dev.off()
```


## Purity by major types
```{r fig.height=6,fig.width=5}


sig.celltype.l2_purity.g75.major.type  <- ggplot(bench.75.no.random,aes(y=celltype.l2_purity,x = method,fill = input)) + 
  geom_boxplot() + theme_bw() + facet_wrap("~celltype.l1") + 
  #facet_wrap("gamma",nrow = 1) + 
  #ylim(c(0,1.425)) + 
  geom_signif(comparisons = comparisons,
              step_increase=0.15,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3)+
  geom_signif(comparisons = comparison.inter.modality,
              step_increase=0.15,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3) +
  scale_x_discrete(guide = guide_axis(angle = 80)) + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Purity")  +
  scale_y_continuous(limits = c(0.15,1.6),breaks =c(0.4,0.7,1)) + theme(axis.title.x = element_blank())

sig.celltype.l2_purity.g75.major.type + NoLegend()
```

```{r}
# pdf("../../../pdf_files/Fig2/figS2E.pdf",height = 6,width = 5)
# sig.celltype.l2_purity.g75.major.type + NoLegend()
# dev.off()
```


```{r fig.height=3,fig.width=3}
pdf("../../../pdf_files/FigS2/figS2GH.pdf",height = 6,width = 5)
sig.celltype.l2_purity.g75.major.type + NoLegend()
wnn.weights<- VlnPlot(bm,'RNA.weight',group.by = "celltype.l1",sort = T,pt.size = 0) + NoLegend(
) + ggtitle("RNA Weights")+ theme(axis.title.y = element_blank()) + coord_flip() 
wnn.weights
```

```{r}
pdf("../../../pdf_files/FigS2/figS2H.pdf",height = 7,width = 3)
wnn.weights + theme(text = element_text(size = 20),
                    title = element_text(size = 20))
dev.off()
```



Metcalls2 outliers
```{r fig.height= 3,fig.width=3}
bm.metacell.rna.g20 <- readRDS("../../../output/bmCiteSeq/MetaCellRNA/g20/seurat.cite.mc.rds")
outliers.mc2 <- data.frame("outliers" = c(length(which(is.na(bm.metacell.rna.g20@misc$membership))),
                                          length(which(is.na(bm.metacell.rna@misc$membership)))),
                           "graining_level" = c("20","75"))
outliers.mc2$perc.outliers <-label_percent()(outliers.mc2$outliers/ncol(bm))
outliers.mc2
outliers.mc2 <- ggplot(outliers.mc2,aes( x= graining_level, y = outliers)) + geom_bar(stat = "identity", position="dodge") + ylab("MetaCell2 outliers") + xlab("graining level") + geom_text(aes(label = perc.outliers),col = "red")
outliers.mc2
```



```{r}
bench.75.no.random.semi.sup <- bench.75.no.random[bench.75.no.random$tool == "ssSuperCell",]

bench.75.no.random.semi.sup$pct_known <- factor(paste0(as.character(bench.75.no.random.semi.sup$pct_known),"%"), levels = rev(c("100%","75%","50%","25%","0%") ))

```


```{r fig.height=4,fig.width=4}

comparisons.semi.sup <- list(
  c("0%","25%"),
  c("0%","50%"),
  c("0%","75%"),
  c("0%","100%")
)


purity.pbmc.multiome.g75.semi.sup <- ggplot(bench.75.no.random.semi.sup[bench.75.no.random.semi.sup$input == "Protein+RNA",],
                                            aes(y=celltype.l2_purity,x = pct_known,fill = input)) + 
  geom_boxplot()  + theme_bw()  + 
  geom_signif(comparisons = comparisons.semi.sup,
              step_increase=0.125,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3)+
  scale_y_continuous(breaks = c(0.4,0.6,0.8,1),limits = c(0.3,1.35)) + 
  
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + theme_bw() + xlab("Annotated cells") +ylab("Purity") + NoLegend()


purity.pbmc.multiome.g75.semi.sup 
```
```{r fig.width=4, fig.height=4}

size.pbmc.multiome.g75.semi.sup <- ggplot(bench.75.no.random.semi.sup[bench.75.no.random.semi.sup$input == "Protein+RNA",],
                                          aes(y=size,x = pct_known,fill = input)) + 
  geom_boxplot() + theme_bw()  + 
  geom_signif(comparisons = comparisons.semi.sup,
              step_increase=0.125,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3)+
  ylim(c(0,525))+
  
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + xlab("Annotated cells") + NoLegend()


size.pbmc.multiome.g75.semi.sup
```

```{r fig.height=4,fig.width=4}

multimodal_compactness.75.semi.sup <- ggplot(bench.75.no.random.semi.sup[bench.75.no.random.semi.sup$input == "Protein+RNA",],aes(y=multimodal_compactness,x = pct_known,fill = input)) + 
  geom_boxplot(outlier.shape = NA)  + theme_bw() + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Multimodal Compactness")  +  # Hides outliers
  coord_cartesian(ylim = c(0,0.08))   + NoLegend() + 
  geom_signif(comparisons = comparisons.semi.sup,
              y_position = 0.04,
              step_increase=0.015,
              map_signif_level=T,
              extend_line = -0.005,
              tip_length = 0.005,
              textsize = 3) + xlab("Annotated cells")
multimodal_compactness.75.semi.sup

```
```{r fig.height=4,fig.width=4}
multimodal_separation.75.semi.sup <- ggplot(bench.75.no.random.semi.sup[bench.75.no.random.semi.sup$input == "Protein+RNA",],aes(y=multimodal_separation,x = pct_known,fill = input)) + 
  geom_boxplot(outlier.shape = NA) +theme_bw() +
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Multimodal Separation")  +  # Hides outliers
  coord_cartesian(ylim = c(0, 0.195))+ NoLegend() + 
  geom_signif(comparisons = comparisons.semi.sup,
              y_position = 0.085,
              step_increase=0.035,
              map_signif_level=T,
              extend_line = -0.005,
              tip_length = 0.01,
              textsize = 3) + xlab("Annotated cells")
multimodal_separation.75.semi.sup
```
```{r fig.height=2.75,fig.width = 7}
wrap_plots(purity.pbmc.multiome.g75.semi.sup,multimodal_compactness.75.semi.sup,multimodal_separation.75.semi.sup,nrow = 1)

pdf("../../../pdf_files/Fig2/fig2J_semi_sup.pdf",height = 2.75,width = 7)
wrap_plots(purity.pbmc.multiome.g75.semi.sup,multimodal_compactness.75.semi.sup,multimodal_separation.75.semi.sup,nrow = 1)
dev.off()
```






```{r fig.height=4,fig.width=18}
plot.list <- list()
for (p in c(100,75,50,25,0)) {
  sobj <- readRDS(paste0("../../../output/bmCiteSeq//SuperCellMulti/testSemiSup/g75/guiding_label_",p,"_pct_hiddenseurat.mc.rds"))
  sobj <- addCellType(sobj)
  plot.list[[paste0("pct_",p)]] <- DimPlotSC(seurat = bm,
                                             seurat.mc = sobj,
                                             metacell.col = "celltype",
                                             sc.col = "celltype",
                                             mc.color = color.celltypes.bm ,
                                             sc.color = color.celltypes.bm) + theme_classic() + ggtitle(label = "SuperCell Protein+RNA",
                                                                                                        subtitle = paste0(100-p, "% annotated cells")) + 
    scale_size(limits = c(0,max(bench.75.no.random.semi.sup$size)),breaks = c(50,100,150,200))  +
    guides(fill=guide_legend(ncol =2,title = "Cell types",
                             override.aes = list(size=4)),
           colour = "none",
           size = guide_legend(title = "Size"))
  
  
}


wrap_plots(plot.list[[2]],plot.list[[3]],plot.list[[4]],plot.list[[5]],guide_area(),guides = "collect",nrow = 1) & 
  theme(legend.spacing.y = unit(-0.35, "line"),legend.key.size = unit(1, "line"))

dir.create("../../../pdf_files/FigS3", recursive = T, showWarnings = F)
pdf("../../../pdf_files/FigS3/figS3B_semi_sup_bm_cite.pdf", height = 4,width = 18)
wrap_plots(plot.list[[2]],plot.list[[3]],plot.list[[4]],plot.list[[5]],guide_area(),guides = "collect",nrow = 1) & 
  theme(legend.spacing.y = unit(-0.35, "line"),legend.key.size = unit(1, "line"))

dev.off()
```


## Same RNA only



```{r fig.height=4,fig.width=4}

comparisons.semi.sup <- list(
  c("0%","25%"),
  c("0%","50%"),
  c("0%","75%"),
  c("0%","100%")
)


purity.pbmc.multiome.g75.semi.sup.rna <- ggplot(bench.75.no.random.semi.sup[bench.75.no.random.semi.sup$input == "RNA",],
                                                aes(y=celltype.l2_purity,x = pct_known,fill = input)) + 
  geom_boxplot()  + theme_bw()  + 
  geom_signif(comparisons = comparisons.semi.sup,
              step_increase=0.125,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3)+
  scale_y_continuous(breaks = c(0.4,0.6,0.8,1),limits = c(0.2,1.4)) + 
  
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + theme_bw() + xlab("Annotated cells") +ylab("Purity") + NoLegend()


purity.pbmc.multiome.g75.semi.sup.rna 
```
```{r fig.width=4, fig.height=4}

size.pbmc.multiome.g75.semi.sup.rna <- ggplot(bench.75.no.random.semi.sup[bench.75.no.random.semi.sup$input == "RNA",],
                                              aes(y=size,x = pct_known,fill = input)) + 
  geom_boxplot() + theme_bw()  + 
  geom_signif(comparisons = comparisons.semi.sup,
              step_increase=0.125,
              map_signif_level=T,
              extend_line = -0.005,
              textsize = 3)+
  ylim(c(0,525))+
  
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + xlab("Annotated cells") + NoLegend()


size.pbmc.multiome.g75.semi.sup.rna
```

```{r fig.height=4,fig.width=4}

multimodal_compactness.75.semi.sup.rna <- ggplot(bench.75.no.random.semi.sup[bench.75.no.random.semi.sup$input == "RNA",],aes(y=multimodal_compactness,x = pct_known,fill = input)) + 
  geom_boxplot(outlier.shape = NA)  + theme_bw() + 
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Multimodal Compactness")  +  # Hides outliers
  coord_cartesian(ylim = c(0,0.15))   + NoLegend() + 
  geom_signif(comparisons = comparisons.semi.sup,
              y_position = 0.09,
              step_increase=0.025,
              map_signif_level=T,
              extend_line = -0.005,
              tip_length = 0.005,
              textsize = 3) + xlab("Annotated cells")
multimodal_compactness.75.semi.sup.rna

```
```{r fig.height=4,fig.width=4}
multimodal_separation.75.semi.sup.rna <- ggplot(bench.75.no.random.semi.sup[bench.75.no.random.semi.sup$input == "RNA",],aes(y=multimodal_separation,x = pct_known,fill = input)) + 
  geom_boxplot(outlier.shape = NA) +theme_bw() +
  theme(legend.position = "bottom")  + scale_fill_manual(values = input.colors.cite) + ylab("Multimodal Separation")  +  # Hides outliers
  coord_cartesian(ylim = c(0, 0.2))+ NoLegend() + 
  geom_signif(comparisons = comparisons.semi.sup,
              y_position = 0.11,
              step_increase=0.035,
              map_signif_level=T,
              extend_line = -0.005,
              tip_length = 0.01,
              textsize = 3) + xlab("Annotated cells")
multimodal_separation.75.semi.sup.rna
```


```{r fig.height=2.75,fig.width = 7}
wrap_plots(purity.pbmc.multiome.g75.semi.sup.rna,multimodal_compactness.75.semi.sup.rna,multimodal_separation.75.semi.sup.rna,nrow = 1)

pdf("../../../pdf_files/FigS3/figS3D_semi_sup_rna_metrics.pdf",height = 2.75,width = 7)
wrap_plots(purity.pbmc.multiome.g75.semi.sup.rna,multimodal_compactness.75.semi.sup.rna,multimodal_separation.75.semi.sup.rna,nrow = 1)
dev.off()
```



```{r}

DefaultAssay(bm.seacells.adt) <- "ADT"
bm.seacells.adt <- NormalizeData(bm.seacells.adt,normalization.method = "CLR",margin = 2)

acr.prot.seacells.prot <- FeatureScatter.SuperCell(bm.seacells.adt[,bm.seacells.adt$celltype.l1 %in% "T cell" ],
                                                   "adt_CD8a","adt_CD4",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("Prot. CD8A") + ylab("Prot. CD4")  + ggtitle(label = "SEACells",subtitle = "Protein") + theme_classic()  + NoLegend() 
```


```{r fig.height=4,fig.width=18}
plot.list <- list()
for (p in c(100,75,50,25,0)) {
  sobj <- readRDS(paste0("../../../output/bmCiteSeq//SuperCellRNA/testSemiSup/g75/guiding_label_",p,"_pct_hiddenseurat.mc.rds"))
  sobj <- addCellType(sobj)
  plot.list[[paste0("pct_",p)]] <- DimPlotSC(seurat = bm,
                                             seurat.mc = sobj,
                                             metacell.col = "celltype",
                                             sc.col = "celltype",
                                             mc.color = color.celltypes.bm ,
                                             sc.color = color.celltypes.bm) + theme_classic() + ggtitle(label = "SuperCell RNA",
                                                                                                        subtitle = paste0(100 - p, "% annotated cells")) + 
    scale_size(limits = c(0,max(bench.75.no.random.semi.sup$size)),breaks = c(50,100,150,200))  +
    guides(fill=guide_legend(ncol =2,title = "Cell types",
                             override.aes = list(size=4)),
           colour = "none",
           size = guide_legend(title = "Size"))
  
  
}


wrap_plots(plot.list[[2]],plot.list[[3]],plot.list[[4]],plot.list[[5]],guide_area(),guides = "collect",nrow = 1) & 
  theme(legend.spacing.y = unit(-0.35, "line"),legend.key.size = unit(1, "line"))

pdf("../../../pdf_files/FigS3/figS3C_semi_sup_bm_cite_rna_umaps.pdf", height = 4,width = 18)
wrap_plots(plot.list[[2]],plot.list[[3]],plot.list[[4]],plot.list[[5]],guide_area(),guides = "collect",nrow = 1) & 
  theme(legend.spacing.y = unit(-0.35, "line"),legend.key.size = unit(1, "line"))

dev.off()
```


```{r fig.height=3,fig.width = 3.5}

bm.supercell.rna.semi <- readRDS(paste0("../../../output/bmCiteSeq//SuperCellRNA/testSemiSup/g75/guiding_label_",25,"_pct_hiddenseurat.mc.rds"))
bm.supercell.rna.semi <- addCellType(bm.supercell.rna.semi)

DefaultAssay(bm.supercell.rna.semi) <- "ADT"
bm.supercell.rna.semi<- NormalizeData(bm.supercell.rna.semi,normalization.method = "CLR",margin = 2)

acr.prot.supercell.rna.semi.sup <- FeatureScatter.SuperCell(bm.supercell.rna.semi[,bm.supercell.rna.semi$celltype.l1 %in% "T cell" ],
                                                            "adt_CD8a","adt_CD4",group.by = "celltype", cols = color.celltypes.bm) + 
  xlab("Prot. CD8A") + ylab("Prot. CD4") + ggtitle(label = "SuperCell RNA",subtitle = "75% annotated cells")  + theme_classic()  

acr.prot.supercell.rna.semi.sup + NoLegend()

pdf("../../../pdf_files/FigS3/figS3E_semi_sup_bm_rna_acrprot.pdf",height = 3,width = 3.5)
acr.prot.supercell.rna.semi.sup + NoLegend()
dev.off()
```


```{r}

```






```{r}
semi.sup <- read.csv("../../../output/bmCiteSeq//SuperCellMulti/testSemiSup/g75/results_test_semisup.csv")
semi.sup.purity <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = celltype.l2_purity)) + geom_boxplot()
semi.sup.size <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = size)) + geom_boxplot()
compactness.pca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = compactness_pca)) + geom_boxplot()
separation.pca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = separation_pca)) + geom_boxplot()
compactness.apca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = compactness_apca)) + geom_boxplot()
separation.apca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = separation_apca)) + geom_boxplot()

patchwork::wrap_plots(semi.sup.purity , semi.sup.size,
                      compactness.pca , separation.pca,
                      compactness.apca , separation.apca)

```



# Semi sup

```{r}
semi.sup <- read.csv("../../../output/bmCiteSeq//SuperCellMulti/testSemiSup/g20/results_test_semisup.csv")
semi.sup.purity <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = celltype.l2_purity)) + geom_boxplot()
semi.sup.size <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = size)) + geom_boxplot()
compactness.pca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = compactness_pca)) + geom_boxplot()
separation.pca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = separation_pca)) + geom_boxplot()
compactness.apca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = compactness_apca)) + geom_boxplot()
separation.apca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = separation_apca)) + geom_boxplot()

patchwork::wrap_plots(semi.sup.purity , semi.sup.size,
                      compactness.pca , separation.pca,
                      compactness.apca , separation.apca)

```




<!-- # Semi sup RNA  -->

<!-- ```{r} -->
<!-- semi.sup <- read.csv("../../../output/bmCiteSeq//SuperCellMulti/testSemiSup_RNA/g75/results_test_semisup.csv") -->
<!-- semi.sup.purity <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = celltype.l2_purity)) + geom_boxplot() -->
<!-- semi.sup.size <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = size)) + geom_boxplot() -->
<!-- compactness.pca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = compactness_pca)) + geom_boxplot() -->
<!-- separation.pca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = separation_pca)) + geom_boxplot() -->
<!-- compactness.apca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = compactness_apca)) + geom_boxplot() -->
<!-- separation.apca <- ggplot(semi.sup,aes(x = as.factor(pct_known),y = separation_apca)) + geom_boxplot() -->

<!-- patchwork::wrap_plots(semi.sup.purity , semi.sup.size, -->
<!--                       compactness.pca , separation.pca, -->
<!--                       compactness.apca , separation.apca) -->

<!-- ``` -->


