## Load needed libraries
```{r}
library(Seurat)
library(Signac)
library(SuperCell)
# library(getopt)
library(ggplot2)
library(ggpubr)
library(MetacellAnalysisToolkit)
library(dplyr)
library(ComplexHeatmap)
library(tidyr)
library(gridExtra)
library(circlize)
library(scales)
library(ggseqlogo)
library(OmnipathR)
library(patchwork)
library(Pando)
library(purrr)
library("stringr")
library(decoupleR)
library(cowplot)

```
```{r}
library(Cairo)
options(bitmapType = "cairo")

# dir.create("../../../output/plots/plots_Intermodality/",recursive = T, showWarnings = F)
dir.create("../../../output/tables/",recursive = T, showWarnings = F)
```

# Set up BM Cite

```{r}



addCellType <- function(bm) {
  bm$celltype <- as.vector(bm$celltype.l2)
  bm$celltype[startsWith(bm$celltype,"Prog_B")] <- "Prog_B"
  bm$celltype[startsWith(bm$celltype,"CD8 Effector")] <- "CD8 Effector"
  bm$celltype[startsWith(bm$celltype,"CD8 Memory")] <- "CD8 Mem"
  # bm$celltype[startsWith(bm$celltype,"CD8 ")] <- "CD8"
  # bm$celltype[startsWith(bm$celltype,"CD4 ")] <- "CD4"
  bm$celltype[bm$celltype == "Naive B"] <- "B Naive"
  bm$celltype[bm$celltype == "Memory B"] <- "B Mem"
  bm$celltype[bm$celltype == "CD4 Memory"] <- "CD4 Mem"
  bm$celltype[bm$celltype == "Plasmablast"] <- "Plasma"


  #bm$celltype[endsWith(bm$celltype,"Mono")] <- "Mono"

  bm$celltype[startsWith(bm$celltype,"CD56 bright NK")] <- "NK"
  bm$celltype[startsWith(bm$celltype,"Prog_Mk")] <- "MEP"
  bm$celltype[startsWith(bm$celltype,"Prog_RBC")] <- "MEP"
  bm$celltype.l2 <- factor(bm$celltype.l2)
  bm$celltype <- factor(bm$celltype)

  return(bm)
}


colors  <- c('#E5D2DD', '#53A85F', '#F1BB72', '#F3B1A0', '#D6E7A3', '#57C3F3', '#476D87',
             '#E95C59', '#E59CC4', '#AB3282', '#BD956A', '#8C549C',
             '#9FA3A8', '#E0D4CA', '#5F3D69', '#58A4C3', "#b20000",'#E4C755', '#F7F398',
             '#AA9A59', '#E63863', '#E39A35', '#C1E6F3', '#6778AE', '#91D0BE', '#B53E2B',
             '#712820', '#DCC1DD', '#CCE0F5', '#CCC9E6', '#625D9E', '#68A180', '#3A6963',
             '#968175')

show_col(colors)

color.methods <- c( "#56B4E9",  "#D55E00" , "#CC79A7", "#F0E442")
names(color.methods) <- c("Metacells","Random-grouping","Down-sampling","Single-cells")


color.celltypes.bm  <- c("MEP" = '#D6E7A3',
                         "gdT" = '#E95C59',
                         "GMP" = '#476D87',
                         "LMPP" = '#3A6963',
                         "Prog_DC" =  '#625D9E',
                         'Prog_B' = "#AA9A59",
                         "CD14 Mono" =  "#F1BB72",
                         "CD16 Mono" = "#53A85F",
                         "CD4 Mem" = '#91D0BE',
                         "CD4 Naive" = "#F3B1A0",
                         "CD8 Effector" = "#AB3282",
                         "CD8 Mem" = "#BD956A",
                         "CD8 Naive" = "#8C549C",
                         "cDC2" = "#9FA3A8",
                         "gdT" = "#E0D4CA",
                         "MAIT" = "#E4C755",
                         "Plasma" = "#ff6db6",
                         'B Mem' = "#F7F398",
                         "B Naive" = "#E63863",
                         "NK" = "#6778AE",
                         "pDC" = "#712820",
                         "Treg" ='#57C3F3',
                         "HSC" = "#58A4C3")
```



# CITE-seq related figure


all single cell corr

```{r}
bm.cite.sc <- readRDS("../../../output/bmCiteSeq/singlecells_analysis/seuratWNN.rds")
bm.cite.sc <- addCellType(bm.cite.sc)
DefaultAssay(bm.cite.sc) <- "RNA"
bm.cite.sc<- NormalizeData(bm.cite.sc)
DefaultAssay(bm.cite.sc) <- "ADT"

bm.cite.sc <- FindVariableFeatures(bm.cite.sc)
bm.cite.sc<- NormalizeData(bm.cite.sc,normalization.method = "CLR",margin = 2)

genes.to.prot <- read.csv("../../../input/bmCiteSeq/gene_protein.csv",header = T)
genes.to.prot

feature_x <- genes.to.prot$gene.name
feature_y <- genes.to.prot$X.protein
bm.cite.sc$size <- 1
w.cor.pearson <- FeatureFeaturePlot.SuperCell(seurat.obj = bm.cite.sc,
                                                     feature.x = genes.to.prot$gene.name,
                                                     feature.y = genes.to.prot$X.protein,
                                                     assays = c("RNA","ADT"),
                                                     is.normalized = T,
                                                     plot = F)


w.cor.pearson$input <- "Single-cells"
w.cor.pearson$gamma <- 1
w.cor.pearson$origIdent <- bm.cite.sc$orig.ident[1]
w.cor.pearson
```


```{r}
corTableAll <- w.cor.pearson
for (g in c("20","50","75","100","200")){
  for (i in c('SuperCellMulti',"randomMetacells")){
    file <- paste0("../../../output/bmCiteSeq/",
                   i,"/g",
                   g,
                   "/corrTablePearson.csv")
    if (file.exists(file)) {
      corTable <- read.csv(file,row.names = 1)
      if (i == 'SuperCellMulti') {i <- "Metacells"}
      if (i == 'randomMetacells') {i <- "Random-grouping"}
      corTable$input <- i
      print(i)
      corTable$gamma <- g
      corTableAll <- rbind(corTable,corTableAll)
    }
  }

  ## subsampling


  sub.cells <- sample(colnames(bm.cite.sc),size = floor(ncol(bm.cite.sc)/as.numeric(g)),replace = F)
  bm.sub <- subset(bm.cite.sc,cells = sub.cells)
  bm.sub$size = 1
  w.cor <- FeatureFeaturePlot.SuperCell(seurat.obj = bm.sub,
                                               feature.x = feature_x,
                                               feature.y = feature_y,
                                               assays = c("RNA","ADT"),
                                               is.normalized = F,
                                               cluster = "celltype",
                                               plot = F)


  w.cor$input <- "Down-sampling"
  w.cor$gamma <- g
  w.cor$origIdent <- bm.sub$orig.ident[1]

  corTableAll <- rbind(corTableAll,w.cor)


}


corTableAll$gene <- stringr::str_split_fixed(corTableAll$feature2,pattern = "_",2)[,2]
corTableAll$gamma <- factor(corTableAll$gamma,level = c("1","20","50","75","100","200"))
corTableAll$method <- factor(corTableAll$input,level = rev(c("Metacells","Random-grouping","Down-sampling","Single-cells")))

table(corTableAll$input,corTableAll$gamma)
corTableAll.cite <- corTableAll
```
```{r}
corTableAll[corTableAll$w.cor<0 & corTableAll$method == "Metacells",]
```

When we don't have two cells expressing the feature in both modalities to compute a correlation we set pearson r to 0

```{r fig.height=3.5,fig.width=4}
corTableAll.cite$w.cor[is.na(corTableAll.cite$w.cor)] <- 0
boxplot.corr.bm.cite <- ggplot(corTableAll.cite,aes(x=gamma,y=w.cor,fill = method)) +
  theme_bw() +  geom_boxplot(position = position_dodge2(preserve = "single")) +
  ylab("Weighted pearson r") +xlab(paste0("Graining level (\u03B3)")) + scale_fill_manual(values = color.methods) + theme(legend.position = "bottom") +
  guides(fill=guide_legend(ncol =2)) + theme(legend.title = element_blank()) + ggtitle("RNA-Protein correlations")

boxplot.corr.bm.cite
```



```{r fig.height=6,fig.width=7.75}
bm.cite.mc <- readRDS("../../../output/bmCiteSeq/SuperCellMulti/g75/seurat.cite.mc.rds")
bm.cite.mc <- addCellType(bm.cite.mc)
DefaultAssay(bm.cite.mc) <- "RNA"
bm.cite.mc<- NormalizeData(bm.cite.mc)
DefaultAssay(bm.cite.mc) <- "ADT"

bm.cite.mc<- NormalizeData(bm.cite.mc,normalization.method = "CLR",margin = 2)

corr.CD8a.mc <- FeatureScatter.SuperCell(bm.cite.mc,
                                         "rna_CD8A","adt_CD8a",group.by = "celltype", cols = color.celltypes.bm) +
  guides(fill=guide_legend(ncol =2,title = "Cell types",
                           override.aes = list(size=3)),
         colour = "none",
         size = guide_legend(title = "Size")) + xlab("RNA CD8A") +ylab("Protein CD8A") +
  ggtitle("Metacell",
          subtitle = paste0("weighted pearson r = ",
                            round(corTableAll[(corTableAll$method == "Metacells" & corTableAll$gamma == 75) & corTableAll$gene == "CD8a","w.cor"],
                                  digits = 2)))
corr.CD14.mc <- FeatureScatter.SuperCell(bm.cite.mc,
                                         "rna_CD14","adt_CD14",group.by = "celltype", cols = color.celltypes.bm) +
  ggtitle("Metacell",
          subtitle = paste0("weighted pearson r = ",
                            round(corTableAll[(corTableAll$method == "Metacells" & corTableAll$gamma == 75) & corTableAll$gene == "CD14","w.cor"],
                                  digits = 2))) + xlab("RNA CD14") +ylab("Protein CD14")





bm.cite.sc$size <- 1
corr.CD8a.sc <- FeatureScatter(bm.cite.sc,
                               "rna_CD8A","adt_CD8a",group.by = "celltype", cols = color.celltypes.bm) +
  ggtitle("Single-cells",
          subtitle = paste0("pearson r = ",
                            round(corTableAll[(corTableAll$gamma == 1) & corTableAll$gene == "CD8a","w.cor"],
                                  digits = 2))) + xlab("RNA CD8A") +ylab("Protein CD8A")
corr.CD14.sc <- FeatureScatter(bm.cite.sc,
                               "rna_CD14","adt_CD14",group.by = "celltype", cols = color.celltypes.bm)   +
  ggtitle("Single-cells",
          subtitle = paste0("pearson r = ",
                            round(corTableAll[(corTableAll$gamma == 1) & corTableAll$gene == "CD14","w.cor"],
                                  digits = 2))) + xlab("RNA CD14") +ylab("Protein CD14")

dir.create("../../../pdf_files/Fig3/", recursive = T, showWarnings = F)
pdf(file = "../../../pdf_files/Fig3/fig3A.pdf",height = 6,width=7.75)
plot_grid(wrap_plots(corr.CD8a.sc + NoLegend(),corr.CD8a.mc+ NoLegend(),corr.CD14.sc + NoLegend(),corr.CD14.mc + NoLegend(),nrow = 2,axis_titles = "collect"),
          get_legend(corr.CD8a.mc),rel_widths = c(4,2))
dev.off()
```

# PBMC multiome related figures

## Global parameters
```{r}
color.celltypes.pbmc <- c("CD14 Mono" =  "#F1BB72",
                          "CD16 Mono" = "#53A85F",
                          "CD4 Mem" = '#91D0BE',
                          "CD4 Naive" = "#F3B1A0",
                          "CD8 Effector" = "#AB3282",
                          "CD8 Mem" = "#BD956A",
                          "CD8 Naive" = "#8C549C",
                          "cDC" = "#9FA3A8",
                          "gdT" = "#E0D4CA",
                          "MAIT" = "#E4C755",
                          "Plasma" = "#ff6db6",
                          'B Mem' = "#F7F398",
                          "B Interm" = "#AA9A59",
                          "B Naive" = "#E63863",
                          "NK" = "#6778AE",
                          "pDC" = "#712820",
                          "Treg" ='#57C3F3',
                          "HSPC" = "#58A4C3")

# plot theme
axis.size <- 15
mytheme <-  theme(axis.title = element_text(size = axis.size),
                  axis.text.x = element_text(size = axis.size),
                  axis.text.y = element_text(size = axis.size),
                  legend.title = element_text(size = 15),
                  legend.text = element_text(size=13))



addCellTypePBMC <- function(pbmc) {
  pbmc$celltype <- pbmc$seurat_annotations

  pbmc$celltype[grepl(pattern = "CD8 TEM",x = pbmc$celltype)] <- "CD8 Mem"

  pbmc$celltype[grepl(pattern = "CD4 TEM",x = pbmc$celltype)] <- "CD4 Mem"
  pbmc$celltype[grepl(pattern = "CD4 TCM",x = pbmc$celltype)] <- "CD4 Mem"

  pbmc$celltype[grepl(pattern = "CD8 TEM",x = pbmc$celltype)] <- "CD8 Mem"

  pbmc$celltype[grepl(pattern = "Intermediate B",x = pbmc$celltype)] <- "B Interm"
  pbmc$celltype[grepl(pattern = "Naive B",x = pbmc$celltype)] <- "B Naive"
  pbmc$celltype[grepl(pattern = "Memory B",x = pbmc$celltype)] <- "B Mem"
  pbmc$celltype <- factor(pbmc$celltype,levels = c( "B Interm",  "B Mem"   ,
                                                    "B Naive" ,  "CD14 Mono",
                                                    "CD16 Mono" ,"CD4 Mem" ,
                                                    "CD4 Naive" ,"CD8 Mem"  ,
                                                    "CD8 Naive", "cDC"   ,
                                                    "gdT"  ,     "HSPC"  ,
                                                    "MAIT",      "NK" ,
                                                    "pDC" , "Plasma",     "Treg"  ))

  Idents(pbmc) <- "celltype"
  return(pbmc)
}
```








all single cell corr

```{r}
pbmc.sc <-  readRDS("../../../output/pbmcMultiome/singlecells_analysis/seurat.multiome.activities.rds")
pbmc.sc <- addCellTypePBMC(pbmc.sc)
DefaultAssay(pbmc.sc) <- "RNA"
pbmc.sc<- NormalizeData(pbmc.sc)
pbmc.sc <- Seurat::FindVariableFeatures(pbmc.sc,nfeatures = 6000)

hvg.info <- HVFInfo(pbmc.sc)[order(HVFInfo(pbmc.sc)$variance.standardized,decreasing = T),]
hvg.info$ATAC <- F
hvg.info$ATAC[rownames(hvg.info)%in% rownames(pbmc.sc[["GA_Signac"]])] <- T
features.ga.rna.pbmc <- rownames(hvg.info[hvg.info$ATAC == T,])[1:4000]


DefaultAssay(pbmc.sc) <- "GA_Signac"
w.cor.pearson <- readRDS("../../../output/pbmcMultiome/singlecells_analysis/CorrTables.rds")

w.cor.pearson <- w.cor.pearson$SignacGA.RNA
w.cor.pearson$input <- "Single-cells"
w.cor.pearson$gamma <- 1
w.cor.pearson$gene <- str_split_fixed(w.cor.pearson$feature1,pattern = "_",n = 2)[,2]
w.cor.pearson <- w.cor.pearson[w.cor.pearson$gene %in% features.ga.rna.pbmc,]
w.cor.pearson
```


```{r}
# source("../../../fun_r/FeatureFeaturePlot.SuperCell.R")
corTableAll <- w.cor.pearson
for (g in c("10","20","50","75","100","200")){
  for (i in c('SuperCellMulti',"randomMetacells")){
    file <- paste0("../../../output/pbmcMultiome/",
                   i,"/g",
                   g,
                   "/CorrTables.rds")
    if (file.exists(file)) {
      corTable <- readRDS(file)$SignacGA.RNA
      if (i == 'SuperCellMulti') {i <- "Metacells"}
      if (i == 'randomMetacells') {i <- "Random-grouping"}
      corTable$input <- i
      print(i)
      corTable$gamma <- g
      corTable$gene <- str_split_fixed(corTable$feature1,pattern = "_",n = 2)[,2]
      corTable <- corTable[corTable$gene %in% features.ga.rna.pbmc,]

      corTableAll <- rbind(corTable,corTableAll)
    }
  }

  ## subsampling


  sub.cells <- sample(colnames(pbmc.sc),size = floor(ncol(pbmc.sc)/as.numeric(g)),replace = F)
  pbmc.sub <- subset(pbmc.sc,cells = sub.cells)
  pbmc.sub$size = 1
  w.cor <- FeatureFeaturePlot.SuperCell(seurat.obj  = pbmc.sub,
                                        feature.x  = features.ga.rna.pbmc,
                                        feature.y  = features.ga.rna.pbmc,
                                        assays = c("GA_Signac","RNA"),
                                        is.normalized = F,
                                        cluster = "celltype",
                                        plot = F)

  w.cor$gene <- str_split_fixed(w.cor$feature1,pattern = "_",n = 2)[,2]

  w.cor$input <- "Down-sampling"
  w.cor$gamma <- g

  corTableAll <- rbind(corTableAll,w.cor)


}


corTableAll$gamma <- factor(corTableAll$gamma,level = c("1","10","20","50","75","100","200"))
corTableAll$method <- factor(corTableAll$input,level = rev(c("Metacells","Random-grouping","Down-sampling","Single-cells")))

table(corTableAll$input,corTableAll$gamma)
```

```{r}
table(corTableAll[corTableAll$method == "Metacells" & corTableAll$gamma == 75,]$w.cor <0)
```   

When we don't have two cells expressing the feature in both modalities to compute a correlation we set pearson r to 0

```{r fig.height=3.5,fig.width=4}
corTableAll$w.cor[is.na(corTableAll$w.cor)] <- 0
boxplot.corr.rna.atac.pbmc <- ggplot(corTableAll,aes(x=gamma,y=w.cor,fill = method)) +
  theme_bw() +  geom_boxplot(position = position_dodge2(preserve = "single")) +
  ylab("Weighted pearson r") +xlab(paste0("Graining level (\u03B3)")) + scale_fill_manual(values = color.methods) + theme(legend.position = "bottom") +
  guides(fill=guide_legend(ncol =2)) + theme(legend.title  = element_blank()) + ggtitle("ATAC-RNA correlations")

boxplot.corr.rna.atac.pbmc
```



```{r fig.height=6,fig.width=7.75}
pbmc.mc <- readRDS("../../../output/pbmcMultiome/SuperCellMulti/g75/seurat.multiome.activities.rds")
DefaultAssay(pbmc.mc) <- "RNA"
pbmc.mc <- NormalizeData(pbmc.mc)
pbmc.mc <- addCellTypePBMC(pbmc.mc)
gc()

corr.TCF7.mc <- FeatureScatter.SuperCell(pbmc.mc,
                                         "gasignac_TCF7",
                                         "rna_TCF7",group.by = "celltype", cols = color.celltypes.pbmc) +
  guides(fill=guide_legend(ncol =2,title = "Cell types",
                           override.aes = list(size=3)),
         colour = "none",
         size = guide_legend(title = "Size")) + xlab("ATAC TCF7") +ylab("RNA TCF7")+
  ggtitle("Metacell",
          subtitle = paste0("weighted pearson r = ",
                            round(corTableAll[(corTableAll$method == "Metacells" & corTableAll$gamma == 75) & corTableAll$feature1 == "rna_TCF7","w.cor"],
                                  digits = 2)))
corr.SPI1.mc <- FeatureScatter.SuperCell(pbmc.mc,
                                         "gasignac_SPI1","rna_SPI1",group.by = "celltype", cols = color.celltypes.bm) +
  ggtitle("Metacell",
          subtitle = paste0("weighted pearson r = ",
                            round(corTableAll[(corTableAll$method == "Metacells" & corTableAll$gamma == 75) & corTableAll$feature1 == "rna_SPI1","w.cor"],
                                  digits = 2))) + xlab("ATAC SPI1") +ylab("RNA SPI1")





pbmc.sc$size <- 1
corr.TCF7.sc <- FeatureScatter(pbmc.sc,"gasignac_TCF7",
                               "rna_TCF7",group.by = "celltype", cols = color.celltypes.bm) +
  ggtitle("Single-cells",
          subtitle = paste0("pearson r = ",
                            round(corTableAll[(corTableAll$gamma == 1) & corTableAll$feature1 == "rna_TCF7","w.cor"],
                                  digits = 2))) + xlab("ATAC TCF7") +ylab("RNA TCF7")
corr.SPI1.sc <- FeatureScatter(pbmc.sc,
                               "gasignac_SPI1","rna_SPI1",group.by = "celltype", cols = color.celltypes.bm)   +
  ggtitle("Single-cells",
          subtitle = paste0("pearson r = ",
                            round(corTableAll[(corTableAll$gamma == 1) & corTableAll$feature1 == "rna_SPI1","w.cor"],
                                  digits = 2))) + xlab("ATAC SPI1") +ylab("RNA SPI1")




pdf(file = "../../../pdf_files/Fig3/fig3C.pdf",height = 6,width=7.75)
plot_grid(wrap_plots(corr.SPI1.sc + NoLegend(),corr.SPI1.mc + NoLegend(),corr.TCF7.sc + NoLegend(),corr.TCF7.mc+ NoLegend(),nrow = 2,axis_titles = "collect"),
          get_legend(corr.TCF7.mc),rel_widths = c(4,2))
dev.off()
```
```{r}
# library(gprofiler2)
# neg.cor.ga.rna <- corTableAll[(corTableAll$gamma == 75) & corTableAll$w.cor < 0 ,"gene"]
# all.genes <- rownames(pbmc.mc[["GA_Signac"]])
# all.genes <- unique(corTableAll$gene)
# gres <- gprofiler2::gost(query = list("weighted r < 0, metacells (\u03B3 = 75)"=neg.cor.ga.rna),organism = "hsapiens",significant = T,custom_bg = all.genes,user_threshold = 0.05)
# unique(gres$result$source)
# gres$result[order(gres$result$p_value),]
#
# ggplot(gres$result,aes(x = term,y = -log10(p_value))) + geom_bar(stat = "identity") + coord_flip()

saveRDS(corTableAll,"../../../output/tables/fig4_corrtables_rna_atac_pbmc.rds")
```
```{r}
atac.rna <- readRDS("../../../output/tables/fig4_corrtables_rna_atac_pbmc.rds")

```


## Motif


```{r}
top.tf.single_cells <-  readRDS("../../../output/pbmcMultiome/singlecells_analysis/multimodalMarkers_mainCellTypes_wilcoxonAUC.rds")
max(top.tf.single_cells$RNA.padj)
max(top.tf.single_cells$chromvar.padj)


w.cor.pearson <- readRDS("../../../output/pbmcMultiome//singlecells_analysis/CorrTables.rds")

w.cor.pearson <- w.cor.pearson$chromVar.RNA
w.cor.pearson$input <- "Single-cells"
w.cor.pearson$gamma <- 1

head(w.cor.pearson)
#
# w.cor.pearson <- w.cor.pearson[w.cor.pearson$feature1 %in% paste0("rna_",top.tf.single_cells$gene),] # some TFs mark multiple cell types
w.cor.pearson
```


```{r}
#source("../../../fun_r/FeatureFeaturePlot.SuperCell.R")
corTableAll <- w.cor.pearson
for (g in c("10","20","50","75","100","200")){
  for (i in c('SuperCellMulti',"randomMetacells")){
    file <- paste0("../../../output/pbmcMultiome/",
                   i,"/g",
                   g,
                   "/CorrTables.rds")
    if (file.exists(file)) {
      corTable <- readRDS(file)$chromVar.RNA
      if (i == 'SuperCellMulti') {i <- "Metacells"}
      if (i == 'randomMetacells') {i <- "Random-grouping"}
      corTable$input <- i
      print(i)
      corTable$gamma <- g
      corTableAll <- rbind(corTable,corTableAll)
    }
  }

  # subsampling


  sub.cells <- sample(colnames(pbmc.sc),size = floor(ncol(pbmc.sc)/as.numeric(g)),replace = F)
  pbmc.sub <- subset(pbmc.sc,cells = sub.cells)
  pbmc.sub$size = 1
  DefaultAssay(pbmc.sub) <- "RNA"
  pbmc.sub <- NormalizeData(pbmc.sub)
  w.cor <- FeatureFeaturePlot.SuperCell(seurat.obj  = pbmc.sub,
                                        feature.x  = stringr::str_split_fixed(w.cor.pearson$feature1,pattern = "_",2)[,2],
                                        feature.y  = stringr::str_split_fixed(w.cor.pearson$feature2,pattern = "_",2)[,2],
                                        assays = c("RNA","chromvar"),
                                        is.normalized = T,
                                        cluster = "celltype",
                                        plot = F)


  w.cor$input <- "Down-sampling"
  w.cor$gamma <- g

  corTableAll <- rbind(corTableAll,w.cor)


}


corTableAll$gamma <- factor(corTableAll$gamma,level = c("1","10","20","50","75","100","200"))
corTableAll$method <- factor(corTableAll$input,level = rev(c("Metacells","Single-cells")))
corTableAll$Gene <- str_split_fixed(corTableAll$feature1,pattern = "_",n=2)[,2]

corTableAll <- corTableAll[corTableAll$Gene %in% top.tf.single_cells$gene,] # some TFs mark multiple cell types

table(corTableAll$input,corTableAll$gamma)
```


When we don't have two cells expressing the feature in both modalities to compute a correlation we set pearson r to 0

```{r fig.height=3.5,fig.width=4}
corTableAll$w.cor[is.na(corTableAll$w.cor)] <- 0
corTableAll$method <- factor(corTableAll$input,level = rev(c("Metacells","Random-grouping","Down-sampling","Single-cells")))

boxplot.corr.rna.chromvar.pbmc <- ggplot(corTableAll,aes(x=gamma,y=w.cor,fill = method)) +
  theme_bw() +  geom_boxplot(position = position_dodge2(preserve = "single")) +
  guides(fill=guide_legend(ncol =1)) +
  ylab("Weighted pearson r") +xlab(paste0("Graining level (\u03B3)")) + scale_fill_manual(values = color.methods)+ theme(legend.position = "bottom") +
  guides(fill=guide_legend(ncol =2)) + theme(legend.title  = element_blank()) +
  theme(legend.title=element_blank()) + ggtitle("Motif-RNA correlations")

boxplot.corr.rna.chromvar.pbmc
```

```{r fig.height=10,fig.width=4}
wrap_plots(boxplot.corr.bm.cite,
           boxplot.corr.rna.atac.pbmc,
           boxplot.corr.rna.chromvar.pbmc,ncol=1)
pdf("../../../pdf_files/Fig3/fig3BDF.pdf", height=10,width=4)
wrap_plots(boxplot.corr.bm.cite,
           boxplot.corr.rna.atac.pbmc,
           boxplot.corr.rna.chromvar.pbmc,ncol=1)
dev.off()
```

## Motifs logo plots
```{r}
TFs <- c("TCF7", "TCF7L2", "LEF1","SPI1")

DefaultAssay(pbmc.sc) <- "ATAC"
detectedMotifs <- rownames(pbmc.sc@assays$chromvar) #motif
relatedTFs <- ConvertMotifID(pbmc.sc, id = detectedMotifs) #tf
detectedMotifs <- detectedMotifs[relatedTFs %in% rownames(pbmc.sc[["RNA"]])]
relatedTFs <- relatedTFs[relatedTFs %in% rownames(pbmc.sc[["RNA"]])]
names(detectedMotifs) = relatedTFs

motifs.p <- list()

for(TF in TFs){
  m <- detectedMotifs[relatedTFs[relatedTFs %in% TF]]
  motifs.p[[TF]] <- MotifPlot(pbmc.sc, motifs = m)

  data.use <- GetMotifData(object = pbmc.sc, assay = "ATAC",
                           slot = "pwm")[m]
  TF_rev = data.use
  names(TF_rev) <- TF
  rownames(TF_rev[[TF]]) <- plyr::revalue(rownames(TF_rev[[TF]]), replace = c("A" = "T", "T"= "A", "C" = "G", "G" = "C"))
  TF_rev[[TF]] <- TF_rev[[TF]][,ncol(TF_rev[[TF]]):1]
  motifs.p[[paste0(TF,"_rev")]] <- ggseqlogo::ggseqlogo(TF_rev)

}

```

```{r fig.height=6,fig.width=7.75}
detectedMotifs[relatedTFs[relatedTFs %in% TF]]


corr.SPI1.mc <- FeatureScatter.SuperCell(pbmc.mc,
                                         "rna_SPI1",detectedMotifs[relatedTFs[relatedTFs %in% "SPI1"]],
                                         group.by = "celltype", cols = color.celltypes.pbmc)+
  ggtitle("Metacell",
          subtitle = paste0("weighted pearson r = ",
                            round(corTableAll[(corTableAll$method == "Metacells" & corTableAll$gamma == 75) & corTableAll$feature1 == "rna_SPI1","w.cor"],
                                  digits = 2))) + xlab("RNA SPI1") + ylab("Motif SPI1")  +
  guides(fill=guide_legend(ncol =2,title = "Cell types",
                           override.aes = list(size=3)),
         colour = "none",
         size = guide_legend(title = "Size"))


corr.TCF7.mc <- FeatureScatter.SuperCell(pbmc.mc,
                                         "rna_TCF7",detectedMotifs[relatedTFs[relatedTFs %in% "TCF7"]],
                                         group.by = "celltype", cols = color.celltypes.pbmc)+
  ggtitle("Metacell",
          subtitle = paste0("weighted pearson r = ",
                            round(corTableAll[(corTableAll$method == "Metacells" & corTableAll$gamma == 75) & corTableAll$feature1 == "rna_TCF7","w.cor"],
                                  digits = 2))) + xlab("RNA TCF7") + ylab("Motif TCF7")

corr.TCF7L2.mc <- FeatureScatter.SuperCell(pbmc.mc,
                                           "rna_TCF7L2",detectedMotifs[relatedTFs[relatedTFs %in% "TCF7L2"]],
                                           group.by = "celltype", cols = color.celltypes.pbmc) +
  ggtitle("Metacell",
          subtitle = paste0("weighted pearson r = ",
                            round(corTableAll[(corTableAll$method == "Metacells" & corTableAll$gamma == 75) & corTableAll$feature1 == "rna_TCF7L2","w.cor"],
                                  digits = 2))) + xlab("RNA TCF7L2") + ylab("Motif TCF7L2")





pbmc.sc$size <- 1

corr.SPI1.sc <- FeatureScatter(pbmc.sc,"rna_SPI1",
                               detectedMotifs[relatedTFs[relatedTFs %in% "SPI1"]],group.by = "celltype", cols = color.celltypes.bm) +
  ggtitle("Single-cells",
          subtitle = paste0("pearson r = ",
                            round(corTableAll[(corTableAll$gamma == 1) & corTableAll$feature1 == "rna_SPI1","w.cor"],
                                  digits = 2)))+ xlab("RNA SPI1") + ylab("Motif SPI1")


corr.TCF7.sc <- FeatureScatter(pbmc.sc,"rna_TCF7",
                               detectedMotifs[relatedTFs[relatedTFs %in% "TCF7"]],group.by = "celltype", cols = color.celltypes.bm) +
  ggtitle("Single-cells",
          subtitle = paste0("pearson r = ",
                            round(corTableAll[(corTableAll$gamma == 1) & corTableAll$feature1 == "rna_TCF7","w.cor"],
                                  digits = 2)))+ xlab("RNA TCF7") + ylab("Motif TCF7")
corr.TCF7L2.sc <- FeatureScatter(pbmc.sc,
                                 "gasignac_SPI1","rna_SPI1",group.by = "celltype", cols = color.celltypes.bm)   +
  ggtitle("Single-cells",
          subtitle = paste0("pearson r = ",
                            round(corTableAll[(corTableAll$gamma == 1) & corTableAll$feature1 == "rna_TCF7L2","w.cor"],
                                  digits = 2))) + xlab("RNA TCF7L2") + ylab("Motif TCF7L2")


pdf(file = "../../../pdf_files/Fig3/fig3E_1.pdf",height = 6,width=7.75)
plot_grid(wrap_plots(
          corr.SPI1.sc + NoLegend(),corr.SPI1.mc+ NoLegend(),
          corr.TCF7.sc + NoLegend(),corr.TCF7.mc + NoLegend(),
          nrow = 2,axis_titles = "collect"),
           element_grob(element_blank()),rel_widths =  c(4,2))
dev.off()
```



```{r fig.height=6,fig.width=3}
pdf(file = "../../../pdf_files/Fig3/fig3E_2.pdf",height = 6,width=3)
wrap_plots( motifs.p$SPI1 + theme(plot.margin = unit(c(40,10,40,10),units = "pt"),
                                  axis.text = element_text(size = 7),
                                  strip.text =  element_text(size = 16)),
           motifs.p$TCF7+ theme(plot.margin = unit(c(40,10,40,10),units = "pt"),
                                  axis.text = element_text(size = 7),
                                  strip.text =  element_text(size = 16)),ncol = 1)
dev.off()
```

<!-- ```{r fig.height=4,fig.width=11} -->
<!-- plot_grid(wrap_plots( -->
<!--             corr.TCF7L2.sc + NoLegend(),corr.TCF7L2.mc + NoLegend(),nrow = 1,axis_titles = "collect"), -->
<!--            get_legend(corr.TCF7L2.mc  + guides(fill = guide_legend(override.aes = list(size=3),ncol = 2))),rel_widths =  c(4,2)) -->
<!-- ``` -->

<!-- ```{r fig.height=3,fig.width=5} -->
<!-- motifs.p$TCF7L2 + theme( strip.text =  element_text(size = 20)) -->
<!-- ``` -->


<!-- ```{r  fig.height=4,fig.width=10} -->
<!-- corr.TCF7L2.TCF7.motif.mc <- FeatureScatter.SuperCell(pbmc.mc, -->
<!--                                                       detectedMotifs[relatedTFs[relatedTFs %in% "TCF7"]],detectedMotifs[relatedTFs[relatedTFs %in% "TCF7L2"]], -->
<!--                                                       group.by = "celltype", cols = color.celltypes.pbmc) + -->
<!--   ggtitle("Metacell") + xlab("Motif TCF7") + ylab("Motif TCF7L2") -->

<!-- corr.TCF7L2.TCF7.motif.mc -->



<!-- bm.cite.sc$size <- 1 -->
<!-- corr.TCF7L2.TCF7.motif.sc <- FeatureScatter(pbmc.sc, -->
<!--                                             detectedMotifs[relatedTFs[relatedTFs %in% "TCF7"]],detectedMotifs[relatedTFs[relatedTFs %in% "TCF7L2"]], -->
<!--                                             group.by = "celltype", cols = color.celltypes.bm) + -->
<!--   ggtitle("Single-cells") + xlab("Motif TCF7") + ylab("Motif TCF7L2") -->

<!-- plot_grid(wrap_plots( -->
<!--             corr.TCF7L2.TCF7.motif.sc+ NoLegend(),corr.TCF7L2.TCF7.motif.mc + NoLegend(),nrow = 1,axis_titles = "collect"), -->
<!--            get_legend(corr.SPI1.mc),rel_widths =  c(4,2)) -->

<!-- ``` -->


<!-- ```{r fig.height=6,fig.width=5} -->

<!-- pdf("../../../output/plots/plots_Intermodality/figS5B_right.pdf",height=6,width=5) -->
<!-- wrap_plots(motifs.p$TCF7 + theme( strip.text =  element_text(size = 20)), -->
<!-- motifs.p$TCF7L2_rev + theme( strip.text =  element_text(size = 20)),ncol = 1) -->
<!-- dev.off() -->

<!-- ``` -->














<!-- ```{r} -->
<!-- # Load single-cell seurat object -->
<!-- seurat.sc = readRDS("../../../output/pbmcMultiome/singlecells_analysis/seurat.multiome.activities.rds") -->
<!-- seraut.sc <- addCellTypePBMC(seurat.sc) -->
<!-- seurat.sc$celltype_main <- seraut.sc$celltype -->

<!-- seurat.sc <- DietSeurat(seurat.sc, assays = c("RNA", "ATAC", "SCT", "GA_Signac", "chromvar")) -->
<!-- DefaultAssay(seurat.sc) <- "RNA" -->
<!-- seurat.sc <- NormalizeData(seurat.sc) -->
<!-- seurat.sc <- FindVariableFeatures(seurat.sc, nfeatures = 2000) -->
<!-- var.genes <- Seurat::VariableFeatures(seurat.sc) -->
<!-- # seurat.sc$celltype_main <- plyr::revalue(seurat.sc$celltype, c("B Interm" = "Bcells","B Mem" = "Bcells","B Naive" = "Bcells", -->
<!-- #                                                                "CD14 Mono" = "Monocytes","CD16 Mono" = "Monocytes", -->
<!-- #                                                                "CD4 Naive" = "CD4_Tcells","CD4 Mem" = "CD4_Tcells", -->
<!-- #                                                                "CD8 Naive" = "CD8_Tcells","CD8 Mem" = "CD8_Tcells")) -->
<!-- names(seurat.sc@assays)[names(seurat.sc@assays) ==  "GA_Signac"] <- "GA" -->
<!-- seurat.sc@assays$GA@key <- "ga_" -->

<!-- # Load metacell seurat object -->
<!-- gamma = 75 -->
<!-- seurat.mc <- readRDS(paste0("../../../output/pbmcMultiome/SuperCellMulti/g", gamma, "/seurat.multiome.activities.rds")) -->

<!-- seurat.mc <- addCellTypePBMC(seurat.mc) -->
<!-- seurat.mc$celltype_main <- seurat.mc$celltype -->


<!-- DefaultAssay(seurat.mc) <- 'RNA' -->
<!-- seurat.mc <- NormalizeData(seurat.mc) -->
<!-- seurat.mc <- DietSeurat(seurat.mc, assays = c("RNA", "ATAC", "SCT", "GA_Signac", "chromvar")) -->
<!-- gc() -->
<!-- # seurat.mc$celltype_main <- plyr::revalue(seurat.mc$celltype, c("B Interm" = "Bcells", "B Mem" = "Bcells", "B Naive" = "Bcells", -->
<!-- #                                                                "CD14 Mono" = "Monocytes", "CD16 Mono" = "Monocytes", -->
<!-- #                                                                "CD4 Naive" = "CD4_Tcells", "CD4 Mem" = "CD4_Tcells", -->
<!-- #                                                                "CD8 Naive" = "CD8_Tcells","CD8 Mem" = "CD8_Tcells")) -->
<!-- names(seurat.mc@assays)[names(seurat.mc@assays) ==  "GA_Signac"] <- "GA" -->
<!-- seurat.mc@assays$GA@key <- "ga_" -->
<!-- ``` -->


<!-- ```{r} -->

<!-- detectedMotifs[relatedTFs[relatedTFs %in% TF]] -->
<!-- ``` -->



<!-- ```{r} -->

<!-- group.by = "celltype" -->
<!-- for(TF in TFs){ -->
<!--   assays <- c("RNA", "GA") -->
<!--   ff.plot.res.sc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.sc, is.normalized = T, cluster = group.by, -->
<!--                                                  assays = assays, feature.x = TF, feature.y = TF, -->
<!--                                                  color.use = color.celltypes.pbmc, -->
<!--                                                  use.size = F, plot = T, pt.size = 2, add.key = T) -->
<!--   sc.p <- ff.plot.res.sc$plots[[1]]+ mytheme + guides(fill = guide_legend(override.aes = list(size=3),ncol = 3)) -->
<!--   assign(paste0(TF, ".sc.GA.RNA"), sc.p) -->

<!--   ff.plot.res.mc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.mc, -->
<!--                                                  is.normalized = T, cluster = group.by, -->
<!--                                                  assays = assays,feature.x = TF, feature.y = TF, -->
<!--                                                  color.use = color.celltypes.pbmc, -->
<!--                                                  use.size = T,plot = T) -->
<!--   mc.p <- ff.plot.res.mc$plots[[1]] + mytheme + guides(fill = guide_legend(override.aes = list(size=3),ncol = 3)) -->
<!--   assign(paste0(TF, ".mc.GA.RNA"), mc.p) -->


<!--   assays <- c("RNA", "chromvar") -->
<!--   ff.plot.res.sc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.sc, is.normalized = T, cluster = group.by, -->
<!--                                                  assays = assays, feature.x = TF, feature.y = detectedMotifs[relatedTFs[relatedTFs %in% TF]], -->
<!--                                                  color.use = color.celltypes.pbmc, -->
<!--                                                  use.size = F, plot = T, pt.size = 2, add.key = F) -->
<!--   sc.p <- ff.plot.res.sc$plots[[1]]+ mytheme + guides(fill = guide_legend(override.aes = list(size=3), ncol = 3)) -->
<!--   assign(paste0(TF, ".sc.chromVAR.RNA"), sc.p) -->

<!--   ff.plot.res.mc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.mc, -->
<!--                                                  is.normalized = T,cluster = group.by, -->
<!--                                                  assays = assays,feature.x = TF, feature.y = detectedMotifs[relatedTFs[relatedTFs %in% TF]], -->
<!--                                                  color.use = color.celltypes.pbmc, -->
<!--                                                  use.size = T,plot = T, add.key = F) -->
<!--   mc.p <- ff.plot.res.mc$plots[[1]] + mytheme + guides(fill = guide_legend(override.aes = list(size=3), ncol = 3)) -->
<!--   assign(paste0(TF, ".mc.chromVAR.RNA"), mc.p) -->

<!-- } -->

<!-- pdf("../../../output/plots/plots_Intermodality/pbmcMultiome_sc_mc_FeatureFeaturePlots_TCF7family.pdf", h=12, w=12) -->
<!-- # grid with blanks and legend -->
<!-- blank_size = 0.05 -->
<!-- blankPlot <- ggplot()+ geom_blank(aes(1,1)) + -->
<!--   cowplot::theme_nothing() -->

<!-- grid.arrange( -->
<!--   TCF7.sc.chromVAR.RNA + mytheme +NoLegend(), blankPlot, TCF7.mc.chromVAR.RNA + mytheme +NoLegend(), blankPlot, arrangeGrob(motifs.p$TCF7_rev, motifs.p$LEF1, motifs.p$TCF7L2), -->
<!--   blankPlot, blankPlot, blankPlot, blankPlot, -->
<!--   LEF1.sc.chromVAR.RNA + mytheme +NoLegend(), blankPlot, LEF1.mc.chromVAR.RNA + mytheme + NoLegend(), blankPlot, -->
<!--   blankPlot, blankPlot, blankPlot, blankPlot, blankPlot, -->
<!--   TCF7L2.sc.chromVAR.RNA + mytheme + NoLegend(), blankPlot, TCF7L2.mc.chromVAR.RNA + mytheme + NoLegend(), blankPlot, cowplot::get_legend(TCF7.mc.chromVAR.RNA), -->
<!--   ncol = 5, layout_matrix = rbind(c(1:5), c(6:9,5), c(10:13, 5), c(14:18), c(19:23)), -->
<!--   widths = c(1, blank_size, 1, blank_size, 1), heights = c(1, blank_size, 1, blank_size, 1) -->
<!-- ) -->
<!-- dev.off() -->

<!-- pdf("../../../output/plots/plots_Intermodality/pbmcMultiom_sc_mc_FeatureFeaturePlots_SPI1.pdf", w=12, h=4) -->
<!-- grid.arrange( -->
<!--   SPI1.sc.GA.RNA + mytheme + NoLegend(), blankPlot, -->
<!--   SPI1.mc.GA.RNA + mytheme + NoLegend(), blankPlot, -->
<!--   cowplot::get_legend(SPI1.sc.GA.RNA + guides(fill = guide_legend(override.aes = list(size=3), ncol = 2))), -->
<!--   ncol = 5, -->
<!--   widths = c(1, blank_size, 1, blank_size, 0.5) -->
<!-- ) -->
<!-- dev.off() -->
<!-- ``` -->

<!-- ## Correlations between GA vs RNA at the cell/metacell level -->
<!-- ```{r} -->

<!-- cor.matrices.sc <- readRDS("../../../output/pbmcMultiome//singlecells_analysis/CorrTables.rds") -->
<!-- GA.Signac.cor <- cor.matrices.sc$SignacGA.perCell -->

<!-- cell.groups <- plyr::revalue(seurat.sc$celltype, c("B Naive" = "Bcells", "B Mem" = "Bcells",  "B Interm" = "Bcells", -->
<!--                                                    "CD16 Mono" = "Mono", "CD14 Mono" = "Mono")) -->
<!-- cor.matrix.sc <- matrix(0, nrow = length(unique(cell.groups)), ncol = length(unique(cell.groups)), dimnames = list(unique(cell.groups), unique(cell.groups))) -->
<!-- for(celltype1 in unique(cell.groups)){ -->
<!--   for(celltype2 in unique(cell.groups)){ -->
<!--     cor.matrix.sc[celltype1, celltype2] <- mean(GA.Signac.cor[cell.groups %in% c(celltype1), cell.groups %in% c(celltype2)]) -->
<!--   } -->
<!-- } -->


<!-- DefaultAssay(seurat.mc) <- "RNA" -->
<!-- seurat.mc <- FindVariableFeatures(seurat.mc) -->
<!-- var.genes.mc <- Seurat::VariableFeatures(seurat.mc) -->
<!-- var.genes.mc <- var.genes.mc[var.genes.mc %in% rownames(seurat.mc[["GA"]])] -->
<!-- GA.Signac.cor <- cor(as.matrix(GetAssayData(seurat.mc, assay = "GA", slot = "data")[var.genes.mc,]), -->
<!--                      as.matrix(GetAssayData(seurat.mc, assay = "RNA", slot = "data")[var.genes.mc,])) -->

<!-- cell.groups <- plyr::revalue(seurat.mc$celltype, c("B Naive" = "Bcells", "B Mem" = "Bcells",  "B Interm" = "Bcells", -->
<!--                                                    "CD16 Mono" = "Mono", "CD14 Mono" = "Mono")) -->
<!-- cor.matrix.mc <- matrix(0, nrow = length(unique(cell.groups)), ncol = length(unique(cell.groups)), dimnames = list(unique(cell.groups), unique(cell.groups))) -->

<!-- for(celltype1 in unique(cell.groups)){ -->
<!--   for(celltype2 in unique(cell.groups)){ -->
<!--     cor.matrix.mc[celltype1, celltype2] <- mean(GA.Signac.cor[cell.groups %in% c(celltype1), cell.groups %in% c(celltype2)]) -->
<!--   } -->
<!-- } -->

<!-- col_fun <- colorRamp2(c(min(c(cor.matrix.sc, cor.matrix.mc)), -->
<!--                         mean(c(cor.matrix.sc, cor.matrix.mc)), -->
<!--                         max(c(cor.matrix.sc, cor.matrix.mc))), -->
<!--                       c("white","gold", "red")) -->

<!-- row_hclust <- hclust(dist(cor.matrix.sc)) -->
<!-- row_dend   <- rev(as.dendrogram(row_hclust)) -->
<!-- row_order  <- order.dendrogram(row_dend) -->
<!-- p1 <- Heatmap(cor.matrix.sc, show_row_names = T, show_column_names = T,row_names_side = "left", -->
<!--               show_row_dend = T, show_column_dend = F, cluster_rows =  row_dend, cluster_columns = F, -->
<!--               row_order = row_order, column_order = row_order, col=col_fun, -->
<!--               name = "Correlation", column_title = paste0("Gamma = ", 1)) -->

<!-- p2 <- Heatmap(cor.matrix.mc[rownames(cor.matrix.sc), colnames(cor.matrix.sc)], show_row_names = T, show_column_names = T,row_names_side = "left", show_heatmap_legend = T, -->
<!--               show_row_dend = T, show_column_dend = F, cluster_rows =  row_dend, cluster_columns = F, -->
<!--               row_order = row_order, column_order = row_order, col=col_fun, -->
<!--               name = "Correlation", column_title = paste0("Gamma = ", gamma)) -->
<!-- draw(p1 + p2, heatmap_legend_side="right") -->
<!-- pdf("../../../output/plots/plots_Intermodality/pbmcMultiome_plasticity_heatmap.pdf",w=6.5,h=3.5) -->
<!-- draw(p1 + p2, heatmap_legend_side="right") -->
<!-- dev.off() -->

<!-- ``` -->


## Pando analysis
### Compare pando methods
```{r}
p_thresh <- 0.05
load(paste0("../../../output/pbmcMultiome/SuperCellMulti/pando_metrics_summary_p_thresh", p_thresh, ".RData"))

n.target.genes$resolution <- factor(n.target.genes$resolution, levels = paste0("gamma.", c(1, 10, 20, 50, 75, 100, 200)))
ggplot(n.target.genes,aes(x = resolution, y = n_genes, color = method)) + geom_boxplot()

n_regions$resolution <- factor(n_regions$resolution,levels=paste0("gamma.", c(1, 10, 20, 50, 75, 100, 200)))
ggplot(n_regions,aes(x = resolution,y=n_regions, color = method)) + geom_boxplot()

n_tfs$resolution <- factor(n_tfs$resolution,levels= paste0("gamma.", c(1, 10, 20, 50, 75, 100, 200)))
ggplot(n_tfs,aes(x = resolution,y=n_tfs, color = method)) + geom_boxplot()

```

### Pando enrichment results


```{r}
seurat.sc <- pbmc.sc
net <- decoupleR::get_collectri(organism='human', split_complexes=T)
```


```{r}


GetEnrichmentPval <- function(tf,
                              modules,
                              net,
                              only.pos = F,
                              tested.genes = hvgs) {

  net <- net[net$source == tf,]
  net <- net[net$target %in% tested.genes,]
  modules <-  data.frame(modules@meta)
  modules <- modules[modules$tf == tf,]
  net$curated_regulation <- paste0(net$mor,"_",net$target)
  modules$predicted_regulation <- paste0(sign(modules$estimate),"_",modules$target)
  if(only.pos) {
    net <- net[net$mor >0,]
    modules <- modules[modules$estimate >0,]
  }

  mor = 2
  if (only.pos) {
    mor = 1
  }

  m = length(net$curated_regulation) # Number of curated regulation in test set
  n = mor*length(tested.genes) - m # Number of non-curated targets in test set
  x = length(intersect(modules$predicted_regulation,net$curated_regulation)) # Overlap between predicted and curated regulations
  k = length(unique(modules$predicted_regulation)) # Total number of predicted targets
  p.value <- phyper(x - 1, m, n, k, lower.tail = F)
  #p.value <- 1 - phyper(x - 1, m, n, k)
  return(p.value)
}




mytheme <- theme(axis.text.x = element_text(size = 11, face = "bold"),
                 axis.text.y = element_text(size = 11),
                 axis.title = element_text(size = 12, face = "bold"),
                 plot.title = element_text(size = 14, face = "bold", hjust = 0.5))

assign("modules_sc", readRDS( paste0("../../../output/pbmcMultiome/singlecells_analysis/modules_g1_met_sc_pval_", p_thresh, ".rds")))

DefaultAssay(seurat.sc) <- "RNA"
seurat.sc <- FindVariableFeatures(seurat.sc, assay='RNA', nfeatures = 4000)
hvgs <- Seurat::VariableFeatures(seurat.sc)

# method =  "LSI2_norm_svy"
# for(method in c("aggregate", "LSI1_norm_svy", "meanSC_norm_svy")){
for(method in c( "LSI1_norm_svy","LSI2_norm_svy")){


  for(gamma in c(10, 20, 50, 75, 100, 200)){
    assign(paste0("modules_g",gamma), readRDS( paste0("../../../output/pbmcMultiome/SuperCellMulti/g", gamma, "/modules_g", gamma, "_met_", method, "_pval_", p_thresh, ".rds")))
  }

  # Counts number of targets genes per TF -----------------------------------

  curated.tf <- names(which(table(net$source)>10))
  tfs <- Reduce(intersect, list(curated.tf,
                                modules_sc@meta$tf,
                                modules_g10@meta$tf,
                                modules_g20@meta$tf,
                                modules_g50@meta$tf,
                                modules_g75@meta$tf,
                                modules_g100@meta$tf,
                                modules_g200@meta$tf))

  predicted.target.sc <- sapply(tfs, function(x) { nrow(modules_sc@meta[modules_sc@meta$tf == x,])})
  predicted.target.g10 <- sapply(tfs, function(x) { nrow(modules_g10@meta[modules_g10@meta$tf == x,])})
  predicted.target.g20 <- sapply(tfs, function(x) { nrow(modules_g20@meta[modules_g20@meta$tf == x,])})
  predicted.target.g50 <- sapply(tfs, function(x) { nrow(modules_g50@meta[modules_g50@meta$tf == x,])})
  predicted.target.g75 <- sapply(tfs, function(x) { nrow(modules_g75@meta[modules_g75@meta$tf == x,])})
  predicted.target.g100 <- sapply(tfs, function(x) { nrow(modules_g100@meta[modules_g100@meta$tf == x,])})
  predicted.target.g200 <- sapply(tfs, function(x) { nrow(modules_g200@meta[modules_g200@meta$tf == x,])})

  nb_genes <- as.data.frame(cbind(predicted.target.sc, predicted.target.g10, predicted.target.g20,
                                  predicted.target.g50, predicted.target.g75,
                                  predicted.target.g100, predicted.target.g200))

  df_long <- nb_genes %>%
    pivot_longer(cols = starts_with("predicted.target"),
                 names_to = "Group",
                 values_to = "Num_Genes")
  df_long$Group <- factor(gsub("predicted.target.", "", df_long$Group), levels = c("sc", paste0("g",c(10,20,50,75,100,200))))


  Means <- df_long %>% group_by(Group) %>%
    summarize(Avg = mean(Num_Genes))

  nb_genes_plot <- ggplot(df_long, aes(x = Group, y = Num_Genes)) +
    geom_boxplot(fill = "lightblue", color = "black", outlier.color = "black") +
    geom_point(mapping = aes(x = Group, y = Avg), data = Means, color = "red", shape = 2) +
    geom_line(data = Means, mapping = aes(x = Group, y = Avg), group = 1, color = "red") +
    theme_bw() +
    labs(title = method,
         x = "",
         y = "Nb. predicted targets") +
    mytheme
  # print(nb_genes_plot)

  # Enrichment results all directions -----------------------------------------------------

  pval.sc <- sapply(tfs,function(x){ GetEnrichmentPval(tf = x,modules = modules_sc,net = net,tested.genes = hvgs)}, USE.NAMES = T)
  pval.g10 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g10,net = net,tested.genes = hvgs)}, USE.NAMES = T)
  pval.g20 <- sapply(tfs,function(x){ GetEnrichmentPval(tf = x,modules = modules_g20,net = net,tested.genes = hvgs)}, USE.NAMES = T)
  pval.g50 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g50,net = net,tested.genes = hvgs)}, USE.NAMES = T)
  pval.g75 <- sapply(tfs,function(x){ GetEnrichmentPval(tf = x,modules = modules_g75,net = net,tested.genes = hvgs)}, USE.NAMES = T)
  pval.g100 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g100,net = net,tested.genes = hvgs)}, USE.NAMES = T)
  pval.g200 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g200,net = net,tested.genes = hvgs)}, USE.NAMES = T)

  res <- data.frame("sc" = pval.sc,
                    "g10" = pval.g10,
                    "g20" = pval.g20,
                    "g50" = pval.g50,
                    "g75" = pval.g75,
                    "g100" = pval.g100,
                    "g200" = pval.g200)


  res_long <- res %>%
    pivot_longer(
      cols = colnames(res),  # Specify the columns to pivot
      names_to = "group",  # Name of the new column for groups
      values_to = "value"  # Name of the new column for values
    )

  res_long$resolution <- factor(res_long$group, levels= c("sc","g10","g20","g50","g75","g100","g200"))

  stats <- res_long %>% group_by(resolution) %>%
    summarize(stat = median(value))

  pval_boxplot <- ggplot(res_long, aes(x = resolution, y=(value))) +
    geom_boxplot(fill = "lightblue", color = "black", outlier.color = "black" ) +
    geom_jitter(width = 0.1) +
    geom_point(mapping = aes(x = resolution, y = stat), data = stats, color = "red", shape = 2) +
    geom_line(data = stats, mapping = aes(x = resolution, y = stat), group = 1, color = "red") +
    theme_bw() +
    labs(title = paste0(method," (common TFs)"),
         x = "",
         y = "P-value") +
    mytheme


  # Enrichment using only positive regulation -------------------------------

  curated.tf <- names(which(table(net[net$mor>0,]$source)>10))

  tfs <- Reduce(intersect, list(
    curated.tf,
    modules_sc@meta$tf,
    modules_g10@meta$tf,
    modules_g20@meta$tf,
    modules_g50@meta$tf,
    modules_g75@meta$tf,
    modules_g100@meta$tf,
    modules_g200@meta$tf
  ))

  pval.sc <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_sc,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T)
  pval.g10 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g10,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T)
  pval.g20 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g20,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T)
  pval.g50 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g50,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T)
  pval.g75 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g75,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T)
  pval.g100 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g100,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T)
  pval.g200 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g200,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T)

  res <- data.frame("sc" = pval.sc,
                    "g10" = pval.g10,
                    "g20"= pval.g20,
                    "g50" = pval.g50,
                    "g75" = pval.g75,
                    "g100" = pval.g100,
                    "g200" = pval.g200)


  res_long <- res %>%
    pivot_longer(
      cols = colnames(res),  # Specify the columns to pivot
      names_to = "group",  # Name of the new column for groups
      values_to = "value"  # Name of the new column for values
    )

  res_long$resolution <- factor(res_long$group,levels= c("sc","g10","g20","g50","g75","g100","g200"))
  stats <- res_long %>% group_by(resolution) %>%
    summarize(stat = median(value))

  pval_boxplot_onlyPos <- ggplot(res_long, aes(x = resolution, y=(value))) +
    geom_boxplot(fill = "lightblue", color = "black", outlier.color = "black" ) +
    geom_jitter(width = 0.1) +
    geom_point(mapping = aes(x = resolution, y = stat), data = stats, color = "red", shape = 2) +
    geom_line(data = stats, mapping = aes(x = resolution, y = stat), group = 1, color = "red") +
    theme_bw() +
    labs(title = paste0(method," (only pos., common TFs)"),
         x = "",
         y = "P-value") +
    mytheme

  combined.plot <- nb_genes_plot | pval_boxplot  | pval_boxplot_onlyPos
  # combined.plot <- nb_genes_plot | pval_boxplot  
  print(combined.plot)
  assign(paste0("p.",method), combined.plot)


  comparisons <- list(

  # c("1","50"),
  c("1", "75"))

library(ggsignif)

df_long$graining_level <- str_split_fixed(df_long$Group,"g",n=2)[,2]
df_long$graining_level[df_long$graining_level == ""] <- "1"
df_long$graining_level <- factor(df_long$graining_level,as.character(c(1,10,20,50,75,100,200)))

nb_genes_plot <- ggplot(df_long, aes(x = graining_level, y = Num_Genes)) +
  geom_boxplot(fill = "lightblue", color = "black", outlier.color = "black") +
  # geom_point(mapping = aes(x = Group, y = Avg), data = Means, color = "red", shape = 2) +
  # geom_line(data = Means, mapping = aes(x = Group, y = Avg), group = 1, color = "red") +
  theme_bw() +
  labs(title = method,
       x = "Graining level (\u03B3)",
       y = "Predicted targets") + ggtitle("Pando regulon size")

stats <- res_long %>% group_by(resolution) %>%
  summarize(stat = median(-log10(value)))

res_long$graining_level <- str_split_fixed(res_long$resolution,"g",n=2)[,2]
res_long$graining_level[res_long$graining_level == ""] <- "1"
res_long$graining_level <- factor(res_long$graining_level,as.character(c(1,10,20,50,75,100,200)))

pval_boxplot <- ggplot(res_long, aes(x = graining_level, y=-log10(value))) +
  geom_boxplot(fill = "lightblue", color = "black", outliers = F ) +
  geom_signif(comparisons = comparisons,y_position = 2.5,
              step_increase=0.05,tip_length = 0.005,
              map_signif_level=F,extend_line = -0.005,
              textsize = 5)+ coord_cartesian(ylim = c(0,3.25))+
  # geom_jitter(width = 0.1) +
  # geom_point(mapping = aes(x = resolution, y = stat), data = stats, color = "red", shape = 2) +
  # geom_line(data = stats, mapping = aes(x = resolution, y = stat), group = 1, color = "red") +
  theme_bw() +
  labs(title = paste0(method," (common TFs)"),
       x = "",
       y = "- log10(P-value)") +
  labs(
    x = "Graining level (\u03B3)",
    y = "Predicted targets")+
  ggtitle("Enrichment in curated targets")

wrap_plots(nb_genes_plot,pval_boxplot)

}
# p.LSI1_norm_svy

```



```{r}

p.LSI2_norm_svy
```
# PLot for LSI method 1 svy
```{r fig.height=4,fig.width=7.25}
comparisons <- list(

  # c("1","50"),
  c("1", "75"))

library(ggsignif)

df_long$graining_level <- str_split_fixed(df_long$Group,"g",n=2)[,2]
df_long$graining_level[df_long$graining_level == ""] <- "1"
df_long$graining_level <- factor(df_long$graining_level,as.character(c(1,10,20,50,75,100,200)))

nb_genes_plot <- ggplot(df_long, aes(x = graining_level, y = Num_Genes)) +
  geom_boxplot(fill = "lightblue", color = "black", outlier.color = "black") +
  # geom_point(mapping = aes(x = Group, y = Avg), data = Means, color = "red", shape = 2) +
  # geom_line(data = Means, mapping = aes(x = Group, y = Avg), group = 1, color = "red") +
  theme_bw() +
  labs(title = method,
       x = "Graining level (\u03B3)",
       y = "Nb. predicted targets") + ggtitle("Pando regulon size")

stats <- res_long %>% group_by(resolution) %>%
  summarize(stat = median(-log10(value)))

res_long$graining_level <- str_split_fixed(res_long$resolution,"g",n=2)[,2]
res_long$graining_level[res_long$graining_level == ""] <- "1"
res_long$graining_level <- factor(res_long$graining_level,as.character(c(1,10,20,50,75,100,200)))

pval_boxplot <- ggplot(res_long, aes(x = graining_level, y=-log10(value))) +
  geom_boxplot(fill = "lightblue", color = "black", outliers = F ) +
  geom_signif(comparisons = comparisons,y_position = 2.5,
              step_increase=0.05,tip_length = 0.005,
              map_signif_level=F,extend_line = -0.005,
              textsize = 5)+ coord_cartesian(ylim = c(0,3.25))+
  # geom_jitter(width = 0.1) +
  # geom_point(mapping = aes(x = resolution, y = stat), data = stats, color = "red", shape = 2) +
  # geom_line(data = stats, mapping = aes(x = resolution, y = stat), group = 1, color = "red") +
  theme_bw() +
  labs(title = paste0(method," (common TFs)"),
       x = "",
       y = "- log10(P-value)") +
  labs(
    x = "Graining level (\u03B3)",
    y = "- log10(P value)")+
  ggtitle("Enrichment in curated targets")

pdf(paste0("../../../pdf_files/Fig3/Fig3pando_figures_pval_",p_thresh,".pdf"), w=6,h=3)

wrap_plots(nb_genes_plot,pval_boxplot,axis_titles = "collect") & theme(axis.title  = element_text(size = 18),
                                               title =  element_text(size = 14) )
dev.off()
```





```{r fig.height=3,fig.width=6}

comparisons <- list(

  # c("1","50"),
  c("1", "75"))

library(ggsignif)

df_long$graining_level <- str_split_fixed(df_long$Group,"g",n=2)[,2]
df_long$graining_level[df_long$graining_level == ""] <- "1"
df_long$graining_level <- factor(df_long$graining_level,as.character(c(1,10,20,50,75,100,200)))

nb_genes_plot <- ggplot(df_long, aes(x = graining_level, y = Num_Genes)) +
  geom_boxplot(fill = "lightblue", color = "black", outlier.color = "black") +
  # geom_point(mapping = aes(x = Group, y = Avg), data = Means, color = "red", shape = 2) +
  # geom_line(data = Means, mapping = aes(x = Group, y = Avg), group = 1, color = "red") +
  theme_bw() +
  labs(title = method,
       x = "Graining level (\u03B3)",
       y = "Predicted targets") + ggtitle("Pando regulon size")

stats <- res_long %>% group_by(resolution) %>%
  summarize(stat = median(-log10(value)))

res_long$graining_level <- str_split_fixed(res_long$resolution,"g",n=2)[,2]
res_long$graining_level[res_long$graining_level == ""] <- "1"
res_long$graining_level <- factor(res_long$graining_level,as.character(c(1,10,20,50,75,100,200)))

pval_boxplot <- ggplot(res_long, aes(x = graining_level, y=-log10(value))) +
  geom_boxplot(fill = "lightblue", color = "black", outliers = F ) +
  geom_signif(comparisons = comparisons,y_position = 2.5,
              step_increase=0.05,tip_length = 0.005,
              map_signif_level=F,extend_line = -0.005,
              textsize = 5)+ coord_cartesian(ylim = c(0,3.25))+
  # geom_jitter(width = 0.1) +
  # geom_point(mapping = aes(x = resolution, y = stat), data = stats, color = "red", shape = 2) +
  # geom_line(data = stats, mapping = aes(x = resolution, y = stat), group = 1, color = "red") +
  theme_bw() +
  labs(title = paste0(method," (common TFs)"),
       x = "",
       y = "- log10(P-value)") +
  labs(
    x = "Graining level (\u03B3)",
    y = "Predicted targets")+
  ggtitle("Enrichment in curated targets")

wrap_plots(nb_genes_plot,pval_boxplot)
```


<!-- # Hspc multiome related figures -->

<!-- ## Global parameters -->
<!-- ```{r} -->
<!-- celltype_colors <- c("HMP" = "#999999", "Mono" = "#004949", "HSC" = "#009292", -->
<!--                      "Ery" = "#FF6DB6", "MEP" = "#490092", "cDC" = "#006DDB", -->
<!--                      "CLP" = "#B66DFF", "pDC" = "#6DB6FF") -->


<!-- # plot theme -->
<!-- axis.size <- 15 -->
<!-- mytheme <-  theme(axis.title = element_text(size = axis.size), -->
<!--                   axis.text.x = element_text(size = axis.size), -->
<!--                   axis.text.y = element_text(size = axis.size), -->
<!--                   legend.title = element_text(size = 15), -->
<!--                   legend.text = element_text(size=13)) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- # Load single-cell seurat object -->
<!-- seurat.sc = readRDS("../../../output/hspcMultiomePersad/singlecells_analysis/seurat.multiome.activities.rds") -->
<!-- seurat.sc <- DietSeurat(seurat.sc, assays = c("RNA", "ATAC", "SCT", "GA_Signac", "chromvar"), dimreducs = "wnn.umap") -->
<!-- DefaultAssay(seurat.sc) <- "RNA" -->
<!-- seurat.sc <- NormalizeData(seurat.sc) -->
<!-- seurat.sc <- FindVariableFeatures(seurat.sc, nfeatures = 2000) -->
<!-- var.genes <- Seurat::VariableFeatures(seurat.sc) -->
<!-- names(seurat.sc@assays)[names(seurat.sc@assays) ==  "GA_Signac"] <- "GA" -->
<!-- seurat.sc@assays$GA@key <- "ga_" -->

<!-- # Load metacell seurat object -->
<!-- gamma = 75 -->
<!-- seurat.mc <- readRDS(paste0("../../../output/hspcMultiomePersad/SuperCellMulti/g", gamma, "/seurat.multiome.activities.rds")) -->
<!-- DefaultAssay(seurat.mc) <- 'RNA' -->
<!-- seurat.mc <- NormalizeData(seurat.mc) -->
<!-- seurat.mc <- DietSeurat(seurat.mc, assays = c("RNA", "ATAC", "SCT", "GA_Signac", "chromvar")) -->
<!-- gc() -->

<!-- names(seurat.mc@assays)[names(seurat.mc@assays) ==  "GA_Signac"] <- "GA" -->
<!-- seurat.mc@assays$GA@key <- "ga_" -->
<!-- ``` -->

<!-- ## Motifs logo plots -->
<!-- ```{r} -->
<!-- TFs <- c("GATA1") -->
<!-- DefaultAssay(seurat.sc) <- "ATAC" -->
<!-- detectedMotifs <- rownames(seurat.sc@assays$chromvar) #motif -->
<!-- relatedTFs <- ConvertMotifID(seurat.sc, id = detectedMotifs) #tf -->
<!-- detectedMotifs <- detectedMotifs[relatedTFs %in% rownames(seurat.sc[["RNA"]])] -->
<!-- relatedTFs <- relatedTFs[relatedTFs %in% rownames(seurat.sc[["RNA"]])] -->
<!-- names(detectedMotifs) = relatedTFs -->

<!-- motifs.p <- list() -->

<!-- for(TF in TFs){ -->
<!--   m <- detectedMotifs[relatedTFs[relatedTFs %in% TF]] -->
<!--   motifs.p[[TF]] <- MotifPlot(seurat.sc, motifs = m) -->

<!--   data.use <- GetMotifData(object = seurat.sc, assay = "ATAC", -->
<!--                            slot = "pwm")[m] -->
<!--   TF_rev = data.use -->
<!--   names(TF_rev) <- TF -->
<!--   rownames(TF_rev[[TF]]) <- plyr::revalue(rownames(TF_rev[[TF]]), replace = c("A" = "T", "T"= "A", "C" = "G", "G" = "C")) -->
<!--   TF_rev[[TF]] <- TF_rev[[TF]][,ncol(TF_rev[[TF]]):1] -->
<!--   motifs.p[[paste0(TF,"_rev")]] <- ggseqlogo::ggseqlogo(TF_rev) -->

<!-- } -->

<!-- ``` -->

<!-- ```{r} -->

<!-- group.by = "celltype" -->
<!-- for(TF in TFs){ -->
<!--   assays <- c("RNA", "GA") -->
<!--   ff.plot.res.sc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.sc, is.normalized = T, cluster = group.by, -->
<!--                                                  assays = assays, feature.x = TF, feature.y = TF, -->
<!--                                                  color.use = celltype_colors, -->
<!--                                                  use.size = F, plot = T, pt.size = 2, add.key = T) -->
<!--   sc.p <- ff.plot.res.sc$plots[[1]]+ mytheme + guides(fill = guide_legend(override.aes = list(size=3),ncol = 3)) -->
<!--   assign(paste0(TF, ".sc.GA.RNA"), sc.p) -->

<!--   ff.plot.res.mc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.mc, -->
<!--                                                  is.normalized = T, cluster = group.by, -->
<!--                                                  assays = assays,feature.x = TF, feature.y = TF, -->
<!--                                                  color.use = celltype_colors, -->
<!--                                                  use.size = T,plot = T) -->
<!--   mc.p <- ff.plot.res.mc$plots[[1]] + mytheme + guides(fill = guide_legend(override.aes = list(size=3),ncol = 3)) -->
<!--   assign(paste0(TF, ".mc.GA.RNA"), mc.p) -->


<!--   assays <- c("RNA", "chromvar") -->
<!--   ff.plot.res.sc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.sc, is.normalized = T, cluster = group.by, -->
<!--                                                  assays = assays, feature.x = TF, feature.y = detectedMotifs[relatedTFs[relatedTFs %in% TF]], -->
<!--                                                  color.use = celltype_colors, -->
<!--                                                  use.size = F, plot = T, pt.size = 2, add.key = F) -->
<!--   sc.p <- ff.plot.res.sc$plots[[1]]+ mytheme + guides(fill = guide_legend(override.aes = list(size=3), ncol = 3)) -->
<!--   assign(paste0(TF, ".sc.chromVAR.RNA"), sc.p) -->

<!--   ff.plot.res.mc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.mc, -->
<!--                                                  is.normalized = T,cluster = group.by, -->
<!--                                                  assays = assays,feature.x = TF, feature.y = detectedMotifs[relatedTFs[relatedTFs %in% TF]], -->
<!--                                                  color.use = celltype_colors, -->
<!--                                                  use.size = T,plot = T, add.key = F) -->
<!--   mc.p <- ff.plot.res.mc$plots[[1]] + mytheme + guides(fill = guide_legend(override.aes = list(size=3), ncol = 3)) -->
<!--   assign(paste0(TF, ".mc.chromVAR.RNA"), mc.p) -->

<!-- } -->

<!-- # grid with blanks and legend -->
<!-- blank_size = 0.05 -->
<!-- blankPlot <- ggplot()+ geom_blank(aes(1,1)) + -->
<!--   cowplot::theme_nothing() -->

<!-- grid.arrange( -->
<!--   GATA1.sc.GA.RNA + mytheme + NoLegend(), blankPlot, -->
<!--   GATA1.mc.GA.RNA + mytheme + NoLegend(), blankPlot, -->
<!--   cowplot::get_legend(GATA1.sc.GA.RNA + guides(fill = guide_legend(override.aes = list(size=3), ncol = 2))), -->
<!--   ncol = 5, -->
<!--   widths = c(1, blank_size, 1, blank_size, 0.5) -->
<!-- ) -->

<!-- # save plot in pdf -->
<!-- pdf("../../../output/plots/plots_Intermodality/hspcMultiomePersad_sc_mc_FeatureFeaturePlots_GATA1.pdf", w=10, h=4) -->
<!-- grid.arrange( -->
<!--   GATA1.sc.GA.RNA + mytheme + NoLegend(), blankPlot, -->
<!--   GATA1.mc.GA.RNA + mytheme + NoLegend(), blankPlot, -->
<!--   cowplot::get_legend(GATA1.sc.GA.RNA + guides(fill = guide_legend(override.aes = list(size=3), ncol = 2))), -->
<!--   ncol = 5, -->
<!--   widths = c(1, blank_size, 1, blank_size, 0.5) -->
<!-- ) -->
<!-- dev.off() -->
<!-- ``` -->
<!-- ## UMAP plot -->
<!-- ```{r} -->
<!-- png("../../../output/plots/plots_Intermodality/hspcMultiomePersad_UMAPprojetcion.png",width = 5*300, height = 4*300, res= 300) -->
<!-- projection <- mc_projection( -->
<!--   sc.obj = seurat.sc, -->
<!--   mc.obj = seurat.mc, -->
<!--   cell.membership = data.frame(row.names = names(seurat.mc@misc$membership), membership = paste0("Metacell_",seurat.mc@misc$membership)), -->
<!--   sc.reduction = "wnn.umap", mc.color = celltype_colors, sc.color = celltype_colors, -->
<!--   sc.label = "celltype", -->
<!--   metacell.label = "celltype" -->
<!-- ) -->
<!-- projection + ggtitle(paste0("UMAP projection (hspcMultiomePersad)")) + mytheme + -->
<!--   guides(colour = guide_legend(override.aes = list(size=4))) -->
<!-- dev.off() -->

<!-- ``` -->

<!-- ## Correlations between GA vs RNA at the cell/metacell level -->
<!-- ```{r} -->
<!-- cor.matrices.sc <- readRDS("../../../output/hspcMultiomePersad/singlecells_analysis/CorrTables.rds") -->
<!-- GA.Signac.cor <- cor.matrices.sc$SignacGA.perCell -->

<!-- cell.groups <- seurat.sc$celltype -->

<!-- cor.matrix.sc <- matrix(0, nrow = length(unique(cell.groups)), ncol = length(unique(cell.groups)), dimnames = list(unique(cell.groups), unique(cell.groups))) -->
<!-- for(celltype1 in unique(cell.groups)){ -->
<!--   for(celltype2 in unique(cell.groups)){ -->
<!--     cor.matrix.sc[celltype1, celltype2] <- mean(GA.Signac.cor[cell.groups %in% c(celltype1), cell.groups %in% c(celltype2)]) -->
<!--   } -->
<!-- } -->


<!-- DefaultAssay(seurat.mc) <- "RNA" -->
<!-- seurat.mc <- FindVariableFeatures(seurat.mc) -->
<!-- var.genes.mc <- Seurat::VariableFeatures(seurat.mc) -->
<!-- var.genes.mc <- var.genes.mc[var.genes.mc %in% rownames(seurat.mc[["GA"]])] -->
<!-- GA.Signac.cor <- cor(as.matrix(GetAssayData(seurat.mc, assay = "GA", slot = "data")[var.genes.mc,]), -->
<!--                      as.matrix(GetAssayData(seurat.mc, assay = "RNA", slot = "data")[var.genes.mc,])) -->

<!-- cor.matrix.mc <- matrix(0, nrow = length(unique(cell.groups)), ncol = length(unique(cell.groups)), dimnames = list(unique(cell.groups), unique(cell.groups))) -->

<!-- cell.groups <- seurat.mc$celltype -->
<!-- for(celltype1 in unique(cell.groups)){ -->
<!--   for(celltype2 in unique(cell.groups)){ -->
<!--     cor.matrix.mc[celltype1, celltype2] <- mean(GA.Signac.cor[cell.groups %in% c(celltype1), cell.groups %in% c(celltype2)]) -->
<!--   } -->
<!-- } -->

<!-- # col_fun <- colorRamp2(c(min(c(cor.matrix.sc, cor.matrix.mc)), -->
<!-- #                         mean(c(cor.matrix.sc, cor.matrix.mc)), -->
<!-- #                         max(c(cor.matrix.sc, cor.matrix.mc))), -->
<!-- #                       c("blue", "white", "red")) -->
<!-- col_fun <- colorRamp2(c(min(c(cor.matrix.sc, cor.matrix.mc)), -->
<!--                         mean(c(cor.matrix.sc, cor.matrix.mc)), -->
<!--                         max(c(cor.matrix.sc, cor.matrix.mc))), -->
<!--                       c("white","gold", "red")) -->

<!-- row_hclust <- hclust(dist(cor.matrix.sc)) -->
<!-- row_dend   <- rev(as.dendrogram(row_hclust)) -->
<!-- row_order  <- order.dendrogram(row_dend) -->
<!-- p1 <- Heatmap(cor.matrix.sc, show_row_names = T, show_column_names = T,row_names_side = "left", -->
<!--               show_row_dend = T, show_column_dend = F, cluster_rows =  row_dend, cluster_columns = F, -->
<!--               row_order = row_order, column_order = row_order, col=col_fun, -->
<!--               name = "Correlation", column_title = paste0("Gamma = ", 1)) -->

<!-- # row_hclust <- hclust(dist(cor.matrix.mc)) -->
<!-- # row_dend   <- rev(as.dendrogram(row_hclust)) -->
<!-- # row_order  <- order.dendrogram(row_dend) -->
<!-- p2 <- Heatmap(cor.matrix.mc[rownames(cor.matrix.sc), colnames(cor.matrix.sc)], show_row_names = T, show_column_names = T,row_names_side = "left", show_heatmap_legend = T, -->
<!--               show_row_dend = T, show_column_dend = F, cluster_rows =  row_dend, cluster_columns = F, -->
<!--               row_order = row_order, column_order = row_order, col=col_fun, -->
<!--               name = "Correlation", column_title = paste0("Gamma = ", gamma)) -->
<!-- pdf("../../../output/plots/plots_Intermodality/hspcMultiomePersad_plasticity_heatmap.pdf",w=6.5,h=3.5) -->
<!-- draw(p1 + p2, heatmap_legend_side="right") -->
<!-- dev.off() -->
<!-- ``` -->



<!-- # Correlations between GA vs RNA at the gene level for each HVGs -->
<!-- ```{r} -->

<!-- cor.summary <- data.frame(gamma = vector(), gene = vector(), dataset= vector(), cor.Signac = vector()) -->
<!-- for(dat in c("hspcMultiomePersad","pbmcMultiome")){ -->
<!--   cor.matrices.sc <- readRDS(paste0("../../../output/", dat, "/singlecells_analysis/CorrTables.rds")) -->

<!--   for(gamma in c(1, 10, 20, 50, 75, 100)){ -->
<!--     if(gamma == 1){ -->
<!--       GA.Signac.cor <- cor.matrices.sc$SignacGA.RNA -->
<!--     }else{ -->
<!--       GA.Signac.cor <- readRDS(paste0("../../../output/", dat, "/SuperCellMulti/g", gamma, "/CorrTables.rds"))$SignacGA.RNA -->
<!--     } -->
<!--     genes <- sapply(rownames(GA.Signac.cor), function(i) unlist(strsplit(i, "_"))[2]) -->
<!--     cor.summary <- rbind(cor.summary, data.frame(gamma = rep(gamma, length(genes)), -->
<!--                                                  gene = genes, -->
<!--                                                  dataset = dat, -->
<!--                                                  cor.Signac = GA.Signac.cor[, "w.cor"])) -->
<!--   } -->
<!-- } -->

<!-- df_long <- as.data.frame(pivot_longer(cor.summary, cols = starts_with("cor"), -->
<!--                                       names_to = "method", values_to = "correlation")) -->
<!-- df_long$dataset <- factor(df_long$dataset) -->
<!-- df_long$gamma <- paste0("g", df_long$gamma) -->
<!-- df_long$gamma <- factor(df_long$gamma, levels = paste0("g", c(1,10,20,50,75,100,200))) -->

<!-- CorGARNA.boxplots <- ggplot(df_long, aes(x = factor(gamma), y = correlation, fill = dataset)) + -->
<!--   geom_boxplot(position = position_dodge(width = 0.8)) + -->
<!--   labs(x = "Gamma", y = "Correlation", title = "Correlation between HVGs expression and gene activity") + -->
<!--   theme_bw() + mytheme + theme(legend.title = element_blank()) -->
<!-- print(CorGARNA.boxplots) -->

<!-- # save figure in pdf -->
<!-- pdf("../../../output/plots/plots_Intermodality/CorGARNA_boxplots.pdf", w=10, h=3) -->
<!-- print(CorGARNA.boxplots) -->
<!-- dev.off() -->

<!-- ``` -->
