## Load needed libraries
```{r}
library(Seurat)
library(Signac)
library(SuperCell)
# library(getopt)
library(ggplot2)
library(ggpubr)
library(MetacellAnalysisToolkit)
library(dplyr)
library(ComplexHeatmap)
library(tidyr)
library(gridExtra)
library(circlize)
library(scales)
library(ggseqlogo)
library(OmnipathR)
library(patchwork)
library(Pando)
library(purrr)
library("stringr")
library(decoupleR)
library(cowplot)
set.seed(2026)

opt <- list()
opt$resdir <- "../../../output/"
opt$outdir <- "figure_3"
dir.create(opt$outdir)
```
```{r}
library(Cairo)
options(bitmapType = "cairo")
```

# Set up PBMC Cite

```{r}
pbmc.cite.sc <- readRDS("../../../output/pbmcCiteSeqAtlas/P1_0/singlecells_analysis/seuratWNN.rds")


addCellType <- function(pbmc) {
  pbmc$celltype <- as.vector(pbmc$celltype.l1.5)

  return(pbmc)
}

color.celltypes.pbmc <- c("#FFD92F", "#999999", "#E69F00", "#33A02C", "#F781BF", "#E78AC3", "#56B4E9", "#FB9A99", "#CCEBC5", "#AD7FA8", "#CAB2D6", "#B15928", "#6A3D9A")
names(color.celltypes.pbmc) <- c( "B" ,    "CD4 T"   ,  "CD8 T"  ,     "dnT"  ,     "gdT"  ,    "MAIT"  ,      "NK" ,      "ILC",      "Mono" ,       "DC" ,    "Eryth",  "Platelet" ,     "HSPC" )



color.methods <- c( "#56B4E9",  "#D55E00" , "#CC79A7", "#F0E442")
names(color.methods) <- c("Metacells","Random-grouping","Down-sampling","Single-cells")


```



# CITE-seq related figure


all single cell corr

```{r}
pbmc.cite.sc <- addCellType(pbmc.cite.sc)
DefaultAssay(pbmc.cite.sc) <- "RNA"
pbmc.cite.sc<- NormalizeData(pbmc.cite.sc)
DefaultAssay(pbmc.cite.sc) <- "ADT"

pbmc.cite.sc <- FindVariableFeatures(pbmc.cite.sc)
pbmc.cite.sc<- NormalizeData(pbmc.cite.sc,normalization.method = "CLR",margin = 2)

genes.to.prot <- read.csv("../../../input/pbmcCiteSeqAtlas/gene_protein.csv",header = T)
genes.to.prot

feature_x <- genes.to.prot$gene.name
feature_y <- genes.to.prot$X.protein
pbmc.cite.sc$size <- 1
w.cor.pearson <- FeatureFeaturePlot.SuperCell(seurat.obj = pbmc.cite.sc,
                                                     feature.x = genes.to.prot$gene.name,
                                                     feature.y = genes.to.prot$X.protein,
                                                     assays = c("RNA","ADT"),
                                                     is.normalized = T,
                                                     plot = F)

w.cor.pearson$input <- "Single-cells"
w.cor.pearson$gamma <- 1
w.cor.pearson$origIdent <- pbmc.cite.sc$orig.ident[1]
w.cor.pearson
```


```{r}
corTableAll <- w.cor.pearson
for (g in c("10","20","50","75","100","200")){
  print(g)
  for (i in c('SuperCellMulti',"randomMetacells")){
    file <- paste0("../../../output/pbmcCiteSeqAtlas/P1_0/",
                   i,"/g",
                   g,
                   "/corrTablePearson.csv")
    if (file.exists(file)) {
      corTable <- read.csv(file,row.names = 1)
      if (i == 'SuperCellMulti') {i <- "Metacells"}
      if (i == 'randomMetacells') {i <- "Random-grouping"}
      corTable$input <- i
      print(i)
      print(anyNA(corTable$feature1))
      corTable$gamma <- g
      corTableAll <- rbind(corTable,corTableAll)
    }
  }
  print(head(corTableAll))
  ## subsampling


  sub.cells <- sample(colnames(pbmc.cite.sc),size = floor(ncol(pbmc.cite.sc)/as.numeric(g)),replace = F)
  pbmc.cite.sub <- subset(pbmc.cite.sc,cells = sub.cells)
  pbmc.cite.sub$size = 1
  w.cor <- FeatureFeaturePlot.SuperCell(seurat.obj = pbmc.cite.sub,
                                               feature.x = feature_x,
                                               feature.y = feature_y,
                                               assays = c("RNA","ADT"),
                                               is.normalized = F,
                                               cluster = "celltype",
                                               plot = F)

  w.cor$input <- "Down-sampling"
  w.cor$gamma <- g
  w.cor$origIdent <- pbmc.cite.sub$orig.ident[1]

  corTableAll <- rbind(corTableAll,w.cor)
  print(head(corTableAll))

}


corTableAll$gene <- stringr::str_split_fixed(corTableAll$feature2,pattern = "_",2)[,2]
corTableAll$gamma <- factor(corTableAll$gamma,level = c("1","10","20","50","75","100","200"))
corTableAll$method <- factor(corTableAll$input,level = rev(c("Metacells","Random-grouping","Down-sampling","Single-cells")))

table(corTableAll$input,corTableAll$gamma)
```
```{r}
corTableAll[corTableAll$w.cor<0 & corTableAll$method == "Metacells",]
```

When we don't have two cells expressing the feature in both modalities to compute a correlation we set pearson r to 0

```{r fig.height=3.5,fig.width=4}
corTableAll$w.cor[is.na(corTableAll$w.cor)] <- 0
boxplot.corr.pbmc.cite <- ggplot(corTableAll,aes(x=gamma,y=w.cor,fill = method)) +
  theme_bw() +  geom_boxplot(position = position_dodge2(preserve = "single")) +
  ylab("Weighted pearson r") +xlab(paste0("Graining level (\u03B3)")) + scale_fill_manual(values = color.methods) + theme(legend.position = "bottom") +
  guides(fill=guide_legend(ncol =2)) + theme(legend.title = element_blank()) + ggtitle("RNA-Protein Correlations")

boxplot.corr.pbmc.cite
dir.create("../../../pdf_files/FigS4/", recursive = T, showWarnings = F)
pdf(file = "../../../pdf_files/FigS4/figS4C.pdf",height = 4,width=6)
boxplot.corr.pbmc.cite
dev.off()
```


```{r fig.height=3.75,fig.width=4.85}
pbmc.cite.mc <- readRDS("../../../output/pbmcCiteSeqAtlas/P1_0/SuperCellMulti/g75/seurat.cite.mc.rds")
pbmc.cite.mc <- addCellType(pbmc.cite.mc)

figSupCov <- DimPlotSC(seurat = pbmc.cite.sc,
                       seurat.mc = pbmc.cite.mc,
                       metacell.col = "celltype",
                       sc.col = "celltype",
                       mc.color = color.celltypes.pbmc,
                       sc.color = color.celltypes.pbmc) + theme_classic()  +
  guides(fill=guide_legend(ncol =1,title = "Cell types",
                           override.aes = list(size=4)),
         colour = "none",
         size = guide_legend(title = "Size")) +
  theme(legend.spacing.y = unit(-0.2, "line"),legend.key.size = unit(1, "line"))

dir.create("../../../pdf_files/FigS4/", recursive = T, showWarnings = F)
pdf(file = "../../../pdf_files/FigS4/figS4A.pdf",height = 4,width=5)
figSupCov
dev.off()
```

```{r fig.height=6,fig.width=6.5}
DefaultAssay(pbmc.cite.mc) <- "RNA"
pbmc.cite.mc<- NormalizeData(pbmc.cite.mc)
DefaultAssay(pbmc.cite.mc) <- "ADT"

pbmc.cite.mc<- NormalizeData(pbmc.cite.mc,normalization.method = "CLR",margin = 2)

corr.CD8a.mc <- FeatureScatter.SuperCell(pbmc.cite.mc,
                                         "rna_CD8A","adt_CD8a",group.by = "celltype", cols = color.celltypes.pbmc) +
  guides(
    colour = "none",fill = "none",
    size = guide_legend(title = "Size")) + xlab("RNA CD8A") +ylab("Protein CD8A") +
  ggtitle("Metacell",
          subtitle = paste0("weighted pearson r = ",
                            round(corTableAll[(corTableAll$method == "Metacells" & corTableAll$gamma == 75) & corTableAll$gene == "CD8a","w.cor"],
                                  digits = 2)))
corr.CD14.mc <- FeatureScatter.SuperCell(pbmc.cite.mc,
                                         "rna_CD14","adt_CD14",group.by = "celltype", cols = color.celltypes.pbmc) +
  guides(
    colour = "none",fill = "none",
    size = guide_legend(title = "Size")) +
  ggtitle("Metacell",
          subtitle = paste0("weighted pearson r = ",
                            round(corTableAll[(corTableAll$method == "Metacells" & corTableAll$gamma == 75) & corTableAll$gene == "CD14","w.cor"],
                                  digits = 2))) + xlab("RNA CD8A") +ylab("Protein CD8A")





pbmc.cite.sc$size <- 1
corr.CD8a.sc <- FeatureScatter(pbmc.cite.sc,
                               "rna_CD8A","adt_CD8a",group.by = "celltype", cols = color.celltypes.pbmc) +
  ggtitle("Single-cells",
          subtitle = paste0("pearson r = ",
                            round(corTableAll[(corTableAll$gamma == 1) & corTableAll$gene == "CD8a","w.cor"],
                                  digits = 2))) + xlab("RNA CD8A") +ylab("Protein CD8A")
corr.CD14.sc <- FeatureScatter(pbmc.cite.sc,
                               "rna_CD14","adt_CD14",group.by = "celltype", cols = color.celltypes.pbmc)   +
  ggtitle("Single-cells",
          subtitle = paste0("pearson r = ",
                            round(corTableAll[(corTableAll$gamma == 1) & corTableAll$gene == "CD14","w.cor"],
                                  digits = 2))) + xlab("RNA CD8A") +ylab("Protein CD8A")

pdf(file = "../../../pdf_files/FigS4/figS4B.pdf",height = 6,width=6)
wrap_plots(corr.CD8a.sc + NoLegend(),corr.CD8a.mc,corr.CD14.sc + NoLegend(),corr.CD14.mc+ NoLegend(),nrow = 2)
dev.off()

```
```{r}
# library(gprofiler2)
# corTableAll$gene
#
# neg.cor.prot.rna <- corTableAll[(corTableAll$gamma == 75) & corTableAll$w.cor < -0.01 ,"gene"]
# all.genes <- unique(corTableAll$gene)
# gres <- gprofiler2::gost(query = neg.cor.prot.rna,organism = "hsapiens",significant = T,custom_bg = all.genes,user_threshold = 0.5)
# unique(gres$result$source)
# gres$result[order(gres$result$p_value),]
# gres$result$intersection_size

```


# HSPC multiome related figures

## Global parameters
```{r}

color.celltypes.hspc <- c("#FFD92F", "#999999", "#E69F00", "#33A02C", "#56B4E9","#CCEBC5", "#FB9A99", "#6A3D9A")

names(color.celltypes.hspc) <- c("HMP" , "Mono","CLP", "cDC","HSC" ,"pDC","Ery", "MEP")


```

all single cell corr

```{r}
hspc.sc <-  readRDS("../../../output/hspcMultiomePersad/singlecells_analysis/seurat.multiome.activities.rds")
DefaultAssay(hspc.sc) <- "RNA"
hspc.sc <- Seurat::FindVariableFeatures(hspc.sc,nfeatures = 6000)

hvg.info <- HVFInfo(hspc.sc)[order(HVFInfo(hspc.sc)$variance.standardized,decreasing = T),]
hvg.info$ATAC <- F
hvg.info$ATAC[rownames(hvg.info)%in% rownames(hspc.sc[["GA_Signac"]])] <- T
features.ga.rna.hspc <- rownames(hvg.info[hvg.info$ATAC == T,])[1:4000]

hspc.sc<- NormalizeData(hspc.sc)
DefaultAssay(hspc.sc) <- "GA_Signac"
w.cor.pearson <- readRDS("../../../output/hspcMultiomePersad/singlecells_analysis/CorrTables.rds")

w.cor.pearson <- w.cor.pearson$SignacGA.RNA
w.cor.pearson$input <- "Single-cells"
w.cor.pearson$gamma <- 1
w.cor.pearson$gene <- str_split_fixed(w.cor.pearson$feature1,pattern = "_",n = 2)[,2]
w.cor.pearson <- w.cor.pearson[w.cor.pearson$gene %in% features.ga.rna.hspc,]
w.cor.pearson
```




```{r}
corTableAll <- w.cor.pearson
for (g in c("10","20","50","75","100","200")){
  for (i in c('SuperCellMulti',"randomMetacells")){
    file <- paste0("../../../output/hspcMultiomePersad/",
                   i,"/g",
                   g,
                   "/CorrTables.rds")
    if (file.exists(file)) {
      corTable <- readRDS(file)$SignacGA.RNA
      if (i == 'SuperCellMulti') {i <- "Metacells"}
      if (i == 'randomMetacells') {i <- "Random-grouping"}
      corTable$input <- i
      print(i)
      corTable$gamma <- g
      corTable$gene <- str_split_fixed(corTable$feature1,pattern = "_",n = 2)[,2]
      corTable <- corTable[corTable$gene %in% features.ga.rna.hspc,]

      corTableAll <- rbind(corTable,corTableAll)
    }
  }

  ## subsampling


  sub.cells <- sample(colnames(hspc.sc),size = floor(ncol(hspc.sc)/as.numeric(g)),replace = F)
  hspc.sub <- subset(hspc.sc,cells = sub.cells)
  hspc.sub$size = 1
  w.cor <- FeatureFeaturePlot.SuperCell(seurat.obj  = hspc.sub,
                                        feature.x  = features.ga.rna.hspc,
                                        feature.y  = features.ga.rna.hspc,
                                        assays = c("GA_Signac","RNA"),
                                        is.normalized = F,
                                        cluster = "celltype",
                                        plot = F)


  w.cor$input <- "Down-sampling"
  w.cor$gamma <- g
  w.cor$gene <- str_split_fixed(w.cor$feature1,pattern = "_",n = 2)[,2]

  corTableAll <- rbind(corTableAll,w.cor)


}


corTableAll$gamma <- factor(corTableAll$gamma,level = c("1","10","20","50","75","100","200"))
corTableAll$method <- factor(corTableAll$input,level = rev(c("Metacells","Random-grouping","Down-sampling","Single-cells")))

table(corTableAll$input,corTableAll$gamma)
```
```{r}
table(corTableAll[corTableAll$method == "Metacells" & corTableAll$gamma == 75,]$w.cor <0)

```


When we don't have two cells expressing the feature in both modalities to compute a correlation we set pearson r to 0

```{r fig.height=3.5,fig.width=4}
corTableAll$w.cor[is.na(corTableAll$w.cor)] <- 0
boxplot.corr.hspc <- ggplot(corTableAll,aes(x=gamma,y=w.cor,fill = method)) +
  theme_bw() +  geom_boxplot(position = position_dodge2(preserve = "single")) +
  ylab("Weighted pearson r") +xlab(paste0("Graining level (\u03B3)")) + scale_fill_manual(values = color.methods) + theme(legend.position = "bottom") +
  guides(fill=guide_legend(ncol =2)) + theme(legend.title  = element_blank()) + ggtitle("ATAC-RNA correlations")

boxplot.corr.hspc
pdf(file = "../../../pdf_files/FigS4/figS4F.pdf",height = 4,width=6)
boxplot.corr.hspc
dev.off()
```



```{r fig.height=6,fig.width=6.5}
hspc.mc <- readRDS("../../../output/hspcMultiomePersad/SuperCellMulti/g75/seurat.multiome.activities.rds")
DefaultAssay(hspc.mc) <- "RNA"
hspc.mc <- NormalizeData(hspc.mc)
gc()

corr.GATA1.mc <- FeatureScatter.SuperCell(hspc.mc,
                                         "gasignac_GATA1",
                                         "rna_GATA1",group.by = "celltype", cols = color.celltypes.hspc) +
  guides(fill="none",
         colour = "none",
         size = guide_legend(title = "Size")) + xlab("ATAC GATA1") +ylab("RNA GATA1")+
  ggtitle("Metacell",
          subtitle = paste0("weighted pearson r = ",
                            round(corTableAll[(corTableAll$method == "Metacells" & corTableAll$gamma == 75) & corTableAll$feature1 == "rna_GATA1","w.cor"],
                                  digits = 2)))
corr.FLT3.mc <- FeatureScatter.SuperCell(hspc.mc,
                                         "gasignac_FLT3","rna_FLT3",group.by = "celltype", cols = color.celltypes.hspc)  +
  guides(fill="none",
         colour = "none",
         size = guide_legend(title = "Size")) +
  ggtitle("Metacell",
          subtitle = paste0("weighted pearson r = ",
                            round(corTableAll[(corTableAll$method == "Metacells" & corTableAll$gamma == 75) & corTableAll$feature1 == "rna_FLT3","w.cor"],
                                  digits = 2))) + xlab("ATAC FLT3") +ylab("RNA FLT3")





hspc.sc$size <- 1
corr.GATA1.sc <- FeatureScatter(hspc.sc,"gasignac_GATA1",
                               "rna_GATA1",group.by = "celltype", cols = color.celltypes.hspc) +
  ggtitle("Single-cells",
          subtitle = paste0("pearson r = ",
                            round(corTableAll[(corTableAll$gamma == 1) & corTableAll$feature1 == "rna_GATA1","w.cor"],
                                  digits = 2))) + xlab("ATAC GATA1") +ylab("RNA GATA1")
corr.FLT3.sc <- FeatureScatter(hspc.sc,
                               "gasignac_FLT3","rna_FLT3",group.by = "celltype", cols = color.celltypes.hspc)   +
  ggtitle("Single-cells",
          subtitle = paste0("pearson r = ",
                            round(corTableAll[(corTableAll$gamma == 1) & corTableAll$feature1 == "rna_FLT3","w.cor"],
                                  digits = 2))) + xlab("ATAC FLT3") +ylab("RNA FLT3")


pdf(file = "../../../pdf_files/FigS4/figS4E.pdf",height = 6,width=6)
wrap_plots(corr.FLT3.sc + NoLegend(),corr.FLT3.mc,corr.GATA1.sc + NoLegend(),corr.GATA1.mc+ NoLegend(),nrow = 2)
dev.off()
```

Fig sup cov HSPC

```{r fig.height=3.75,fig.width=4.85}


figSupCovHSPC <- DimPlotSC(seurat = hspc.sc,
                       seurat.mc = hspc.mc,
                       metacell.col = "celltype",
                       sc.col = "celltype",
                       mc.color = color.celltypes.hspc,
                       sc.color = color.celltypes.hspc) + theme_classic()  +
  guides(fill=guide_legend(ncol =1,title = "Cell types",
                           override.aes = list(size=4)),
         colour = "none",
         size = guide_legend(title = "Size")) +
  theme(legend.spacing.y = unit(-0.35, "line"),legend.key.size = unit(1, "line"))


figSupCovHSPC
pdf(file = "../../../pdf_files/FigS4/figS4D.pdf",height = 4,width=5)
figSupCovHSPC
dev.off()
```
```{r}
saveRDS(corTableAll,"../../../output/tables/figS4_corrtables_rna_atac_hspc.rds")
```
```{r}
library(gprofiler2)
neg.cor.ga.rna <- unique(corTableAll[(corTableAll$gamma == 75) & corTableAll$w.cor < 0 & corTableAll$method == "Metacells" ,"gene"])
# all.genes <- rownames(pbmc.mc[["GA_Signac"]])
all.genes <- unique(corTableAll$gene)
gres <- gprofiler2::gost(query = list("weighted r < 0, HSPC metacells (\u03B3 = 75)"=neg.cor.ga.rna),organism = "hsapiens",significant = T,custom_bg = all.genes,user_threshold = 0.05,evcodes = TRUE)
gres$result[order(gres$result$p_value),]
gres$result$dataset <- "HSPC"
```




```{r}
library(gprofiler2)
corTableAll.pbmc <- readRDS("../../../output/tables/fig4_corrtables_rna_atac_pbmc.rds")
neg.cor.ga.rna <- unique(corTableAll.pbmc[(corTableAll.pbmc$gamma == 75) & corTableAll.pbmc$w.cor < 0 & corTableAll.pbmc$method == "Metacells" ,"gene"])
# all.genes <- rownames(pbmc.mc[["GA_Signac"]])
all.genes <- unique(corTableAll.pbmc$gene)
gres.pbmc <- gprofiler2::gost(query = list("weighted r < 0, PBMC metacells (\u03B3 = 75)"=neg.cor.ga.rna),organism = "hsapiens",significant = T,custom_bg = all.genes,user_threshold = 0.05,evcodes = TRUE)
unique(gres.pbmc$result$source)
if(!is.null(gres.pbmc$result) ){
  gres.pbmc$result[order(gres.pbmc$result$p_value),]
  gres.pbmc$result$dataset <- "PBMC"
}


```

```{r fig.height=2,fig.width=7}
gres.all <- rbind(gres.pbmc$result,gres$result)
gres.all$term_source <- paste0(gres.all$source, " : " ,gres.all$term_name)

pdf(file = "../../../pdf_files/FigS4/figS4H.pdf",height = 3.5,width=8)

ggplot(gres.all,aes(x= term_source,y=-log10(p_value),fill = dataset)) +
  geom_bar(stat = "identity",colour  = "black") + theme_bw() + theme(axis.title.y = element_blank()) +
  geom_hline(yintercept = -log10(0.05),linetype = "dashed",color = 'red',size = 1.24)+
  coord_flip() +
  scale_fill_manual(values = scales::grey_pal(0,1)(10)[c(3,8)]) +
  ggtitle("Functional enrichments of ATAC-RNA \nanticorrelated genes")
dev.off()
```
```{r}
corTableAll.pbmc$Dataset <- "PBMC"
corTableAll$Dataset <- "HSPC"
corTableAllDatasets <- rbind(corTableAll.pbmc,corTableAll)
corTableAllDatasets <- corTableAllDatasets[corTableAll$method %in% c("Single-cells","Metacells"),]
```


```{r fig.height=2.5,fig.width=4}
corTableAllDatasets$w.cor[is.na(corTableAllDatasets$w.cor)] <- 0
boxplot.corr.datasets <- ggplot(corTableAllDatasets,aes(x=gamma,y=w.cor,fill = Dataset)) +
  theme_bw() +  geom_boxplot() +
  ylab("Weighted pearson r") +xlab(paste0("Graining level (\u03B3)")) +
  scale_fill_manual(values = scales::grey_pal(0,1)(10)[c(3,8)]) + NoLegend()+
  guides(fill=guide_legend(ncol =1)) + theme(legend.title  = element_blank()) + ggtitle("ATAC-RNA correlations")

boxplot.corr.datasets
pdf(file = "../../../pdf_files/FigS4/figS4G.pdf",height = 4,width=6)
boxplot.corr.datasets
dev.off()
```

<!-- ## Motif -->


<!-- ```{r} -->
<!-- top.tf.single_cells <-  readRDS( "../../../output/hspcMultiomePersad/singlecells_analysis/multimodalMarkers_mainCellTypes_wilcoxonAUC.rds") -->
<!-- max(top.tf.single_cells$RNA.padj) -->
<!-- max(top.tf.single_cells$chromvar.padj) -->


<!-- w.cor.pearson <- readRDS("../../../output/hspcMultiomePersad/singlecells_analysis/CorrTables.rds") -->

<!-- w.cor.pearson <- w.cor.pearson$chromVar.RNA -->
<!-- w.cor.pearson$input <- "Single-cells" -->
<!-- w.cor.pearson$gamma <- 1 -->

<!-- head(w.cor.pearson) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- corTableAll <- w.cor.pearson -->
<!-- for (g in c("10","20","50","75","100","200")){ -->
<!--   for (i in c('SuperCellMulti')){ -->
<!--     file <- paste0("../../../output/hspcMultiomePersad/", -->
<!--                    i,"/g", -->
<!--                    g, -->
<!--                    "/CorrTables.rds") -->
<!--     if (file.exists(file)) { -->
<!--       corTable <- readRDS(file)$chromVar.RNA -->
<!--       if (i == 'SuperCellMulti') {i <- "Metacells"} -->
<!--       if (i == 'randomMetacells') {i <- "Random-grouping"} -->
<!--       corTable$input <- i -->
<!--       print(i) -->
<!--       corTable$gamma <- g -->
<!--       corTableAll <- rbind(corTable,corTableAll) -->
<!--     } -->
<!--   } -->

<!--   ## subsampling -->


<!--   # sub.cells <- sample(colnames(pbmc.sc),size = floor(ncol(pbmc.sc)/as.numeric(g)),replace = F) -->
<!--   # pbmc.sub <- subset(pbmc.sc,cells = sub.cells) -->
<!--   # pbmc.sub$size = 1 -->
<!--   # w.cor <- FeatureFeaturePlot.SuperCell(seurat.obj  = pbmc.sub, -->
<!--   #                                       feature.x  = stringr::str_split_fixed(w.cor.pearson$feature1,pattern = "_",3)[,2], -->
<!--   #                                       feature.y  = stringr::str_split_fixed(w.cor.pearson$feature1,pattern = "_",3)[,2], -->
<!--   #                                       assays = c("GA_Signac","RNA"), #TODO: DEFINE a RNA slot an the beginning -->
<!--   #                                       is.normalized = F,method = "pearson", -->
<!--   #                                       cluster = "celltype", -->
<!--   #                                       plot = F) -->
<!--   #  -->
<!--   #  -->
<!--   # w.cor$input <- "Down-sampling" -->
<!--   # w.cor$gamma <- g -->
<!--   #  -->
<!--   # corTableAll <- rbind(corTableAll,w.cor) -->


<!-- } -->


<!-- corTableAll$gamma <- factor(corTableAll$gamma,level = c("1","10","20","50","75","100","200")) -->
<!-- corTableAll$method <- factor(corTableAll$input,level = rev(c("Metacells","Single-cells"))) -->
<!-- corTableAll$Gene <- str_split_fixed(corTableAll$feature1,pattern = "_",n=2)[,2] -->
<!-- corTableAll$multimodal_marker <- "Other TFs" -->
<!-- corTableAll$multimodal_marker[corTableAll$Gene %in% top.tf.single_cells$gene] <- "Multimodal markers" -->


<!-- table(corTableAll$input,corTableAll$gamma) -->
<!-- ``` -->


<!-- When we don't have two cells expressing the feature in both modalities to compute a correlation we set pearson r to 0 -->

<!-- ```{r fig.height=3.5,fig.width=4} -->
<!-- corTableAll$w.cor[is.na(corTableAll$w.cor)] <- 0  -->
<!-- boxplot.corr.pbmc <- ggplot(corTableAll,aes(x=gamma,y=w.cor,fill = multimodal_marker)) +  -->
<!--   theme_bw() +  geom_boxplot(position = position_dodge2(preserve = "single")) +  -->
<!--   guides(fill=guide_legend(ncol =1)) + -->
<!--   ylab("Weighted pearson r") +xlab(paste0("Graining level (\u03B3)")) + scale_fill_manual(values = scales::brewer_pal(palette = 'Dark2')(2))+ theme(legend.position = "bottom") + -->
<!--   theme(legend.title=element_blank())  -->
<!-- boxplot.corr.pbmc -->
<!-- ``` -->

<!-- ```{r} -->
<!-- library(gprofiler2) -->
<!-- neg.cor.ga.rna <- corTableAll[(corTableAll$gamma == 75) & corTableAll$w.cor < -0.01  ,"Gene"] -->
<!-- all.genes <- unique(corTableAll$Gene) -->
<!-- gres <- gprofiler2::gost(query = neg.cor.ga.rna,organism = "hsapiens",significant = T,custom_bg = all.genes,user_threshold = 0.1) -->
<!-- unique(gres$result$source) -->
<!-- gres$result[order(gres$result$p_value),] -->
<!-- gres$result$intersection_size -->
<!-- ``` -->


<!-- ```{r fig.height=6,fig.width=8.25} -->
<!-- detectedMotifs[relatedTFs[relatedTFs %in% TF]] -->



<!-- corr.TCF7.mc <- FeatureScatter.SuperCell(pbmc.mc, -->
<!--                                          "rna_TCF7",detectedMotifs[relatedTFs[relatedTFs %in% "TCF7"]], -->
<!--                                          group.by = "celltype", cols = color.celltypes.pbmc)+  -->
<!--   ggtitle("Metacell", -->
<!--           subtitle = paste0("weighted pearson r = ", -->
<!--                             round(corTableAll[(corTableAll$method == "Metacells" & corTableAll$gamma == 75) & corTableAll$feature1 == "rna_TCF7","w.cor"], -->
<!--                                   digits = 2))) + xlab("RNA TCF7") + ylab("Motif TCF7") -->

<!-- corr.TCF7L2.mc <- FeatureScatter.SuperCell(pbmc.mc, -->
<!--                                            "rna_TCF7L2",detectedMotifs[relatedTFs[relatedTFs %in% "TCF7L2"]], -->
<!--                                            group.by = "celltype", cols = color.celltypes.pbmc) + -->
<!--   ggtitle("Metacell", -->
<!--           subtitle = paste0("weighted pearson r = ", -->
<!--                             round(corTableAll[(corTableAll$method == "Metacells" & corTableAll$gamma == 75) & corTableAll$feature1 == "rna_TCF7L2","w.cor"], -->
<!--                                   digits = 2))) + xlab("RNA TCF7L2") + ylab("Motif TCF7L2") -->





<!-- pbmc.cite.sc$size <- 1 -->
<!-- corr.TCF7.sc <- FeatureScatter(pbmc.sc,"rna_TCF7", -->
<!--                                detectedMotifs[relatedTFs[relatedTFs %in% "TCF7"]],group.by = "celltype", cols = color.celltypes.pbmc) +  -->
<!--   ggtitle("Single-cells", -->
<!--           subtitle = paste0("pearson r = ", -->
<!--                             round(corTableAll[(corTableAll$gamma == 1) & corTableAll$feature1 == "rna_TCF7L2","w.cor"], -->
<!--                                   digits = 2)))+ xlab("RNA TCF7") + ylab("Motif TCF7") -->
<!-- corr.TCF7L2.sc <- FeatureScatter(pbmc.sc, -->
<!--                                  "gasignac_SPI1","rna_SPI1",group.by = "celltype", cols = color.celltypes.pbmc)   +  -->
<!--   ggtitle("Single-cells", -->
<!--           subtitle = paste0("pearson r = ", -->
<!--                             round(corTableAll[(corTableAll$gamma == 1) & corTableAll$feature1 == "rna_SPI1","w.cor"], -->
<!--                                   digits = 2))) + xlab("RNA TCF7L2") + ylab("Motif TCF7L2") -->

<!-- wrap_plots(motifs.p$TCF7, corr.TCF7.sc + NoLegend(),corr.TCF7.mc + NoLegend(), -->
<!--            motifs.p$TCF7L2_rev,corr.TCF7L2.sc + NoLegend(),corr.TCF7L2.mc+ NoLegend(),nrow = 2,widths = c(2.7,2,2)) -->
<!-- ``` -->







<!-- ```{r  fig.height=6,fig.width=12} -->
<!-- corr.TCF7L2.TCF7.motif.mc <- FeatureScatter.SuperCell(pbmc.mc, -->
<!--                                                       detectedMotifs[relatedTFs[relatedTFs %in% "TCF7"]],detectedMotifs[relatedTFs[relatedTFs %in% "TCF7L2"]], -->
<!--                                                       group.by = "celltype", cols = color.celltypes.pbmc) + -->
<!--   ggtitle("Metacell") -->

<!-- corr.TCF7L2.TCF7.motif.mc -->



<!-- pbmc.cite.sc$size <- 1 -->
<!-- corr.TCF7L2.TCF7.motif.sc <- FeatureScatter(pbmc.sc, -->
<!--                                             detectedMotifs[relatedTFs[relatedTFs %in% "TCF7"]],detectedMotifs[relatedTFs[relatedTFs %in% "TCF7L2"]], -->
<!--                                             group.by = "celltype", cols = color.celltypes.pbmc) +  -->
<!--   ggtitle("Single-cells") -->

<!-- wrap_plots(corr.TCF7L2.TCF7.motif.sc+ NoLegend(),corr.TCF7L2.TCF7.motif.mc) -->

<!-- ``` -->


<!-- ```{r} -->

<!-- ``` -->














<!-- ```{r} -->
<!-- # Load single-cell seurat object -->
<!-- seurat.sc = readRDS("../../../output/hspcMultiomePersad/singlecells_analysis/seurat.multiome.activities.rds") -->
<!-- seraut.sc <- addCellTypePBMC(seurat.sc) -->
<!-- seurat.sc$celltype_main <- seraut.sc$celltype -->

<!-- seurat.sc <- DietSeurat(seurat.sc, assays = c("RNA", "ATAC", "SCT", "GA_Signac", "chromvar")) -->
<!-- DefaultAssay(seurat.sc) <- "RNA" -->
<!-- seurat.sc <- NormalizeData(seurat.sc) -->
<!-- seurat.sc <- FindVariableFeatures(seurat.sc, nfeatures = 2000) -->
<!-- var.genes <- Seurat::VariableFeatures(seurat.sc) -->
<!-- # seurat.sc$celltype_main <- plyr::revalue(seurat.sc$celltype, c("B Interm" = "Bcells","B Mem" = "Bcells","B Naive" = "Bcells", -->
<!-- #                                                                "CD14 Mono" = "Monocytes","CD16 Mono" = "Monocytes", -->
<!-- #                                                                "CD4 Naive" = "CD4_Tcells","CD4 Mem" = "CD4_Tcells", -->
<!-- #                                                                "CD8 Naive" = "CD8_Tcells","CD8 Mem" = "CD8_Tcells")) -->
<!-- names(seurat.sc@assays)[names(seurat.sc@assays) ==  "GA_Signac"] <- "GA" -->
<!-- seurat.sc@assays$GA@key <- "ga_" -->

<!-- # Load metacell seurat object -->
<!-- gamma = 75 -->
<!-- seurat.mc <- readRDS(paste0("../../../output/hspcMultiomePersad/SuperCellMulti/g", gamma, "/seurat.multiome.activities.rds")) -->

<!-- seurat.mc <- addCellTypePBMC(seurat.mc) -->
<!-- seurat.mc$celltype_main <- seurat.mc$celltype -->


<!-- DefaultAssay(seurat.mc) <- 'RNA' -->
<!-- seurat.mc <- NormalizeData(seurat.mc) -->
<!-- seurat.mc <- DietSeurat(seurat.mc, assays = c("RNA", "ATAC", "SCT", "GA_Signac", "chromvar")) -->
<!-- gc() -->
<!-- # seurat.mc$celltype_main <- plyr::revalue(seurat.mc$celltype, c("B Interm" = "Bcells", "B Mem" = "Bcells", "B Naive" = "Bcells", -->
<!-- #                                                                "CD14 Mono" = "Monocytes", "CD16 Mono" = "Monocytes", -->
<!-- #                                                                "CD4 Naive" = "CD4_Tcells", "CD4 Mem" = "CD4_Tcells", -->
<!-- #                                                                "CD8 Naive" = "CD8_Tcells","CD8 Mem" = "CD8_Tcells")) -->
<!-- names(seurat.mc@assays)[names(seurat.mc@assays) ==  "GA_Signac"] <- "GA" -->
<!-- seurat.mc@assays$GA@key <- "ga_" -->
<!-- ``` -->

<!-- ## Motifs logo plots  -->
<!-- ```{r} -->
<!-- TFs <- c("TCF7", "TCF7L2", "LEF1")  -->

<!-- DefaultAssay(pbmc.sc) <- "ATAC" -->
<!-- detectedMotifs <- rownames(pbmc.sc@assays$chromvar) #motif -->
<!-- relatedTFs <- ConvertMotifID(pbmc.sc, id = detectedMotifs) #tf -->
<!-- detectedMotifs <- detectedMotifs[relatedTFs %in% rownames(pbmc.sc[["RNA"]])] -->
<!-- relatedTFs <- relatedTFs[relatedTFs %in% rownames(pbmc.sc[["RNA"]])] -->
<!-- names(detectedMotifs) = relatedTFs -->

<!-- motifs.p <- list() -->

<!-- for(TF in TFs){ -->
<!--   m <- detectedMotifs[relatedTFs[relatedTFs %in% TF]] -->
<!--   motifs.p[[TF]] <- MotifPlot(pbmc.sc, motifs = m)  -->

<!--   data.use <- GetMotifData(object = pbmc.sc, assay = "ATAC",  -->
<!--                            slot = "pwm")[m] -->
<!--   TF_rev = data.use -->
<!--   names(TF_rev) <- TF -->
<!--   rownames(TF_rev[[TF]]) <- plyr::revalue(rownames(TF_rev[[TF]]), replace = c("A" = "T", "T"= "A", "C" = "G", "G" = "C")) -->
<!--   TF_rev[[TF]] <- TF_rev[[TF]][,ncol(TF_rev[[TF]]):1] -->
<!--   motifs.p[[paste0(TF,"_rev")]] <- ggseqlogo::ggseqlogo(TF_rev)  -->

<!-- } -->

<!-- ``` -->
<!-- ```{r} -->

<!-- detectedMotifs[relatedTFs[relatedTFs %in% TF]] -->
<!-- ``` -->



<!-- ```{r} -->

<!-- group.by = "celltype" -->
<!-- for(TF in TFs){ -->
<!--   assays <- c("RNA", "GA") -->
<!--   ff.plot.res.sc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.sc, is.normalized = T, cluster = group.by, -->
<!--                                                  assays = assays, feature.x = TF, feature.y = TF, -->
<!--                                                  color.use = celltype_colors, -->
<!--                                                  use.size = F, plot = T, pt.size = 2, add.key = T) -->
<!--   sc.p <- ff.plot.res.sc$plots[[1]]+ mytheme + guides(fill = guide_legend(override.aes = list(size=3),ncol = 3)) -->
<!--   assign(paste0(TF, ".sc.GA.RNA"), sc.p) -->

<!--   ff.plot.res.mc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.mc, -->
<!--                                                  is.normalized = T, cluster = group.by, -->
<!--                                                  assays = assays,feature.x = TF, feature.y = TF, -->
<!--                                                  color.use = celltype_colors, -->
<!--                                                  use.size = T,plot = T) -->
<!--   mc.p <- ff.plot.res.mc$plots[[1]] + mytheme + guides(fill = guide_legend(override.aes = list(size=3),ncol = 3)) -->
<!--   assign(paste0(TF, ".mc.GA.RNA"), mc.p) -->


<!--   assays <- c("RNA", "chromvar") -->
<!--   ff.plot.res.sc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.sc, is.normalized = T, cluster = group.by, -->
<!--                                                  assays = assays, feature.x = TF, feature.y = detectedMotifs[relatedTFs[relatedTFs %in% TF]], -->
<!--                                                  color.use = celltype_colors, -->
<!--                                                  use.size = F, plot = T, pt.size = 2, add.key = F) -->
<!--   sc.p <- ff.plot.res.sc$plots[[1]]+ mytheme + guides(fill = guide_legend(override.aes = list(size=3), ncol = 3)) -->
<!--   assign(paste0(TF, ".sc.chromVAR.RNA"), sc.p) -->

<!--   ff.plot.res.mc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.mc, -->
<!--                                                  is.normalized = T,cluster = group.by, -->
<!--                                                  assays = assays,feature.x = TF, feature.y = detectedMotifs[relatedTFs[relatedTFs %in% TF]], -->
<!--                                                  color.use = celltype_colors, -->
<!--                                                  use.size = T,plot = T, add.key = F) -->
<!--   mc.p <- ff.plot.res.mc$plots[[1]] + mytheme + guides(fill = guide_legend(override.aes = list(size=3), ncol = 3)) -->
<!--   assign(paste0(TF, ".mc.chromVAR.RNA"), mc.p) -->

<!-- } -->

<!-- pdf("../../../output/plots/plots_Intermodality_Sup/pbmcMultiome_sc_mc_FeatureFeaturePlots_TCF7family.pdf", h=12, w=12) -->
<!-- # grid with blanks and legend -->
<!-- blank_size = 0.05 -->
<!-- blankPlot <- ggplot()+ geom_blank(aes(1,1)) +  -->
<!--   cowplot::theme_nothing() -->

<!-- grid.arrange( -->
<!--   TCF7.sc.chromVAR.RNA + mytheme +NoLegend(), blankPlot, TCF7.mc.chromVAR.RNA + mytheme +NoLegend(), blankPlot, arrangeGrob(motifs.p$TCF7_rev, motifs.p$LEF1, motifs.p$TCF7L2), -->
<!--   blankPlot, blankPlot, blankPlot, blankPlot, -->
<!--   LEF1.sc.chromVAR.RNA + mytheme +NoLegend(), blankPlot, LEF1.mc.chromVAR.RNA + mytheme + NoLegend(), blankPlot, -->
<!--   blankPlot, blankPlot, blankPlot, blankPlot, blankPlot, -->
<!--   TCF7L2.sc.chromVAR.RNA + mytheme + NoLegend(), blankPlot, TCF7L2.mc.chromVAR.RNA + mytheme + NoLegend(), blankPlot, cowplot::get_legend(TCF7.mc.chromVAR.RNA), -->
<!--   ncol = 5, layout_matrix = rbind(c(1:5), c(6:9,5), c(10:13, 5), c(14:18), c(19:23)), -->
<!--   widths = c(1, blank_size, 1, blank_size, 1), heights = c(1, blank_size, 1, blank_size, 1) -->
<!-- ) -->
<!-- dev.off() -->

<!-- pdf("../../../output/plots/plots_Intermodality_Sup/pbmcMultiom_sc_mc_FeatureFeaturePlots_SPI1.pdf", w=12, h=4) -->
<!-- grid.arrange( -->
<!--   SPI1.sc.GA.RNA + mytheme + NoLegend(), blankPlot,  -->
<!--   SPI1.mc.GA.RNA + mytheme + NoLegend(), blankPlot,  -->
<!--   cowplot::get_legend(SPI1.sc.GA.RNA + guides(fill = guide_legend(override.aes = list(size=3), ncol = 2))), -->
<!--   ncol = 5,  -->
<!--   widths = c(1, blank_size, 1, blank_size, 0.5) -->
<!-- ) -->
<!-- dev.off() -->
<!-- ``` -->

<!-- ## Correlations between GA vs RNA at the cell/metacell level -->
<!-- ```{r} -->

<!-- cor.matrices.sc <- readRDS( "../../../output/pbmcMultiome/singlecells_analysis/CorrTables.rds") -->
<!-- GA.Signac.cor <- cor.matrices.sc$SignacGA.perCell -->

<!-- cell.groups <- plyr::revalue(seurat.sc$celltype, c("B Naive" = "Bcells", "B Mem" = "Bcells",  "B Interm" = "Bcells", -->
<!--                                                    "CD16 Mono" = "Mono", "CD14 Mono" = "Mono")) -->
<!-- cor.matrix.sc <- matrix(0, nrow = length(unique(cell.groups)), ncol = length(unique(cell.groups)), dimnames = list(unique(cell.groups), unique(cell.groups))) -->
<!-- for(celltype1 in unique(cell.groups)){ -->
<!--   for(celltype2 in unique(cell.groups)){ -->
<!--     cor.matrix.sc[celltype1, celltype2] <- mean(GA.Signac.cor[cell.groups %in% c(celltype1), cell.groups %in% c(celltype2)]) -->
<!--   } -->
<!-- } -->


<!-- DefaultAssay(seurat.mc) <- "RNA" -->
<!-- seurat.mc <- FindVariableFeatures(seurat.mc) -->
<!-- var.genes.mc <- Seurat::VariableFeatures(seurat.mc) -->
<!-- var.genes.mc <- var.genes.mc[var.genes.mc %in% rownames(seurat.mc[["GA"]])] -->
<!-- GA.Signac.cor <- cor(as.matrix(GetAssayData(seurat.mc, assay = "GA", slot = "data")[var.genes.mc,]),  -->
<!--                      as.matrix(GetAssayData(seurat.mc, assay = "RNA", slot = "data")[var.genes.mc,])) -->

<!-- cell.groups <- plyr::revalue(seurat.mc$celltype, c("B Naive" = "Bcells", "B Mem" = "Bcells",  "B Interm" = "Bcells", -->
<!--                                                    "CD16 Mono" = "Mono", "CD14 Mono" = "Mono")) -->
<!-- cor.matrix.mc <- matrix(0, nrow = length(unique(cell.groups)), ncol = length(unique(cell.groups)), dimnames = list(unique(cell.groups), unique(cell.groups))) -->

<!-- for(celltype1 in unique(cell.groups)){ -->
<!--   for(celltype2 in unique(cell.groups)){ -->
<!--     cor.matrix.mc[celltype1, celltype2] <- mean(GA.Signac.cor[cell.groups %in% c(celltype1), cell.groups %in% c(celltype2)]) -->
<!--   } -->
<!-- } -->

<!-- col_fun <- colorRamp2(c(min(c(cor.matrix.sc, cor.matrix.mc)),  -->
<!--                         mean(c(cor.matrix.sc, cor.matrix.mc)),  -->
<!--                         max(c(cor.matrix.sc, cor.matrix.mc))), -->
<!--                       c("white","gold", "red")) -->

<!-- row_hclust <- hclust(dist(cor.matrix.sc)) -->
<!-- row_dend   <- rev(as.dendrogram(row_hclust)) -->
<!-- row_order  <- order.dendrogram(row_dend) -->
<!-- p1 <- Heatmap(cor.matrix.sc, show_row_names = T, show_column_names = T,row_names_side = "left", -->
<!--               show_row_dend = T, show_column_dend = F, cluster_rows =  row_dend, cluster_columns = F,  -->
<!--               row_order = row_order, column_order = row_order, col=col_fun, -->
<!--               name = "Correlation", column_title = paste0("Gamma = ", 1)) -->

<!-- p2 <- Heatmap(cor.matrix.mc[rownames(cor.matrix.sc), colnames(cor.matrix.sc)], show_row_names = T, show_column_names = T,row_names_side = "left", show_heatmap_legend = T, -->
<!--               show_row_dend = T, show_column_dend = F, cluster_rows =  row_dend, cluster_columns = F,  -->
<!--               row_order = row_order, column_order = row_order, col=col_fun, -->
<!--               name = "Correlation", column_title = paste0("Gamma = ", gamma)) -->
<!-- draw(p1 + p2, heatmap_legend_side="right") -->
<!-- pdf("../../../output/plots/plots_Intermodality_Sup/pbmcMultiome_plasticity_heatmap.pdf",w=6.5,h=3.5) -->
<!-- draw(p1 + p2, heatmap_legend_side="right") -->
<!-- dev.off() -->

<!-- ``` -->


<!-- ## Pando analysis -->
<!-- ### Compare pando methods -->
<!-- ```{r} -->
<!-- p_thresh <- 0.1 -->
<!-- load(paste0(data_path, "/SuperCellMulti/pando_metrics_summary_p_thresh", p_thresh, ".RData")) -->

<!-- n.target.genes$resolution <- factor(n.target.genes$resolution, levels = paste0("gamma.", c(1, 10, 20, 50, 75, 100, 200))) -->
<!-- ggplot(n.target.genes,aes(x = resolution, y = n_genes, color = method)) + geom_boxplot() -->

<!-- n_regions$resolution <- factor(n_regions$resolution,levels=paste0("gamma.", c(1, 10, 20, 50, 75, 100, 200))) -->
<!-- ggplot(n_regions,aes(x = resolution,y=n_regions, color = method)) + geom_boxplot() -->

<!-- n_tfs$resolution <- factor(n_tfs$resolution,levels= paste0("gamma.", c(1, 10, 20, 50, 75, 100, 200))) -->
<!-- ggplot(n_tfs,aes(x = resolution,y=n_tfs, color = method)) + geom_boxplot() -->

<!-- ``` -->

<!-- ### Pando enrichment results -->


<!-- ```{r} -->
<!-- seurat.sc <- pbmc.sc -->
<!-- net <- decoupleR::get_collectri(organism='human', split_complexes=T) -->
<!-- ``` -->

<!-- ```{r} -->



<!-- GetEnrichmentPval <- function(tf, -->
<!--                               modules, -->
<!--                               net, -->
<!--                               only.pos = F, -->
<!--                               tested.genes = hvgs) {  -->

<!--   net <- net[net$source == tf,] -->
<!--   net <- net[net$target %in% tested.genes,] -->
<!--   modules <-  data.frame(modules@meta) -->
<!--   modules <- modules[modules$tf == tf,] -->
<!--   net$curated_regulation <- paste0(net$mor,"_",net$target) -->
<!--   modules$predicted_regulation <- paste0(sign(modules$estimate),"_",modules$target) -->
<!--   if(only.pos) { -->
<!--     net <- net[net$mor >0,] -->
<!--     modules <- modules[modules$estimate >0,] -->
<!--   } -->

<!--   mor = 2 -->
<!--   if (only.pos) { -->
<!--     mor = 1 -->
<!--   } -->

<!--   m = length(net$curated_regulation) # Number of curated regulation in test set -->
<!--   n = mor*length(tested.genes) - m # Number of non-curated targets in test set -->
<!--   x = length(intersect(modules$predicted_regulation,net$curated_regulation)) # Overlap between predicted and curated regulations -->
<!--   k = length(unique(modules$predicted_regulation)) # Total number of predicted targets -->
<!--   p.value <- phyper(x - 1, m, n, k, lower.tail = F) -->
<!--   #p.value <- 1 - phyper(x - 1, m, n, k) -->
<!--   return(p.value) -->
<!-- } -->




<!-- mytheme <- theme(axis.text.x = element_text(size = 11, face = "bold"), -->
<!--                  axis.text.y = element_text(size = 11), -->
<!--                  axis.title = element_text(size = 12, face = "bold"), -->
<!--                  plot.title = element_text(size = 14, face = "bold", hjust = 0.5)) -->

<!-- assign("modules_sc", readRDS( paste0(data_path, "/singlecells_analysis/modules_g1_met_sc_pval_", p_thresh, ".rds"))) -->

<!-- DefaultAssay(seurat.sc) <- "RNA" -->
<!-- seurat.sc <- FindVariableFeatures(seurat.sc, assay='RNA', nfeatures = 4000) -->
<!-- hvgs <- Seurat::VariableFeatures(seurat.sc) -->

<!-- # method =  "LSI2_norm_svy" -->
<!-- # for(method in c("aggregate", "LSI1_norm_svy", "meanSC_norm_svy")){ -->
<!-- for(method in c( "LSI1_norm_svy")){ -->


<!--   for(gamma in c(10, 20, 50, 75, 100, 200)){ -->
<!--     assign(paste0("modules_g",gamma), readRDS( paste0(data_path, "/SuperCellMulti/g", gamma, "/modules_g", gamma, "_met_", method, "_pval_", p_thresh, ".rds"))) -->
<!--   } -->

<!--   # Counts number of targets genes per TF ----------------------------------- -->

<!--   curated.tf <- names(which(table(net$source)>10)) -->
<!--   tfs <- Reduce(intersect, list(curated.tf, -->
<!--                                 modules_sc@meta$tf, -->
<!--                                 modules_g10@meta$tf, -->
<!--                                 modules_g20@meta$tf, -->
<!--                                 modules_g50@meta$tf, -->
<!--                                 modules_g75@meta$tf, -->
<!--                                 modules_g100@meta$tf, -->
<!--                                 modules_g200@meta$tf)) -->

<!--   predicted.target.sc <- sapply(tfs, function(x) { nrow(modules_sc@meta[modules_sc@meta$tf == x,])}) -->
<!--   predicted.target.g10 <- sapply(tfs, function(x) { nrow(modules_g10@meta[modules_g10@meta$tf == x,])}) -->
<!--   predicted.target.g20 <- sapply(tfs, function(x) { nrow(modules_g20@meta[modules_g20@meta$tf == x,])}) -->
<!--   predicted.target.g50 <- sapply(tfs, function(x) { nrow(modules_g50@meta[modules_g50@meta$tf == x,])}) -->
<!--   predicted.target.g75 <- sapply(tfs, function(x) { nrow(modules_g75@meta[modules_g75@meta$tf == x,])}) -->
<!--   predicted.target.g100 <- sapply(tfs, function(x) { nrow(modules_g100@meta[modules_g100@meta$tf == x,])}) -->
<!--   predicted.target.g200 <- sapply(tfs, function(x) { nrow(modules_g200@meta[modules_g200@meta$tf == x,])}) -->

<!--   nb_genes <- as.data.frame(cbind(predicted.target.sc, predicted.target.g10, predicted.target.g20,  -->
<!--                                   predicted.target.g50, predicted.target.g75,  -->
<!--                                   predicted.target.g100, predicted.target.g200)) -->

<!--   df_long <- nb_genes %>% -->
<!--     pivot_longer(cols = starts_with("predicted.target"),  -->
<!--                  names_to = "Group",  -->
<!--                  values_to = "Num_Genes") -->
<!--   df_long$Group <- factor(gsub("predicted.target.", "", df_long$Group), levels = c("sc", paste0("g",c(10,20,50,75,100,200)))) -->


<!--   Means <- df_long %>% group_by(Group) %>%  -->
<!--     summarize(Avg = mean(Num_Genes)) -->

<!--   nb_genes_plot <- ggplot(df_long, aes(x = Group, y = Num_Genes)) + -->
<!--     geom_boxplot(fill = "lightblue", color = "black", outlier.color = "black") + -->
<!--     geom_point(mapping = aes(x = Group, y = Avg), data = Means, color = "red", shape = 2) + -->
<!--     geom_line(data = Means, mapping = aes(x = Group, y = Avg), group = 1, color = "red") + -->
<!--     theme_bw() + -->
<!--     labs(title = method,  -->
<!--          x = "",  -->
<!--          y = "Nb. predicted targets") + -->
<!--     mytheme -->
<!--   # print(nb_genes_plot) -->

<!--   # Enrichment results all directions ----------------------------------------------------- -->

<!--   pval.sc <- sapply(tfs,function(x){ GetEnrichmentPval(tf = x,modules = modules_sc,net = net,tested.genes = hvgs)}, USE.NAMES = T) -->
<!--   pval.g10 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g10,net = net,tested.genes = hvgs)}, USE.NAMES = T) -->
<!--   pval.g20 <- sapply(tfs,function(x){ GetEnrichmentPval(tf = x,modules = modules_g20,net = net,tested.genes = hvgs)}, USE.NAMES = T) -->
<!--   pval.g50 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g50,net = net,tested.genes = hvgs)}, USE.NAMES = T) -->
<!--   pval.g75 <- sapply(tfs,function(x){ GetEnrichmentPval(tf = x,modules = modules_g75,net = net,tested.genes = hvgs)}, USE.NAMES = T) -->
<!--   pval.g100 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g100,net = net,tested.genes = hvgs)}, USE.NAMES = T) -->
<!--   pval.g200 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g200,net = net,tested.genes = hvgs)}, USE.NAMES = T) -->

<!--   res <- data.frame("sc" = pval.sc, -->
<!--                     "g10" = pval.g10, -->
<!--                     "g20" = pval.g20, -->
<!--                     "g50" = pval.g50, -->
<!--                     "g75" = pval.g75, -->
<!--                     "g100" = pval.g100, -->
<!--                     "g200" = pval.g200) -->


<!--   res_long <- res %>% -->
<!--     pivot_longer( -->
<!--       cols = colnames(res),  # Specify the columns to pivot -->
<!--       names_to = "group",  # Name of the new column for groups -->
<!--       values_to = "value"  # Name of the new column for values -->
<!--     ) -->

<!--   res_long$resolution <- factor(res_long$group, levels= c("sc","g10","g20","g50","g75","g100","g200")) -->

<!--   stats <- res_long %>% group_by(resolution) %>%  -->
<!--     summarize(stat = median(value)) -->

<!--   pval_boxplot <- ggplot(res_long, aes(x = resolution, y=(value))) +  -->
<!--     geom_boxplot(fill = "lightblue", color = "black", outlier.color = "black" ) +  -->
<!--     geom_jitter(width = 0.1) +  -->
<!--     geom_point(mapping = aes(x = resolution, y = stat), data = stats, color = "red", shape = 2) + -->
<!--     geom_line(data = stats, mapping = aes(x = resolution, y = stat), group = 1, color = "red") + -->
<!--     theme_bw() + -->
<!--     labs(title = paste0(method," (common TFs)"),  -->
<!--          x = "",  -->
<!--          y = "P-value") + -->
<!--     mytheme -->


<!--   # Enrichment using only positive regulation ------------------------------- -->

<!--   curated.tf <- names(which(table(net[net$mor>0,]$source)>10)) -->

<!--   tfs <- Reduce(intersect, list( -->
<!--     curated.tf, -->
<!--     modules_sc@meta$tf, -->
<!--     modules_g10@meta$tf, -->
<!--     modules_g20@meta$tf, -->
<!--     modules_g50@meta$tf, -->
<!--     modules_g75@meta$tf, -->
<!--     modules_g100@meta$tf, -->
<!--     modules_g200@meta$tf -->
<!--   )) -->

<!--   pval.sc <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_sc,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T) -->
<!--   pval.g10 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g10,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T) -->
<!--   pval.g20 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g20,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T) -->
<!--   pval.g50 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g50,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T) -->
<!--   pval.g75 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g75,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T) -->
<!--   pval.g100 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g100,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T) -->
<!--   pval.g200 <- sapply(tfs,function(x){ GetEnrichmentPval(x,modules_g200,net = net,tested.genes = hvgs,only.pos = T)},USE.NAMES = T) -->

<!--   res <- data.frame("sc" = pval.sc, -->
<!--                     "g10" = pval.g10, -->
<!--                     "g20"= pval.g20, -->
<!--                     "g50" = pval.g50, -->
<!--                     "g75" = pval.g75, -->
<!--                     "g100" = pval.g100, -->
<!--                     "g200" = pval.g200) -->


<!--   res_long <- res %>% -->
<!--     pivot_longer( -->
<!--       cols = colnames(res),  # Specify the columns to pivot -->
<!--       names_to = "group",  # Name of the new column for groups -->
<!--       values_to = "value"  # Name of the new column for values -->
<!--     ) -->

<!--   res_long$resolution <- factor(res_long$group,levels= c("sc","g10","g20","g50","g75","g100","g200")) -->
<!--   stats <- res_long %>% group_by(resolution) %>%  -->
<!--     summarize(stat = median(value)) -->

<!--   pval_boxplot_onlyPos <- ggplot(res_long, aes(x = resolution, y=(value))) +  -->
<!--     geom_boxplot(fill = "lightblue", color = "black", outlier.color = "black" ) + -->
<!--     geom_jitter(width = 0.1) +  -->
<!--     geom_point(mapping = aes(x = resolution, y = stat), data = stats, color = "red", shape = 2) + -->
<!--     geom_line(data = stats, mapping = aes(x = resolution, y = stat), group = 1, color = "red") + -->
<!--     theme_bw() + -->
<!--     labs(title = paste0(method," (only pos., common TFs)"),  -->
<!--          x = "",  -->
<!--          y = "P-value") + -->
<!--     mytheme -->

<!--   combined.plot <- nb_genes_plot | pval_boxplot  | pval_boxplot_onlyPos -->
<!--   # combined.plot <- nb_genes_plot | pval_boxplot   -->
<!--   print(combined.plot) -->
<!--   assign(paste0("p.",method), combined.plot) -->

<!-- } -->
<!-- pdf(paste0("../../../output/plots/plots_Intermodality_Sup/pando_figures_pval_",p_thresh,".pdf"), w=15,h=5) -->
<!-- # p.LSI1_norm_svy -->
<!-- dev.off() -->

<!-- ``` -->


<!-- ```{r} -->

<!-- p.LSI2_norm_svy -->
<!-- ``` -->
<!-- # PLot for LSI method 1 svy -->
<!-- ```{r fig.height=3,fig.width=6} -->
<!-- comparisons <- list( -->

<!--   # c("1","50"), -->
<!--   c("1", "75")) -->

<!-- library(ggsignif) -->

<!-- df_long$graining_level <- str_split_fixed(df_long$Group,"g",n=2)[,2] -->
<!-- df_long$graining_level[df_long$graining_level == ""] <- "1" -->
<!-- df_long$graining_level <- factor(df_long$graining_level,as.character(c(1,10,20,50,75,100,200))) -->

<!-- nb_genes_plot <- ggplot(df_long, aes(x = graining_level, y = Num_Genes)) + -->
<!--   geom_boxplot(fill = "lightblue", color = "black", outlier.color = "black") + -->
<!--   # geom_point(mapping = aes(x = Group, y = Avg), data = Means, color = "red", shape = 2) + -->
<!--   # geom_line(data = Means, mapping = aes(x = Group, y = Avg), group = 1, color = "red") + -->
<!--   theme_bw() + -->
<!--   labs(title = method,  -->
<!--        x = "Graining level (\u03B3)",  -->
<!--        y = "Predicted targets") + ggtitle("Pando regulon size") -->

<!-- stats <- res_long %>% group_by(resolution) %>%  -->
<!--   summarize(stat = median(-log10(value))) -->

<!-- res_long$graining_level <- str_split_fixed(res_long$resolution,"g",n=2)[,2] -->
<!-- res_long$graining_level[res_long$graining_level == ""] <- "1" -->
<!-- res_long$graining_level <- factor(res_long$graining_level,as.character(c(1,10,20,50,75,100,200))) -->

<!-- pval_boxplot <- ggplot(res_long, aes(x = graining_level, y=-log10(value))) +  -->
<!--   geom_boxplot(fill = "lightblue", color = "black", outliers = F ) +  -->
<!--   geom_signif(comparisons = comparisons,y_position = 2.5, -->
<!--               step_increase=0.05,tip_length = 0.005, -->
<!--               map_signif_level=F,extend_line = -0.005, -->
<!--               textsize = 5)+ coord_cartesian(ylim = c(0,3.25))+ -->
<!--   # geom_jitter(width = 0.1) +  -->
<!--   # geom_point(mapping = aes(x = resolution, y = stat), data = stats, color = "red", shape = 2) + -->
<!--   # geom_line(data = stats, mapping = aes(x = resolution, y = stat), group = 1, color = "red") + -->
<!--   theme_bw() + -->
<!--   labs(title = paste0(method," (common TFs)"),  -->
<!--        x = "",  -->
<!--        y = "- log10(P-value)") + -->
<!--   labs( -->
<!--     x = "Graining level (\u03B3)",  -->
<!--     y = "Predicted targets")+ -->
<!--   ggtitle("Enrichment in curated targets") -->

<!-- wrap_plots(nb_genes_plot,pval_boxplot) -->
<!-- ``` -->

<!-- # Hspc multiome related figures -->

<!-- ## Global parameters -->
<!-- ```{r} -->
<!-- data_path <- paste0(opt$resdir, "/hspcMultiomePersad/") -->
<!-- celltype_colors <- c("HMP" = "#999999", "Mono" = "#004949", "HSC" = "#009292", -->
<!--                      "Ery" = "#FF6DB6", "MEP" = "#490092", "cDC" = "#006DDB",  -->
<!--                      "CLP" = "#B66DFF", "pDC" = "#6DB6FF") -->


<!-- # plot theme -->
<!-- axis.size <- 15 -->
<!-- mytheme <-  theme(axis.title = element_text(size = axis.size), -->
<!--                   axis.text.x = element_text(size = axis.size), -->
<!--                   axis.text.y = element_text(size = axis.size), -->
<!--                   legend.title = element_text(size = 15), -->
<!--                   legend.text = element_text(size=13))  -->

<!-- ``` -->

<!-- ```{r} -->
<!-- # Load single-cell seurat object -->
<!-- seurat.sc = readRDS(paste0(data_path, "singlecells_analysis/seurat.multiome.activities.rds")) -->
<!-- seurat.sc <- DietSeurat(seurat.sc, assays = c("RNA", "ATAC", "SCT", "GA_Signac", "chromvar"), dimreducs = "wnn.umap") -->
<!-- DefaultAssay(seurat.sc) <- "RNA" -->
<!-- seurat.sc <- NormalizeData(seurat.sc) -->
<!-- seurat.sc <- FindVariableFeatures(seurat.sc, nfeatures = 2000) -->
<!-- var.genes <- Seurat::VariableFeatures(seurat.sc) -->
<!-- names(seurat.sc@assays)[names(seurat.sc@assays) ==  "GA_Signac"] <- "GA" -->
<!-- seurat.sc@assays$GA@key <- "ga_" -->

<!-- # Load metacell seurat object -->
<!-- gamma = 75 -->
<!-- seurat.mc <- readRDS(paste0(data_path, "SuperCellMulti/g", gamma, "/seurat.multiome.activities.rds")) -->
<!-- DefaultAssay(seurat.mc) <- 'RNA' -->
<!-- seurat.mc <- NormalizeData(seurat.mc) -->
<!-- seurat.mc <- DietSeurat(seurat.mc, assays = c("RNA", "ATAC", "SCT", "GA_Signac", "chromvar")) -->
<!-- gc() -->

<!-- names(seurat.mc@assays)[names(seurat.mc@assays) ==  "GA_Signac"] <- "GA" -->
<!-- seurat.mc@assays$GA@key <- "ga_" -->
<!-- ``` -->

<!-- ## Motifs logo plots  -->
<!-- ```{r} -->
<!-- TFs <- c("GATA1")  -->
<!-- DefaultAssay(seurat.sc) <- "ATAC" -->
<!-- detectedMotifs <- rownames(seurat.sc@assays$chromvar) #motif -->
<!-- relatedTFs <- ConvertMotifID(seurat.sc, id = detectedMotifs) #tf -->
<!-- detectedMotifs <- detectedMotifs[relatedTFs %in% rownames(seurat.sc[["RNA"]])] -->
<!-- relatedTFs <- relatedTFs[relatedTFs %in% rownames(seurat.sc[["RNA"]])] -->
<!-- names(detectedMotifs) = relatedTFs -->

<!-- motifs.p <- list() -->

<!-- for(TF in TFs){ -->
<!--   m <- detectedMotifs[relatedTFs[relatedTFs %in% TF]] -->
<!--   motifs.p[[TF]] <- MotifPlot(seurat.sc, motifs = m)  -->

<!--   data.use <- GetMotifData(object = seurat.sc, assay = "ATAC",  -->
<!--                            slot = "pwm")[m] -->
<!--   TF_rev = data.use -->
<!--   names(TF_rev) <- TF -->
<!--   rownames(TF_rev[[TF]]) <- plyr::revalue(rownames(TF_rev[[TF]]), replace = c("A" = "T", "T"= "A", "C" = "G", "G" = "C")) -->
<!--   TF_rev[[TF]] <- TF_rev[[TF]][,ncol(TF_rev[[TF]]):1] -->
<!--   motifs.p[[paste0(TF,"_rev")]] <- ggseqlogo::ggseqlogo(TF_rev)  -->

<!-- } -->

<!-- ``` -->

<!-- ```{r} -->

<!-- group.by = "celltype" -->
<!-- for(TF in TFs){ -->
<!--   assays <- c("RNA", "GA") -->
<!--   ff.plot.res.sc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.sc, is.normalized = T, cluster = group.by, -->
<!--                                                  assays = assays, feature.x = TF, feature.y = TF, -->
<!--                                                  color.use = celltype_colors, -->
<!--                                                  use.size = F, plot = T, pt.size = 2, add.key = T) -->
<!--   sc.p <- ff.plot.res.sc$plots[[1]]+ mytheme + guides(fill = guide_legend(override.aes = list(size=3),ncol = 3)) -->
<!--   assign(paste0(TF, ".sc.GA.RNA"), sc.p) -->

<!--   ff.plot.res.mc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.mc, -->
<!--                                                  is.normalized = T, cluster = group.by, -->
<!--                                                  assays = assays,feature.x = TF, feature.y = TF, -->
<!--                                                  color.use = celltype_colors, -->
<!--                                                  use.size = T,plot = T) -->
<!--   mc.p <- ff.plot.res.mc$plots[[1]] + mytheme + guides(fill = guide_legend(override.aes = list(size=3),ncol = 3)) -->
<!--   assign(paste0(TF, ".mc.GA.RNA"), mc.p) -->


<!--   assays <- c("RNA", "chromvar") -->
<!--   ff.plot.res.sc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.sc, is.normalized = T, cluster = group.by, -->
<!--                                                  assays = assays, feature.x = TF, feature.y = detectedMotifs[relatedTFs[relatedTFs %in% TF]], -->
<!--                                                  color.use = celltype_colors, -->
<!--                                                  use.size = F, plot = T, pt.size = 2, add.key = F) -->
<!--   sc.p <- ff.plot.res.sc$plots[[1]]+ mytheme + guides(fill = guide_legend(override.aes = list(size=3), ncol = 3)) -->
<!--   assign(paste0(TF, ".sc.chromVAR.RNA"), sc.p) -->

<!--   ff.plot.res.mc <- FeatureFeaturePlot.SuperCell(seurat.obj = seurat.mc, -->
<!--                                                  is.normalized = T,cluster = group.by, -->
<!--                                                  assays = assays,feature.x = TF, feature.y = detectedMotifs[relatedTFs[relatedTFs %in% TF]], -->
<!--                                                  color.use = celltype_colors, -->
<!--                                                  use.size = T,plot = T, add.key = F) -->
<!--   mc.p <- ff.plot.res.mc$plots[[1]] + mytheme + guides(fill = guide_legend(override.aes = list(size=3), ncol = 3)) -->
<!--   assign(paste0(TF, ".mc.chromVAR.RNA"), mc.p) -->

<!-- } -->

<!-- # grid with blanks and legend -->
<!-- blank_size = 0.05 -->
<!-- blankPlot <- ggplot()+ geom_blank(aes(1,1)) +  -->
<!--   cowplot::theme_nothing() -->

<!-- grid.arrange( -->
<!--   GATA1.sc.GA.RNA + mytheme + NoLegend(), blankPlot,  -->
<!--   GATA1.mc.GA.RNA + mytheme + NoLegend(), blankPlot,  -->
<!--   cowplot::get_legend(GATA1.sc.GA.RNA + guides(fill = guide_legend(override.aes = list(size=3), ncol = 2))), -->
<!--   ncol = 5,  -->
<!--   widths = c(1, blank_size, 1, blank_size, 0.5) -->
<!-- ) -->

<!-- # save plot in pdf -->
<!-- pdf(paste0(opt$outdir, "hspcMultiomePersad_sc_mc_FeatureFeaturePlots_GATA1.pdf"), w=10, h=4) -->
<!-- grid.arrange( -->
<!--   GATA1.sc.GA.RNA + mytheme + NoLegend(), blankPlot,  -->
<!--   GATA1.mc.GA.RNA + mytheme + NoLegend(), blankPlot,  -->
<!--   cowplot::get_legend(GATA1.sc.GA.RNA + guides(fill = guide_legend(override.aes = list(size=3), ncol = 2))), -->
<!--   ncol = 5,  -->
<!--   widths = c(1, blank_size, 1, blank_size, 0.5) -->
<!-- ) -->
<!-- dev.off() -->
<!-- ``` -->
<!-- ## UMAP plot -->
<!-- ```{r} -->
<!-- png(paste0(opt$outdir, "hspcMultiomePersad_UMAPprojetcion.png"),width = 5*300, height = 4*300, res= 300) -->
<!-- projection <- mc_projection( -->
<!--   sc.obj = seurat.sc,  -->
<!--   mc.obj = seurat.mc, -->
<!--   cell.membership = data.frame(row.names = names(seurat.mc@misc$membership), membership = paste0("Metacell_",seurat.mc@misc$membership)), -->
<!--   sc.reduction = "wnn.umap", mc.color = celltype_colors, sc.color = celltype_colors,  -->
<!--   sc.label = "celltype", -->
<!--   metacell.label = "celltype" -->
<!-- )  -->
<!-- projection + ggtitle(paste0("UMAP projection (hspcMultiomePersad)")) + mytheme + -->
<!--   guides(colour = guide_legend(override.aes = list(size=4))) -->
<!-- dev.off() -->

<!-- ``` -->

<!-- ## Correlations between GA vs RNA at the cell/metacell level -->
<!-- ```{r} -->
<!-- cor.matrices.sc <- readRDS(paste0(opt$resdir, "hspcMultiomePersad/singlecells_analysis/CorrTables.rds")) -->
<!-- GA.Signac.cor <- cor.matrices.sc$SignacGA.perCell -->

<!-- cell.groups <- seurat.sc$celltype -->

<!-- cor.matrix.sc <- matrix(0, nrow = length(unique(cell.groups)), ncol = length(unique(cell.groups)), dimnames = list(unique(cell.groups), unique(cell.groups))) -->
<!-- for(celltype1 in unique(cell.groups)){ -->
<!--   for(celltype2 in unique(cell.groups)){ -->
<!--     cor.matrix.sc[celltype1, celltype2] <- mean(GA.Signac.cor[cell.groups %in% c(celltype1), cell.groups %in% c(celltype2)]) -->
<!--   } -->
<!-- } -->


<!-- DefaultAssay(seurat.mc) <- "RNA" -->
<!-- seurat.mc <- FindVariableFeatures(seurat.mc) -->
<!-- var.genes.mc <- VariableFeatures(seurat.mc) -->
<!-- var.genes.mc <- var.genes.mc[var.genes.mc %in% rownames(seurat.mc[["GA"]])] -->
<!-- GA.Signac.cor <- cor(as.matrix(GetAssayData(seurat.mc, assay = "GA", slot = "data")[var.genes.mc,]),  -->
<!--                      as.matrix(GetAssayData(seurat.mc, assay = "RNA", slot = "data")[var.genes.mc,])) -->

<!-- cor.matrix.mc <- matrix(0, nrow = length(unique(cell.groups)), ncol = length(unique(cell.groups)), dimnames = list(unique(cell.groups), unique(cell.groups))) -->

<!-- cell.groups <- seurat.mc$celltype -->
<!-- for(celltype1 in unique(cell.groups)){ -->
<!--   for(celltype2 in unique(cell.groups)){ -->
<!--     cor.matrix.mc[celltype1, celltype2] <- mean(GA.Signac.cor[cell.groups %in% c(celltype1), cell.groups %in% c(celltype2)]) -->
<!--   } -->
<!-- } -->

<!-- # col_fun <- colorRamp2(c(min(c(cor.matrix.sc, cor.matrix.mc)),  -->
<!-- #                         mean(c(cor.matrix.sc, cor.matrix.mc)),  -->
<!-- #                         max(c(cor.matrix.sc, cor.matrix.mc))), -->
<!-- #                       c("blue", "white", "red")) -->
<!-- col_fun <- colorRamp2(c(min(c(cor.matrix.sc, cor.matrix.mc)),  -->
<!--                         mean(c(cor.matrix.sc, cor.matrix.mc)),  -->
<!--                         max(c(cor.matrix.sc, cor.matrix.mc))), -->
<!--                       c("white","gold", "red")) -->

<!-- row_hclust <- hclust(dist(cor.matrix.sc)) -->
<!-- row_dend   <- rev(as.dendrogram(row_hclust)) -->
<!-- row_order  <- order.dendrogram(row_dend) -->
<!-- p1 <- Heatmap(cor.matrix.sc, show_row_names = T, show_column_names = T,row_names_side = "left", -->
<!--               show_row_dend = T, show_column_dend = F, cluster_rows =  row_dend, cluster_columns = F,  -->
<!--               row_order = row_order, column_order = row_order, col=col_fun, -->
<!--               name = "Correlation", column_title = paste0("Gamma = ", 1)) -->

<!-- # row_hclust <- hclust(dist(cor.matrix.mc)) -->
<!-- # row_dend   <- rev(as.dendrogram(row_hclust)) -->
<!-- # row_order  <- order.dendrogram(row_dend) -->
<!-- p2 <- Heatmap(cor.matrix.mc[rownames(cor.matrix.sc), colnames(cor.matrix.sc)], show_row_names = T, show_column_names = T,row_names_side = "left", show_heatmap_legend = T, -->
<!--               show_row_dend = T, show_column_dend = F, cluster_rows =  row_dend, cluster_columns = F,  -->
<!--               row_order = row_order, column_order = row_order, col=col_fun, -->
<!--               name = "Correlation", column_title = paste0("Gamma = ", gamma)) -->
<!-- pdf(paste0(opt$outdir, "hspcMultiomePersad_plasticity_heatmap.pdf"),w=6.5,h=3.5) -->
<!-- draw(p1 + p2, heatmap_legend_side="right") -->
<!-- dev.off() -->
<!-- ``` -->



<!-- # Correlations between GA vs RNA at the gene level for each HVGs -->
<!-- ```{r} -->

<!-- cor.summary <- data.frame(gamma = vector(), gene = vector(), dataset= vector(), cor.Signac = vector()) -->
<!-- for(dat in c("hspcMultiomePersad","pbmcMultiome")){ -->
<!--   cor.matrices.sc <- readRDS(paste0(opt$resdir, dat, "/singlecells_analysis/CorrTables.rds")) -->

<!--   for(gamma in c(1, 10, 20, 30, 50, 75, 100)){ -->
<!--     if(gamma == 1){ -->
<!--       GA.Signac.cor <- cor.matrices.sc$SignacGA.RNA -->
<!--     }else{ -->
<!--       GA.Signac.cor <- readRDS(paste0(opt$resdir, dat, "/SuperCellMulti/g", gamma, "/CorrTables.rds"))$SignacGA.RNA -->
<!--     } -->
<!--     genes <- sapply(rownames(GA.Signac.cor), function(i) unlist(strsplit(i, "_"))[2]) -->
<!--     cor.summary <- rbind(cor.summary, data.frame(gamma = rep(gamma, length(genes)),  -->
<!--                                                  gene = genes,  -->
<!--                                                  dataset = dat, -->
<!--                                                  cor.Signac = GA.Signac.cor[, "w.cor"])) -->
<!--   } -->
<!-- } -->

<!-- df_long <- as.data.frame(pivot_longer(cor.summary, cols = starts_with("cor"),  -->
<!--                                       names_to = "method", values_to = "correlation")) -->
<!-- df_long$dataset <- factor(df_long$dataset) -->
<!-- df_long$gamma <- paste0("g", df_long$gamma) -->
<!-- df_long$gamma <- factor(df_long$gamma, levels = paste0("g", c(1,10,20,30,50,75,100,200))) -->

<!-- CorGARNA.boxplots <- ggplot(df_long, aes(x = factor(gamma), y = correlation, fill = dataset)) + -->
<!--   geom_boxplot(position = position_dodge(width = 0.8)) + -->
<!--   labs(x = "Gamma", y = "Correlation", title = "Correlation between HVGs expression and gene activity") + -->
<!--   theme_bw() + mytheme + theme(legend.title = element_blank())  -->
<!-- print(CorGARNA.boxplots) -->

<!-- # save figure in pdf -->
<!-- pdf(paste0(opt$outdir, "CorGARNA_boxplots.pdf"), w=10, h=3) -->
<!-- print(CorGARNA.boxplots) -->
<!-- dev.off() -->

<!-- ``` -->
